### 2018-05-09 paper/paper.tex
add paper draft

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{svproc}
%
% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\usepackage{graphicx}

\usepackage{caption}
\usepackage{subcaption}

\captionsetup{compatibility=false}

\usepackage{amsmath}
\usepackage{tikz}
\usepackage{adjustbox}

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,
                shadows, shapes.geometric, shapes.misc}

\def\UrlFont{\rmfamily}

%%%%%%%%%%%%% math stuff
\usepackage{amssymb}

%flowchart definitions
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
\tikzstyle{decision} = [diamond, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\tikzset{
  font={\fontsize{11pt}{12}\selectfont}}

% vectors in bold
\newcommand{\vp}{\mathbf{p}}
\newcommand{\valpha}{\mathbf{\alpha}}
\newcommand{\vP}{\mathbf{P}}
\newcommand{\vg}{\mathbf{g}}
\newcommand{\vf}{\mathbf{f}}
\newcommand{\vw}{\mathbf{w}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vq}{\mathbf{q}}
\newcommand{\vzero}{\mathbf{0}}
\newcommand{\vn}{\mathbf{n}}
\newcommand{\vo}{\mathbf{o}}

% sets as caligraphics
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cS}{\mathcal{S}}

% misc
\newcommand{\R}{\mathbb{R}} % real numbers

%%%%%%%%%%%%%

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Motion Execution
% 
\title{Distributed Realtime Trajectory Replanning for Robust Motion Execution in Multi-Robot Systems}

%
\titlerunning{Distributed Realtime Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskin Senbaslar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskin Senbaslar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

\maketitle              % typeset the title of the contribution

\begin{abstract}
\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots have to interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
However, all such solutions assume that the resulting trajectories can be executed approximately perfectly, which is in particular not true for teams of hundreds of robots that have to operate persistently.

We propose robust motion execution as a framework that can take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

Robust motion execution is an extension of cooperative collision avoidance where our objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.\footnote{test footnote}

% todo: perhaps write some more about what experiments we did, after we have the material

\section{Problem Formulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
We solve our problem completely in a distributed fashion. No central authority coordinates the robots and robots themselves can't communicate with their peers, hence they have no information about the plans of other robots. In every time step $K$, seperated by replanning period $\delta t$, each robot $i$ solves the following problem:
\begin{align*}
    \text{Given,}\ \ \ \ \ &\\
    \vo^i(t')&:\text{ original trajectory of robot $i$},\\
    ct&:\text{ current global time},\\
    \delta t&:\text{ replanning period},\\
    \tau&: \text{time horizon},\\ 
    c&:\text{ maximum continuity between pieces},\\
    \Theta&:\text{ occupancy grid of the environment},\\
    \{\vp_i\}&:\text{ set of positions of all robots},\\
    \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
    &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
    \text{find a new}&\text{ trajectory $\vf_K^i(t)$ such that},\\
    \vf_K^i(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
    \frac{d^j\vf_K^i(t)}{dt^j}(0) &= \frac{d^j\vf_{K-1}^i(t)}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
    \vf_K^i(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
    \vf_K^i(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
    \left\|\frac{d^j \vf^i(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
\end{align*}

Robot $i$'s trajectory $f^i(t)$ is $f_K^i(t)$ in $K^{th}$ time step. It follows the trajectory for $\delta t$ seconds, and replans to calculate $f_{K+1}^i(t)$ and replaces $f^i(t)$ with it.

\section{Preliminaries}

\subsection{Buffered Voronoi Cells}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{align*}
    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\\
    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
\end{align*}

The set of all buffered voronoi cells is called the buffered voronoi decomposition of the space. For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most. We are using this fact in order to guarantee robot-to-robot collision avoidance.

The hyperspace $\cS_i^j$ has the following definition:
\begin{align}
    \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
\end{align}
Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
\begin{align}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j. \label{voronoi_intersection_definition}
\end{align}
This definition suggests a natural algorithm to compute the buffered voronoi cell of any robot $i$ in terms of the hyperplanes $H_i^j$:
\begin{algorithmic}[1]
    \Function{Voronoi}{[$p_i$]: robot positions, $i$: robot that we want to calculate voronoi cell of, $r_i$: radius of robot $i$}
        \State $H = \{\}$
        \ForAll{$j\neq i$}
            \State $H_i^j = (\alpha_i^j, \beta_i^j)$
            \State $H = H\cup H_i^j$
        \EndFor
        \State \Return $H$
    \EndFunction
\end{algorithmic}
This is an $O(m)$ operation, $m$ being the number of robots.

\subsection{B\'ezier Curves}
A degree $d$ b\'ezier curve $\vg(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vg(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve. A b\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}. We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.

We use polynomial splines as trajectories where each piece is a b\'ezier curve. Given a trajectory $\vf^i(t)$ for robot $i$ with $l$ pieces, $T^i_j$ denotes the duration of $j^{th}$ piece, $\vf^i_j(t; T^i_j)$ denotes the $j^{th}$ piece of the trajectory, $\vP^i_{j,k}$ denotes the $k^{th}$ control point of $j^{th}$ piece, and $P^i_{j,k,u}$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $k \in \{0,1,...,d\}$, $u \in \{1,2,...,n\}$.

\subsection{Support Vector Machine}
Support vector machine is a supervised learning method that is used to classify data into several classes. In binary classification problems, given linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label, SVM problem tries to find a hyperplane with normal $\vw$ and distance along the normal $b$ that separates two classes. SVM problem for binary classification with separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
\begin{align*}
    \text{minimize}\ \ \  &\|\vw\|\\
    \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
\end{align*}
We use SVMs to define collision free convex subspaces that are obstacle-free.
\subsection{Trajectory Optimization}
We present our replanning problem as a quadratic optimization problem where the control points of the trajectory are the variables. The overall structure of quadratic optimization problems is as follows \cite{qpOASES}:
\begin{align*}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^Tg\\
    \text{subject to}\ \ \ & lbA \leq A\vx \leq ubA\\
    &lb \leq \vx \leq ub
\end{align*}

Each constraint on the problem appends a set of rows to the matrices $A$, $lbA$, and $ubA$. There are 4 types of constraints we impose: starting point constraints, end point constraints, continuity constraints and hyperplane constraints.
\subsubsection{Initial Point Constraints}
For each of the curves in the trajectory, we can impose initial point constraints. An initial point constraint requires curve to have a specific value in any order of its derivatives in the beginning. $S_j(D, T)$ is the matrix we append to $A$ in order to evaluate curve $j$ at its starting point, $D$ being the degree of derivation, $T$ being the duration of the curve.

The value of the curve in the beginning is simply a linear combination of the control points. The rows of $S_j$ are the coefficients of control points in this linear combination, each of which corresponding to a different dimension. We append the desired vector $\vq$ for the constraint to both $lbA$ and $ubA$ matrices. Note that by adding the same vector to both upper and lower bound matrices, we impose an equality constraint.
\subsubsection{End Point Constraints}
This is essentially same with starting point constraints. Only difference is that instead of evaluating the curve at $t=0$, we evaluate it at $t=T$.

$E_j(D,T)$ denotes the matrix we append to $A$ in order to evaluate the curve $j$ at its end point, $D$ being the degree of derivation, $T$ being the duration of the curve. We again append desired value vector $\vq$ to both $lbA$ and $ubA$.
\subsubsection{Continuity Constraints}
For each consecutive curves $j$ and $j+1$ in the trajectory, we can impose a continuity constraint of any degree $D$. We basically take the difference of the $D^{th}$ derivative of curve $j$ evaluated at time $t=T_j$ and the $D^{th}$ derivative of curve $j+1$ evaluated at time $t=0$ and require it to be $\vzero$. This difference is again a linear combination of the control points.

$C_j(D,T_j,T_{j+1})$ denotes the matrix we append to A in order to calculate the difference between curves $j$ and $j+1$, $D$ being the degree of derivation, $T_j$ being the duration of curve $j$ and $T_{j+1}$ being the duration of curve $j+1$. We append $\vzero$ to both $lbA$ and $ubA$.
\subsubsection{Hyperspace Constraints}
For each of the control points, we can add a hyperplane constraint that requires the point not to be in the positive side of the hyperplane. Given hyperplane with normal $\vn$ and distance along the normal $d$, not-positive side of the hyperplane is simply the set $J$ defined as
\begin{align*}
    J = \left\{\vp: \vn \cdot \vp - d \leq 0\right\}
\end{align*}

The constraint is again a linear combination of control points. $H_{j,k}(\vn)$ denotes the row we append to $A$ in order to impose a hyperplane constraint on the $k^{th}$ control point of $j^{th}$ curve, $\vn$ being the normal of the hyperplane. We add $d$ to $ubA$ and $-\infty$ to $lbA$.
\\

Notice that $S_j, E_j, C_j$ and $H_{j,k}$ matrices defined above also depend on the problem dimension $n$ and number of control points per curve $d+1$. To not to complicate the notation, we omitted these details in the symbols. In our treatment, we do not change the number of control points per curve and the dimension of the problem between replanning iterations. Therefore, omitting these details does not present any problems in terms of the completeness of our explanation. In any instance, dimension and points per curve will be inferred from the context.
\section{Approach}

% TODO: running example?

\subsection{Approach Overview}
Our approach has three big components: \emph{discrete planning} that is used in case using only optimization may present problems, \emph{trajectory optimization} to optimize trajectory while avoiding obstacles and other robots, and \emph{dynamic rescaling} to comform to the dynamic limits of the robot.

In each iteration, pipeline that is summarized in figure \ref{fig:flowchart} gets executed. Period of each iteration is $\delta_t$, and all pipeline gets executed every $\delta_t$.

In the beginning of the each iteration, we check for some conditions defined in the following sections to see if we need discrete replanning. If the answer is yes, we do a discrete search that results in a discrete path that is obstacle and robot free. Then, we transform this discrete plan to b\'ezier control points and use those points as the initial data for trajectory optimization. If the answer is no, we skip discrete search, and directly use the control points of the previous plan as the initial data.

Depending on whether we did discrete search or not, we build objective matrix $H$ for trajectory optimization in a slightly different way.

At this point, algorithm has the same flow independent of the fact that we did discrete search or not. We compute $A$ matrix that represents continuity, hyperspace, initial point and end point constraints. Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles. When the optimization is done, we check whether the dynamic limits are violated. While the answer is yes, we increase durations of pieces and do the optimization again until dynamic limits are not violated. In the end, we have a trajectory $f^i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory and is a good starting point for the next iteration.

\begin{figure}
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {need discrete replanning?};
    \node (discretesearch) [process, right of=discrete, xshift=1.2cm, yshift = 1cm, text width = 2cm] {discrete search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {discrete objective builder};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {continuous objective builder};
    \node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    {constraint builder};
    \node (trajopt) [process, right of=constraintbuild, xshift = 1cm, text width = 2cm] {trajectory optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 1.5cm, text width = 2cm] {dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
    \node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

    \coordinate[above=2cm of discrete.west, xshift=-0.2cm] (c1);
    \coordinate[below=2cm of discrete.west, xshift=-0.2cm] (c2);
    \coordinate[above=2cm of discretesearch.east, xshift = 0.2cm, yshift=-1cm] (c3);
    \coordinate[below=2cm of discretesearch.east, xshift = 0.2cm, yshift = -1cm] (c4);

    \coordinate[above=2cm of discobjbuild.west, xshift=-0.2cm, yshift=-1cm] (c5);
    \coordinate[below=2cm of discobjbuild.west, xshift=-0.2cm, yshift = -1cm] (c6);
    \coordinate[above=2cm of trajopt.east, xshift = 0.2cm] (c7);
    \coordinate[below=2cm of trajopt.east, xshift = 0.2cm] (c8);

    \coordinate[above=2cm of dynamiclimits.west, xshift=-0.2cm, ] (c9);
    \coordinate[below=2cm of dynamiclimits.west, xshift=-0.2cm, yshift = -1.5cm] (c10);
    \coordinate[above=2cm of dynamiclimits.east, xshift = 0.2cm] (c11);
    \coordinate[below=2cm of dynamiclimits.east, xshift = 0.2cm, yshift = -1.5cm] (c12);

    \draw [arrow] (discrete) -- node[anchor=south] {yes} (discretesearch);
    \draw [arrow] (discrete) -- node[anchor=north] {no} (contobjbuild);
    \draw [arrow] (discretesearch) -- (discobjbuild);
    \draw [arrow] (discobjbuild) -- (constraintbuild);
    \draw [arrow] (contobjbuild) -- (constraintbuild);
    \draw [arrow] (constraintbuild) -- (trajopt);
    \draw [arrow] (trajopt) -- (dynamiclimits);
    \draw [arrow] (dynamiclimits) -- node[anchor=south] {no} (end);
    \draw [arrow] (dynamiclimits) -- node[anchor=east] {yes} (rescale);
    \draw [arrow] (rescale) -| (trajopt);

    \node[right = 0cm of c1, yshift=0.3cm] {Discrete planning};
    \node[right = 0cm of c5, yshift=0.3cm] {Continuous optimization};
    \node[right = 0cm of c9, yshift=0.3cm] {Dynamic rescaling};

    \draw [dotted] (c1) -- (c2);
    \draw [dotted] (c2) -- (c4);
    \draw [dotted] (c4) -- (c3);
    \draw [dotted] (c3) -- (c1);

    \draw [dotted] (c5) -- (c6);
    \draw [dotted] (c6) -- (c8);
    \draw [dotted] (c8) -- (c7);
    \draw [dotted] (c7) -- (c5);

    \draw [dotted] (c9) -- (c10);
    \draw [dotted] (c10) -- (c12);
    \draw [dotted] (c12) -- (c11);
    \draw [dotted] (c11) -- (c9);
\end{tikzpicture}
}
%\end{adjustbox}
\caption{Overview of the replanning pipeline.
}
\label{fig:flowchart}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=.9\textwidth]{images/swap2_initial.pdf}
\caption{Initial configuration.}
\label{fig:swap2:initial}
\end{subfigure} \hfill
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=.9\textwidth]{images/swap2_final.pdf}
\caption{Final configuration and executed trajectories.}
\label{fig:swap2:final}
\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
}
\label{fig:swap2}
\end{figure}

\subsection{Discrete Planning}

WOLFGANG (text + pics)

% consider moving ushape down (so green guy goes up)
% fig showing (one of the) initial conditions violated
% fig showing discrete plan and initial control points, color-coded by piece [might be just one figure]

\subsection{Continuous Optimization}

BASKIN (math)

WOLFGANG (pics)
% fig showing result from before (initial control points), hyperspaces (transparent, color-coded by piece), and resulting smooth trajectory (color-coded by piece).

\subsection{Enforcing Dynamic Limits} % might be part of overview

BASKIN (math)

% potentially more subsections about SVM, hyperplanes etc, as needed
% can look at T-RO paper for this part

\subsection{Theoretical Guarantees} %maybe
% see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
% might be able to account for possible faceshift

BASKIN

\section{Evaluation}

\cite{cvxgen}
\cite{qpOASES}
\cite{osqp}

% TODO: figure out if there is some baseline (look at buffered vornoi paper)
% different use-case examples (see README.md)

\subsection{Simulation}
% scalability: #curves, #obstacles, #robots (voronoi constraint), qp-solver

% could talk about nlopt/ipopt "issues"; or: other subsection (e.g, other approaches)

\subsection{Physical Robots}

\section{Related Work}
\label{sec:relatedWork}

Our method is closely related to cooperative collision avoidance.
Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered voronoi cells, and safety barrier certificates.
Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon. Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi partition shifted by the physical extent of the robot. 
Safety barrier certificates achieves collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
All approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVO), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}).

Our realtime planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search. Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
Our robust motion execution uses the same optimization framework to generate trajectories, although with a different cost function.
We also use discrete search to quickly get out of local minima, but, unlike previous work, do so in a distributed manner.

While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
Using a discrete plan (generated by RRT*), polynomial trajectories can be generated using a quadratic program~\cite{richterISRR}.
In this case a unconstrained QP-formulation might be used, but obstacles cannot be directly taken into account.
Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
In contrast, our formulation uses a hard constraint and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
The optimization can use a discrete plan as initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.

% multi-robot:
% BVC, RVO, barrier certificate

% stanford paper

% tu munich paper
%\cite{replanning-usenko}

% t-ro paper (& other traj opt papers)
%\cite{crazyplanning-ieeetro}
%\cite{tang}
%\cite{flores}

% other traj opt:
%\cite{replanning-eth}
%\cite{richterISRR}

\section{Conclusion}

%
% ---- Bibliography ----
%
\bibliographystyle{spmpsci}
\bibliography{bibliography}

\section{TODO}

\subsection{Baskin}
problem formulation, Preliminaries

RVO2 baseline (see \url{http://gamma.cs.unc.edu/RVO2/documentation/2.0/using.html})

\subsection{Wolfgang}
%Bibliography
%related work
%intro

proper occupancy grid (respecting the robots size during planning, not during occupancy grid construction).

% Monday - Thursday/ Saturday: writing
% 
% May 11/13: physical robot experiments [warehouse]
% May 14: paper ready for review within the lab
% Tuesday May 22: submission

\end{document}

### 2018-05-09 paper/paper_example.tex
add paper draft

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{svproc}
%
% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\def\UrlFont{\rmfamily}

\begin{document}
\mainmatter              % start of a contribution
%
\title{Hamiltonian Mechanics unter besonderer Ber\"ucksichtigung der
h\"ohereren Lehranstalten}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}
Jeffrey Dean \and David Grove \and Craig Chambers \and Kim~B.~Bruce \and
Elsa Bertino}
%
\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Princeton University, Princeton NJ 08544, USA,\\
\email{I.Ekeland@princeton.edu},\\ WWW home page:
\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle              % typeset the title of the contribution

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
% We would like to encourage you to list your keywords within
% the abstract section using the \keywords{...} command.
\keywords{computational geometry, graph theory, Hamilton cycles}
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions to Hamiltonian systems. All this will be done in
the convex case; that is, we shall study the boundary-value problem
\begin{eqnarray*}
  \dot{x}&=&JH' (t,x)\\
  x(0) &=& x(T)
\end{eqnarray*}
with $H(t,\cdot)$ a convex function of $x$, going to $+\infty$ when
$\left\|x\right\| \to \infty$.

%
\subsection{Autonomous Systems}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.

We shall first consider the question of nontriviality, within the
general framework of
$\left(A_{\infty},B_{\infty}\right)$-subquadratic Hamiltonians. In
the second subsection, we shall look into the special case when $H$ is
$\left(0,b_{\infty}\right)$-subquadratic,
and we shall try to derive additional information.
%
\subsubsection{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty},B_{\infty}\right)$-sub\-qua\-dra\-tic at infinity,
for some constant symmetric matrices $A_{\infty}$ and $B_{\infty}$,
with $B_{\infty}-A_{\infty}$ positive definite. Set:
\begin{eqnarray}
\gamma :&=&{\rm smallest\ eigenvalue\ of}\ \ B_{\infty} - A_{\infty} \\
  \lambda : &=& {\rm largest\ negative\ eigenvalue\ of}\ \
  J \frac{d}{dt} +A_{\infty}\ .
\end{eqnarray}

Theorem~\ref{ghou:pre} tells us that if $\lambda +\gamma < 0$, the
boundary-value problem:
\begin{equation}
\begin{array}{rcl}
  \dot{x}&=&JH' (x)\\
  x(0)&=&x (T)
\end{array}
\end{equation}
has at least one solution
$\overline{x}$, which is found by minimizing the dual
action functional:
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt
\end{equation}
on the range of $\Lambda$, which is a subspace $R (\Lambda)_{L}^{2}$
with finite codimension. Here
\begin{equation}
  N(x) := H(x) - \frac{1}{2} \left(A_{\infty} x,x\right)
\end{equation}
is a convex function, and
\begin{equation}
  N(x) \le \frac{1}{2}
  \left(\left(B_{\infty} - A_{\infty}\right) x,x\right)
  + c\ \ \ \forall x\ .
\end{equation}

%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set:
\begin{equation}
  \delta := \liminf_{x\to 0} 2 N (x) \left\|x\right\|^{-2}\ .
  \label{eq:one}
\end{equation}

If $\gamma < - \lambda < \delta$,
the solution $\overline{u}$ is non-zero:
\begin{equation}
  \overline{x} (t) \ne 0\ \ \ \forall t\ .
\end{equation}
\end{proposition}
%
\begin{proof}
Condition (\ref{eq:one}) means that, for every
$\delta ' > \delta$, there is some $\varepsilon > 0$ such that
\begin{equation}
  \left\|x\right\| \le \varepsilon \Rightarrow N (x) \le
  \frac{\delta '}{2} \left\|x\right\|^{2}\ .
\end{equation}

It is an exercise in convex analysis, into which we shall not go, to
show that this implies that there is an $\eta > 0$ such that
\begin{equation}
  f\left\|x\right\| \le \eta
  \Rightarrow N^{\ast} (y) \le \frac{1}{2\delta '}
  \left\|y\right\|^{2}\ .
  \label{eq:two}
\end{equation}

\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white eagle and
a white horse on a snow field}
\end{figure}

Since $u_{1}$ is a smooth function, we will have
$\left\|hu_{1}\right\|_\infty \le \eta$
for $h$ small enough, and inequality (\ref{eq:two}) will hold,
yielding thereby:
\begin{equation}
  \psi (hu_{1}) \le \frac{h^{2}}{2}
  \frac{1}{\lambda} \left\|u_{1} \right\|_{2}^{2} + \frac{h^{2}}{2}
  \frac{1}{\delta '} \left\|u_{1}\right\|^{2}\ .
\end{equation}

If we choose $\delta '$ close enough to $\delta$, the quantity
$\left(\frac{1}{\lambda} + \frac{1}{\delta '}\right)$
will be negative, and we end up with
\begin{equation}
  \psi (hu_{1}) < 0\ \ \ \ \ {\rm for}\ \ h\ne 0\ \ {\rm small}\ .
\end{equation}

On the other hand, we check directly that $\psi (0) = 0$. This shows
that 0 cannot be a minimizer of $\psi$, not even a local one.
So $\overline{u} \ne 0$ and
$\overline{u} \ne \Lambda_{o}^{-1} (0) = 0$. \qed
\end{proof}
%
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty},b_{\infty}\right)$-subquadratic at infinity. Let
$\xi_{1},\allowbreak\dots,\allowbreak\xi_{N}$  be the
equilibria, that is, the solutions of $H' (\xi ) = 0$.
Denote by $\omega_{k}$
the smallest eigenvalue of $H'' \left(\xi_{k}\right)$, and set:
\begin{equation}
  \omega : = {\rm Min\,} \left\{\omega_{1},\dots,\omega_{k}\right\}\ .
\end{equation}
If:
\begin{equation}
  \frac{T}{2\pi} b_{\infty} <
  - E \left[- \frac{T}{2\pi}a_{\infty}\right] <
  \frac{T}{2\pi}\omega
  \label{eq:three}
\end{equation}
then minimization of $\psi$ yields a non-constant $T$-periodic solution
$\overline{x}$.
\end{corollary}
%

We recall once more that by the integer part $E [\alpha ]$ of
$\alpha \in \bbbr$, we mean the $a\in \bbbz$
such that $a< \alpha \le a+1$. For instance,
if we take $a_{\infty} = 0$, Corollary 2 tells
us that $\overline{x}$ exists and is
non-constant provided that:

\begin{equation}
  \frac{T}{2\pi} b_{\infty} < 1 < \frac{T}{2\pi}
\end{equation}
or
\begin{equation}
  T\in \left(\frac{2\pi}{\omega},\frac{2\pi}{b_{\infty}}\right)\ .
  \label{eq:four}
\end{equation}

%
\begin{proof}
The spectrum of $\Lambda$ is $\frac{2\pi}{T} \bbbz +a_{\infty}$. The
largest negative eigenvalue $\lambda$ is given by
$\frac{2\pi}{T}k_{o} +a_{\infty}$,
where
\begin{equation}
  \frac{2\pi}{T}k_{o} + a_{\infty} < 0
  \le \frac{2\pi}{T} (k_{o} +1) + a_{\infty}\ .
\end{equation}
Hence:
\begin{equation}
  k_{o} = E \left[- \frac{T}{2\pi} a_{\infty}\right] \ .
\end{equation}

The condition $\gamma < -\lambda < \delta$ now becomes:
\begin{equation}
  b_{\infty} - a_{\infty} <
  - \frac{2\pi}{T} k_{o} -a_{\infty} < \omega -a_{\infty}
\end{equation}
which is precisely condition (\ref{eq:three}).\qed
\end{proof}
%

\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n} \setminus \{ 0\}$ and
that $H'' (x)$ is non-de\-gen\-er\-ate for any $x\ne 0$. Then any local
minimizer $\widetilde{x}$ of $\psi$ has minimal period $T$.
\end{lemma}
%
\begin{proof}
We know that $\widetilde{x}$, or
$\widetilde{x} + \xi$ for some constant $\xi
\in \bbbr^{2n}$, is a $T$-periodic solution of the Hamiltonian system:
\begin{equation}
  \dot{x} = JH' (x)\ .
\end{equation}

There is no loss of generality in taking $\xi = 0$. So
$\psi (x) \ge \psi (\widetilde{x} )$
for all $\widetilde{x}$ in some neighbourhood of $x$ in
$W^{1,2} \left(\bbbr / T\bbbz ; \bbbr^{2n}\right)$.

But this index is precisely the index
$i_{T} (\widetilde{x} )$ of the $T$-periodic
solution $\widetilde{x}$ over the interval
$(0,T)$, as defined in Sect.~2.6. So
\begin{equation}
  i_{T} (\widetilde{x} ) = 0\ .
  \label{eq:five}
\end{equation}

Now if $\widetilde{x}$ has a lower period, $T/k$ say,
we would have, by Corollary 31:
\begin{equation}
  i_{T} (\widetilde{x} ) =
  i_{kT/k}(\widetilde{x} ) \ge
  ki_{T/k} (\widetilde{x} ) + k-1 \ge k-1 \ge 1\ .
\end{equation}

This would contradict (\ref{eq:five}), and thus cannot happen.\qed
\end{proof}
%
\paragraph{Notes and Comments.}
The results in this section are a
refined version of \cite{smit:wat};
the minimality result of Proposition
14 was the first of its kind.

To understand the nontriviality conditions, such as the one in formula
(\ref{eq:four}), one may think of a one-parameter family
$x_{T}$, $T\in \left(2\pi\omega^{-1}, 2\pi b_{\infty}^{-1}\right)$
of periodic solutions, $x_{T} (0) = x_{T} (T)$,
with $x_{T}$ going away to infinity when $T\to 2\pi \omega^{-1}$,
which is the period of the linearized system at 0.

\begin{table}
\caption{This is the example table taken out of {\it The
\TeX{}book,} p.\,246}
\begin{center}
\begin{tabular}{r@{\quad}rl}
\hline
\multicolumn{1}{l}{\rule{0pt}{12pt}
                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
\hline\rule{0pt}{12pt}
8000 B.C.  &     5,000,000& \\
  50 A.D.  &   200,000,000& \\
1650 A.D.  &   500,000,000& \\
1945 A.D.  & 2,300,000,000& \\
1980 A.D.  & 4,400,000,000& \\[2pt]
\hline
\end{tabular}
\end{center}
\end{table}
%
\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
Assume $H(t,x)$ is
$(0,\varepsilon )$-subquadratic at
infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
\begin{equation}
  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
\end{equation}
\begin{equation}
  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
\end{equation}
\begin{equation}
  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
\end{equation}
\begin{equation}
  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
\end{equation}

Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
$kT$-periodic solutions of the system
\begin{equation}
  \dot{x} = JH' (t,x)
\end{equation}
such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
\begin{equation}
  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
\end{equation}
\qed
\end{theorem}
%
\begin{example} [{{\rm External forcing}}]
Consider the system:
\begin{equation}
  \dot{x} = JH' (x) + f(t)
\end{equation}
where the Hamiltonian $H$ is
$\left(0,b_{\infty}\right)$-subquadratic, and the
forcing term is a distribution on the circle:
\begin{equation}
  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
\end{equation}
where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
\begin{equation}
  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
\end{equation}
where $\delta_{k}$ is the Dirac mass at $t= k$ and
$\xi \in \bbbr^{2n}$ is a
constant, fits the prescription. This means that the system
$\dot{x} = JH' (x)$ is being excited by a
series of identical shocks at interval $T$.
\end{example}
%
\begin{definition}
Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
operators in $\bbbr^{2n}$, depending continuously on
$t\in [0,T]$, such that
$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.

A Borelian function
$H: [0,T]\times \bbbr^{2n} \to \bbbr$
is called
$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
if there exists a function $N(t,x)$ such that:
\begin{equation}
  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
\end{equation}
\begin{equation}
  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
  {\rm is\ convex\ with\  respect\  to}\ \ x
\end{equation}
\begin{equation}
  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
\end{equation}
\begin{equation}
  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
\end{equation}

If $A_{\infty} (t) = a_{\infty} I$ and
$B_{\infty} (t) = b_{\infty} I$, with
$a_{\infty} \le b_{\infty} \in \bbbr$,
we shall say that $H$ is
$\left(a_{\infty},b_{\infty}\right)$-subquadratic
at infinity. As an example, the function
$\left\|x\right\|^{\alpha}$, with
$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
for every $\varepsilon > 0$. Similarly, the Hamiltonian
\begin{equation}
H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
\end{equation}
is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
Note that, if $k<0$, it is not convex.
\end{definition}
%

\paragraph{Notes and Comments.}
The first results on subharmonics were
obtained by Rabinowitz in \cite{fo:kes:nic:tue}, who showed the existence of
infinitely many subharmonics both in the subquadratic and superquadratic
case, with suitable growth conditions on $H'$. Again the duality
approach enabled Clarke and Ekeland in \cite{may:ehr:stein} to treat the
same problem in the convex-subquadratic case, with growth conditions on
$H$ only.

Recently, Michalek and Tarantello (see \cite{fost:kes} and \cite{czaj:fitz})
have obtained lower bound on the number of subharmonics of period $kT$,
based on symmetry considerations and on pinching estimates, as in
Sect.~5.2 of this article.

%
% ---- Bibliography ----
%
\begin{thebibliography}{6}
%

\bibitem {smit:wat}
Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}

\bibitem {may:ehr:stein}
May, P., Ehrlich, H.-C., Steinke, T.: ZIB structure prediction pipeline:
composing a complex biological workflow through web services.
In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
LNCS, vol. 4128, pp. 1148?1158. Springer, Heidelberg (2006).
\url{doi:10.1007/11823285_121}

\bibitem {fost:kes}
Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing Infrastructure.
Morgan Kaufmann, San Francisco (1999)

\bibitem {czaj:fitz}
Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
for distributed resource sharing. In: 10th IEEE International Symposium
on High Performance Distributed Computing, pp. 181?184. IEEE Press, New York (2001).
\url{doi: 10.1109/HPDC.2001.945188}

\bibitem {fo:kes:nic:tue}
Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The physiology of the grid: an open grid services architecture for distributed systems integration. Technical report, Global Grid
Forum (2002)

\bibitem {onlyurl}
National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}
\end{document}

### 2018-05-11 discrete_search.hpp
code: debug qp failures

@@ -172,7 +172,7 @@ private:
       return false;
     }
 
-    // check of occupied by another robot
+    // check if occupied by another robot
     for (const auto& otherRobot : m_otherRobots) {
       double distSq = pow(otherRobot.first - coord.first, 2) + pow(otherRobot.second - coord.second, 2);
       if (distSq < pow(2 * m_robotRadius, 2)) {

### 2018-05-11 main.cpp

@@ -80,6 +80,7 @@ int main(int argc, char** argv) {
   const double cell_size = jsn["cell_size"];
   const double v_max = jsn["v_max"];
   const double a_max = jsn["a_max"];
+  const double lambda_hyperplanes = jsn["lambda_hyperplanes"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
 
@@ -245,6 +246,10 @@ int main(int argc, char** argv) {
     accelerations[i] = trajectories[i].neval(0, 2);
     cout << "init acc: " << accelerations[i]<< endl;
   }
+
+  // add some pertubation at the beginning for first robot
+  // positions[0][0] += 0.2;
+  // positions[0][1] -= 0.4;
 
   for(int i=0; i<original_trajectories.size(); i++) {
     for(double t=0; t<=total_t; t+=printdt) {
@@ -450,22 +455,23 @@ int main(int argc, char** argv) {
         if (goal.x == -1) {
           std::cerr << "Couldn't find unoccupied space on original trajectory!" << ct << std::endl;
           // throw std::runtime_error("Couldn't find unoccupied space on original trajectory!");
-        }
-        std::cout << "discrete horizon: " << discrete_horizon << std::endl;
+        } else {
+          std::cout << "discrete horizon: " << discrete_horizon << std::endl;
 
-        OG::index startIdx = og.get_index(positions[i][0], positions[i][1]);
-        discreteSearch::State start(startIdx.i, startIdx.j, OG::direction::NONE);
+          OG::index startIdx = og.get_index(positions[i][0], positions[i][1]);
+          discreteSearch::State start(startIdx.i, startIdx.j, OG::direction::NONE);
 
-        discreteSearch::Environment env(og, otherRobots, robot_radius, goal);
+          // otherRobots.clear();
+          discreteSearch::Environment env(og, otherRobots, robot_radius, goal);
 
-        libSearch::AStar<discreteSearch::State, discreteSearch::Action, int, discreteSearch::Environment> astar(env);
-        libSearch::PlanResult<discreteSearch::State, discreteSearch::Action, int> solution;
+          libSearch::AStar<discreteSearch::State, discreteSearch::Action, int, discreteSearch::Environment> astar(env);
+          libSearch::PlanResult<discreteSearch::State, discreteSearch::Action, int> solution;
 
-        t_start_a_star = Time::now();
-        bool success = astar.search(start, solution);
-        t_end_a_star = Time::now();
+          t_start_a_star = Time::now();
+          bool success = astar.search(start, solution);
[…]

### 2018-05-11 qp_optimize.h

@@ -74,6 +74,29 @@ public:
     }
   }
 
+  // Maximize distance to the given hyperplane
+  // d^2 - 2 d n1 x1 - 2 d n2 x2 + n1^2 x1^2 + 2 n1 n2 x1 x2 + n2^2 x2^2
+  void maxHyperplaneDist(
+    size_t piece,
+    double lambda,
+    const Vector& normal,
+    double dist)
+  {
+    for (size_t i = 0; i < 8; ++i) {
+      size_t idx_x = column(piece, 0) + i;
+      size_t idx_y = column(piece, 1) + i;
+     /* m_H(idx_x, idx_x) += -2 * normal[0] * normal[0] * lambda;
+      m_H(idx_y, idx_y) += -2 * normal[1] * normal[1] * lambda;
+      m_H(idx_x, idx_y) += -2 * normal[0] * normal[1] * lambda;
+      m_H(idx_y, idx_x) += -2 * normal[0] * normal[1] * lambda;
+      m_g(idx_x) += 2 * dist * normal[0] * lambda;
+      m_g(idx_y) += 2 * dist * normal[1] * lambda;
+    */
+      m_g(idx_x) += normal[0] * lambda;
+      m_g(idx_y) += normal[1] * lambda;
+    }
+  }
+
   const Matrix& H() const
   {
     return m_H;

### 2018-05-11 rvo2_main.cpp

@@ -232,7 +232,7 @@ int main(int argc, char** argv) {
       bool original_traj_occupied = og.occupied(original_trajectories[i], robot_radius, ct, min(ct+hor, total_times[i]));
 
       bool discretePath = false;
-      if (original_traj_occupied) {
+      if (false && original_traj_occupied) {
         // attempt to follow discrete path
 
         std::vector< std::pair<double, double> > otherRobots;

### 2018-05-11 svm_seperator.cpp

@@ -42,7 +42,15 @@ vector<hyperplane> SvmSeperator::_2_4_seperate() {
 
     auto& hp = result.back();
     for (auto& pt : obs.pts) {
-      if (pt.dot(hp.normal) < hp.distance - 1e-3) {
+      if (pt.dot(hp.normal) < hp.distance - 1e-6) {
+        std::stringstream sstr;
+        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        // throw runtime_error(sstr.str());
+        std::cerr << sstr.str() << std::endl;
+      }
+    }
+    for (auto& pt : pts) {
+      if (pt.dot(hp.normal) > hp.distance + 1e-6) {
         std::stringstream sstr;
         sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
         // throw runtime_error(sstr.str());
@@ -80,7 +88,16 @@ vector<hyperplane> SvmSeperator::_8_4_seperate() {
 
     auto& hp = result.back();
     for (auto& pt : obs.pts) {
-      if (pt.dot(hp.normal) < hp.distance - 1e-3) {
+      if (pt.dot(hp.normal) < hp.distance - 1e-6) {
+        std::stringstream sstr;
+        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        // throw runtime_error(sstr.str());
+        std::cerr << sstr.str() << std::endl;
+      }
+    }
+
+    for (auto& pt : pts) {
+      if (pt.dot(hp.normal) > hp.distance + 1e-6) {
         std::stringstream sstr;
         sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
         // throw runtime_error(sstr.str());

### 2018-05-11 vis/stats.py

@@ -10,7 +10,7 @@ if __name__ == "__main__":
   parser.add_argument("--robot", default='all', help="robot number for details for one robot, or all for overview of all robots")
   args = parser.parse_args()
 
-  colors = ['b', 'g', 'r', 'c', 'm', 'y', 'k']
+  colors = ['b', 'g', 'r', 'c', 'm', 'y', 'k'] * 10
   entries = ["total", "Astar", "SVM", "QP"]
 
   csvfile = args.csvfile

### 2018-05-11 vis/vis.py

@@ -64,7 +64,8 @@ def genvoroxy(voronoi):
     a = voronoi[0]
     b = voronoi[1]
     c = voronoi[2]
-    xc = np.arange(-5,5,0.01).tolist()
+    #xc = np.arange(-5,5,0.01).tolist()
+    xc = [-5,5]
     yc = []
     for xx in xc:
       if b != 0.0:
@@ -72,6 +73,16 @@ def genvoroxy(voronoi):
       else:
         yc.append(0.0)
     return (xc,yc)
+
+def genvoronormal(voronoi):
+    a = voronoi[0]
+    b = voronoi[1]
+    c = voronoi[2]
+    xstart = a*c
+    ystart = b*c
+    xend = a*(c+0.1)
+    yend = b*(c+0.1)
+    return ([xstart,xend], [ystart,yend])
 
 def init():
     global trajectories
@@ -85,26 +96,28 @@ def init():
     if frameId != 0:
       return to_animate
 
-    x = []
-    y = []
-    for atraj in trajectories:
-        atraj.set_data([],[])
-        x.append([])
-        y.append([])
+    x = dict()
+    y = dict()
+    for i in robots:
+        trajectories[i].set_data([],[])
+        x[i] = []
+        y[i] = []
     time_text.set_text('')
     if args.voronoi and "voronois" in jsn:
-        for i in range(jsn["number_of_robots"]):
+        for i in robots:
             j = 0
             for v in jsn["voronois"][0][i]:
                 (xx,yy) = genvoroxy(v)
                 voronois[i][j].set_data(xx,yy)
+                (xx,yy) = genvoronormal(v)
+                voronoinormals[i][j].set_data(xx,yy)
                 j+=1
     if "planned_trajs" in jsn:
-      for i in range(jsn["number_of_robots"]):
+      for i in robots:
           plans[i].set_data(jsn["planned_trajs"][0][i]["x"], jsn["planned_trajs"][0][i]["y"])
           originals[i].set_data(jsn["originals"][i]["x"], jsn["originals"][i]["y"])
     if args.controlpoints:
-      for i in range(jsn["number_of_robots"]):
+      for i in robots:
           cpts = controlpoints[i]
           pts = jsn["controlpoints"][0][i]
           k = 0
@@ -129,28 +142,30 @@ def animate(frame):
     global x
     global y
 
-    for i, atraj in enumerate(trajectories):
+    for i in robots:
[…]

### 2018-05-11 paper/paper.tex
updated paper

@@
 
-\usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{caption}
+%\usepackage{subcaption}
+%\captionsetup{compatibility=false}
 
-\captionsetup{compatibility=false}
+% Springer does not support subcaption/caption => use subfig instead and avoid loading the caption package
+\usepackage[caption=false]{subfig}
 
+\usepackage{siunitx}
 \usepackage{amsmath}
@@
 \usepackage{adjustbox}
+
+\usepackage{ upgreek }
 
@@
 \tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
-\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
-\tikzstyle{decision} = [diamond, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=green!30]
+\tikzstyle{process} = [rectangle, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=white!30]
+\tikzstyle{decision} = [diamond, minimum width=1cm, minimum height=1cm, text centered, draw=black, fill=cyan!30]
 \tikzstyle{arrow} = [thick,->,>=stealth]
@@
 \newcommand{\vo}{\mathbf{o}}
+\newcommand{\vchi}{\mathbf{\chi}}
+\newcommand{\vlbA}{\mathbf{lbA}}
+\newcommand{\vubA}{\mathbf{ubA}}
+\newcommand{\vlb}{\mathbf{lb}}
+\newcommand{\vub}{\mathbf{ub}}
 
@@
 \newcommand{\cS}{\mathcal{S}}
+\newcommand{\cC}{\mathcal{C}}
+\newcommand{\cE}{\mathcal{E}}
+\newcommand{\cO}{\mathcal{O}}
 
@@
 %%%%%%%%%%%%%
+\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}
 
@@
 
-We propose robust motion execution as a framework that can take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
+We propose robust motion execution as a framework that take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
+Consider the example in Fig.~\ref{fig:swap2:initial}, where two robots are tasked with swapping their position.
+The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the right location.
+Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories (see Fig.~\ref{fig:swap2:final}).
 Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.
+
+\begin{figure}
+\centering
+\subfloat[Initial configuration.]{
+\includegraphics[width=0.48\textwidth]{images/swap2_initial.pdf}
+\label{fig:swap2:initial}
+}
+\hfill
+\subfloat[Final configuration and executed trajectories.]{
+\includegraphics[width=0.48\textwidth]{images/swap2_final.pdf}
+\label{fig:swap2:final}
+}
+%\begin{subfigure}[t]{0.48\textwidth}
+%\centering
+%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
+%\caption{Initial configuration.}
+%\label{fig:swap2:initial}
+%\end{subfigure} \hfill
+%\begin{subfigure}[t]{0.48\textwidth}
+%\centering
+%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
+%\caption{Final configuration and executed trajectories.}
+%\label{fig:swap2:final}
+%\end{subfigure}
+\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
+The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
+Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
+}
+\label{fig:swap2}
+\end{figure}
 
@@
 Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
-At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning.
-The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.\footnote{test footnote}
+At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
+The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.
 
-% todo: perhaps write some more about what experiments we did, after we have the material
+\todo{perhaps write some more about what experiments we did, after we have the material}
 
-\section{Problem Formulation}
+\section{Problem Formulation} \label{problemFormulation}
 % assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
@@
 % issues: no live-lock guarantee
-We solve our problem completely in a distributed fashion.
-No central authority coordinates the robots and robots themselves can't communicate with their peers, hence they have no information about the plans of other robots.
-In every time step $K$, seperated by replanning period $\delta t$, each robot $i$ solves the following problem:
+
+We consider a group of $m$ robots and each robot $i$ is given the following:
 \begin{align*}
-    \text{Given,}\ \ \ \ \ &\\
-    \vo^i(t')&:\text{ original trajectory of robot $i$},\\
-    ct&:\text{ current global time},\\
-    \delta t&:\text{ replanning period},\\
-    \tau&: \text{time horizon},\\ 
-    c&:\text{ maximum continuity between pieces},\\
-    \Theta&:\text{ occupancy grid of the environment},\\
-    \{\vp_i\}&:\text{ set of positions of all robots},\\
-    \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
-    &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
-    \text{find a new}&\text{ trajectory $\vf_K^i(t)$ such that},\\
-    \vf_K^i(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
-    \frac{d^j\vf_K^i(t)}{dt^j}(0) &= \frac{d^j\vf_{K-1}^i(t)}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
-    \vf_K^i(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
-    \vf_K^i(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
-    \left\|\frac{d^j \vf^i(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
+    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
+    %ct&:\text{ current global time},\\
+    %\delta t&:\text{ replanning period},\\
+    %\tau&: \text{time horizon},\\ 
+    c&:\text{ derivative up to which smoothness is required},\\
+    %\cO&:\text{ free space representation of the environment},\\
+    %\{\vp_i\}&:\text{ set of positions of all robots},\\
+    R_i(\vp)&:\text{ physical extend of robot $i$ at position $\vp$}, and\\
+    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
+    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
 \end{align*}
 
-Robot $i$'s trajectory $f^i(t)$ is $f_K^i(t)$ in $K^{th}$ time step. It follows the trajectory for $\delta t$ seconds, and replans to calculate $f_{K+1}^i(t)$ and replaces $f^i(t)$ with it.
+At time $t$ each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
+However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
+%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
+Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
+\begin{align*}
+    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
+    \text{subject to }& \\
+    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
+    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
+    &\vf_i(t)\text{ is collision free, and}\\ 
+    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
+    \text{where } & t\in [0,T_i].
+\end{align*}
+
+We approximately solve this problem using a dynamic receding horizon approach.
+At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position.
+We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.
+
+%\todo{add paragraph about how we actually (approximately solve this problem)}
+
+% \begin{align*}
+%     \text{Given,}\ \ \ \ \ &\\
+%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
+%     ct&:\text{ current global time},\\
+%     \delta t&:\text{ replanning period},\\
+%     \tau&: \text{time horizon},\\ 
+%     c&:\text{ maximum continuity between pieces},\\
+%     \cO&:\text{ free space representation of the environment},\\
+%     \{\vp_i\}&:\text{ set of positions of all robots},\\
+%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
+%     &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
+%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
+%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
+%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
+%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
+%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
+%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
+% \end{align*}
 
@@
 
-\subsection{Buffered Voronoi Cells}
+\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
 Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
@@
 The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
-\begin{align*}
-    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\\
-    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
-\end{align*}
+\begin{align}
+    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
+    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
+\end{align}
 
@@
 \end{align}
+
 Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
 \begin{align}
-    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j. \label{voronoi_intersection_definition}
+    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
 \end{align}
-This definition suggests a natural algorithm to compute the buffered voronoi cell of any robot $i$ in terms of the hyperplanes $H_i^j$:
-\begin{algorithmic}[1]
-    \Function{Voronoi}{[$p_i$]: robot positions, $i$: robot that we want to calculate voronoi cell of, $r_i$: radius of robot $i$}
-        \State $H = \{\}$
-        \ForAll{$j\neq i$}
-            \State $H_i^j = (\alpha_i^j, \beta_i^j)$
-            \State $H = H\cup H_i^j$
-        \EndFor
-        \State \Return $H$
-    \EndFunction
-\end{algorithmic}
-This is an $O(m)$ operation, $m$ being the number of robots.
 
-\subsection{B\'ezier Curves}
-A degree $d$ b\'ezier curve $\vg(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
+Thus, we can compute the buffered voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.
+
+\subsection{B\'ezier Curves} \label{bezierCurves}
+A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
 \begin{align}
-    \vg(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
+    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
 \end{align}
@@
 It does not interpolate the control points, but uses them to guide the curve.
-A b\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}.
+A B\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}.
+This is called the \emph{convex hull property of B\'ezier curves}.
 We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.
 
-We use polynomial splines as trajectories where each piece is a b\'ezier curve.
-Given a trajectory $\vf^i(t)$ for robot $i$ with $l$ pieces, $T^i_j$ denotes the duration of $j^{th}$ piece, $\vf^i_j(t; T^i_j)$ denotes the $j^{th}$ piece of the trajectory, $\vP^i_{j,k}$ denotes the $k^{th}$ control point of $j^{th}$ piece, and $P^i_{j,k,u}$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $k \in \{0,1,...,d\}$, $u \in \{1,2,...,n\}$.
+We use splines as trajectories where each piece is a B\'ezier curve.
+Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at time step $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of $j^{th}$ piece, $\vf^{K}_{i,j}(t; T^{K}_{i,j})$ denotes the $j^{th}$ piece of the trajectory, $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of $j^{th}$ piece, and $P^{K}_{i,j,\rho}[u]$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $\rho \in \{0,1,...,d\}$, and $u \in \{1,2,...,n\}$.
 
-\subsection{Support Vector Machine}
-Support vector machine is a supervised learning method that is used to classify data into several classes.
-In binary classification problems, given linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label, SVM problem tries to find a hyperplane with normal $\vw$ and distance along the normal $b$ that separates two classes.
-SVM problem for binary classification with separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
+\subsection{Support Vector Machine}\label{svmSection}
+A support vector machine is a supervised learning method that is used to classify data into several classes.
+In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
+The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
+The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
 \begin{align*}
@@
 We use SVMs to define collision free convex subspaces that are obstacle-free.
-\subsection{Trajectory Optimization}
-We present our replanning problem as a quadratic optimization problem where the control points of the trajectory are the variables.
-The overall structure of quadratic optimization problems is as follows \cite{qpOASES}:
+\subsection{Trajectory Optimization} \label{trajectoryOptimization}
+A part of our replanning approach utilizes quadratic programming for trajectory optimization using control points of curves as decision variables.
+The overall structure of our quadratic optimization problem is as follows:
 \begin{align*}
-    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^Tg\\
-    \text{subject to}\ \ \ & lbA \leq A\vx \leq ubA\\
-    &lb \leq \vx \leq ub
+    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
+    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA
+    % &\vlb \leq \vx \leq \vub
 \end{align*}
+%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.
 
-Each constraint on the problem appends a set of rows to the matrices $A$, $lbA$, and $ubA$.
-There are 4 types of constraints we impose: starting point constraints, end point constraints, continuity constraints and hyperplane constraints.
-\subsubsection{Initial Point Constraints}
-For each of the curves in the trajectory, we can impose initial point constraints.
-An initial point constraint requires curve to have a specific value in any order of its derivatives in the beginning.
-$S_j(D, T)$ is the matrix we append to $A$ in order to evaluate curve $j$ at its starting point, $D$ being the degree of derivation, $T$ being the duration of the curve.
+A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
+Notice that all constraints should be linear in the decision variables.
 
-The value of the curve in the beginning is simply a linear combination of the control points.
-The rows of $S_j$ are the coefficients of control points in this linear combination, each of which corresponding to a different dimension.
-We append the desired vector $\vq$ for the constraint to both $lbA$ and $ubA$ matrices.
-Note that by adding the same vector to both upper and lower bound matrices, we impose an equality constraint.
-\subsubsection{End Point Constraints}
-This is essentially same with starting point constraints. Only difference is that instead of evaluating the curve at $t=0$, we evaluate it at $t=T$.
+There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
 
-$E_j(D,T)$ denotes the matrix we append to $A$ in order to evaluate the curve $j$ at its end point, $D$ being the degree of derivation, $T$ being the duration of the curve.
-We again append desired value vector $\vq$ to both $lbA$ and $ubA$.
-\subsubsection{Continuity Constraints}
-For each consecutive curves $j$ and $j+1$ in the trajectory, we can impose a continuity constraint of any degree $D$.
-We basically take the difference of the $D^{th}$ derivative of curve $j$ evaluated at time $t=T_j$ and the $D^{th}$ derivative of curve $j+1$ evaluated at time $t=0$ and require it to be $\vzero$.
-This difference is again a linear combination of the control points.
+\begin{description}
+\item [Initial Point Constraints]
+An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
+This requires $n$ linear constraints on the control points, $n$ being the dimension we are working in.
 
-$C_j(D,T_j,T_{j+1})$ denotes the matrix we append to A in order to calculate the difference between curves $j$ and $j+1$, $D$ being the degree of derivation, $T_j$ being the duration of curve $j$ and $T_{j+1}$ being the duration of curve $j+1$.
-We append $\vzero$ to both $lbA$ and $ubA$.
-\subsubsection{Hyperspace Constraints}
-For each of the control points, we can add a hyperplane constraint that requires the point not to be in the positive side of the hyperplane.
-Given hyperplane with normal $\vn$ and distance along the normal $d$, not-positive side of the hyperplane is simply the set $J$ defined as
-\begin{align*}
-    J = \left\{\vp: \vn \cdot \vp - d \leq 0\right\}
-\end{align*}
+\item[Continuity Constraints]
+A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ in the end to be equal to the curve $j+1$ in the beginning in any order of derivation.
+We take the vector difference of those values and require it to be equal to $\vzero$.
+This requires $n$ linear constraints on the control points.
 
-The constraint is again a linear combination of control points.
-$H_{j,k}(\vn)$ denotes the row we append to $A$ in order to impose a hyperplane constraint on the $k^{th}$ control point of $j^{th}$ curve, $\vn$ being the normal of the hyperplane.
-We add $d$ to $ubA$ and $-\infty$ to $lbA$.
-\\
+\item[Hyperspace Constraints]
+A hyperspace constraint requires a point of a curve to be on a specific side of a hyperplane.
+Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires $1$ linear constraint on the control points.
+\end{description}
 
-Notice that $S_j, E_j, C_j$ and $H_{j,k}$ matrices defined above also depend on the problem dimension $n$ and number of control points per curve $d+1$.
-To not to complicate the notation, we omitted these details in the symbols.
-In our treatment, we do not change the number of control points per curve and the dimension of the problem between replanning iterations.
-Therefore, omitting these details does not present any problems in terms of the completeness of our explanation.
-In any instance, dimension and points per curve will be inferred from the context.
 \section{Approach}
@@
 \subsection{Approach Overview}
-Our approach has three big components: \emph{discrete planning} that is used in case using only optimization may present problems, \emph{trajectory optimization} to optimize trajectory while avoiding obstacles and other robots, and \emph{dynamic rescaling} to comform to the dynamic limits of the robot.
+Our approach has three major components: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot.
 
-In each iteration, pipeline that is summarized in figure \ref{fig:flowchart} gets executed. Period of each iteration is $\delta_t$, and all pipeline gets executed every $\delta_t$.
+In each iteration $K$, each robot executes the flow chart outlined in Fig.
+~\ref{fig:flowchart}.
+Replanning is done at a fixed period of $\delta t$ and results in a trajectory $f^K_i(t)$ that is defined for $t\in [0,\tau]$, safe to execute up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.
 
-In the beginning of the each iteration, we check for some conditions defined in the following sections to see if we need discrete replanning.
-If the answer is yes, we do a discrete search that results in a discrete path that is obstacle and robot free.
-Then, we transform this discrete plan to b\'ezier control points and use those points as the initial data for trajectory optimization.
-If the answer is no, we skip discrete search, and directly use the control points of the previous plan as the initial data.
+In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
+If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
+We use this discrete path as an initial guess in trajectory optimization.
+If discrete planning is not required, we skip discrete search, and directly use the control points of the previous plan as the initial variables.
 
-Depending on whether we did discrete search or not, we build objective matrix $H$ for trajectory optimization in a slightly different way.
+Depending on whether discrete search is done or not, we construct the objective matrix $H$ and objective vector $g$ for trajectory optimization in a slightly different way.
+Exact difference in construction processes is explained in ~\ref{continuousOptimization}.
 
-At this point, algorithm has the same flow independent of the fact that we did discrete search or not.
-We compute $A$ matrix that represents continuity, hyperspace, initial point and end point constraints.
+Than, we compute the $A$ matrix that represents continuity, hyperspace, and initial point constraints.
 Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles.
-When the optimization is done, we check whether the dynamic limits are violated.
-While the answer is yes, we increase durations of pieces and do the optimization again until dynamic limits are not violated.
-In the end, we have a trajectory $f^i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory and is a good starting point for the next iteration.
+Since quadratic optimization requires constraints to be linear and dynamic limits can't be represented as linear constraints, we check dynamic limit violations not during trajectory optimization but in the temporal rescaling stage that runs after optimization.
+As long as dynamic limits are violated, we increase durations of pieces and do the optimization again until dynamic limits are not violated.
+In the end, we have a trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
 
@@
     \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
-    \node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};
+    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};
 
-    \coordinate[above=2cm of discrete.west, xshift=-0.2cm] (c1);
-    \coordinate[below=2cm of discrete.west, xshift=-0.2cm] (c2);
-    \coordinate[above=2cm of discretesearch.east, xshift = 0.2cm, yshift=-1cm] (c3);
-    \coordinate[below=2cm of discretesearch.east, xshift = 0.2cm, yshift = -1cm] (c4);
+    \coordinate[above=2cm of discrete.west, xshift=-0.2cm, yshift=0.2cm] (c1);
+    \coordinate[below=2cm of discrete.west, xshift=-0.2cm, yshift=-0.2cm] (c2);
+    \coordinate[above=2cm of discretesearch.east, xshift = 0.2cm, yshift=-0.8cm] (c3);
+    \coordinate[below=2cm of discretesearch.east, xshift = 0.2cm, yshift = -1.2cm] (c4);
 
-    \coordinate[above=2cm of discobjbuild.west, xshift=-0.2cm, yshift=-1cm] (c5);
-    \coordinate[below=2cm of discobjbuild.west, xshift=-0.2cm, yshift = -1cm] (c6);
+    \coordinate[above=2cm of discobjbuild.west, xshift=-0.2cm, yshift=-0.8cm] (c5);
+    \coordinate[below=2cm of discobjbuild.west, xshift=-0.2cm, yshift = -1.2cm] (c6);
     \coordinate[above=2cm of trajopt.east, xshift = 0.2cm] (c7);
-    \coordinate[below=2cm of trajopt.east, xshift = 0.2cm] (c8);
+    \coordinate[below=2cm of trajopt.east, xshift = 0.2cm, yshift=-0.4cm] (c8);
 
-    \coordinate[above=2cm of dynamiclimits.west, xshift=-0.2cm, ] (c9);
+    \coordinate[above=2cm of dynamiclimits.west, xshift=-0.2cm] (c9);
     \coordinate[below=2cm of dynamiclimits.west, xshift=-0.2cm, yshift = -1.5cm] (c10);
@@
     \draw [arrow] (trajopt) -- (dynamiclimits);
-    \draw [arrow] (dynamiclimits) -- node[anchor=south] {no} (end);
+    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {no} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {start next iteration} -|   (discrete);
     \draw [arrow] (dynamiclimits) -- node[anchor=east] {yes} (rescale);
@@
     \node[right = 0cm of c5, yshift=0.3cm] {Continuous optimization};
-    \node[right = 0cm of c9, yshift=0.3cm] {Dynamic rescaling};
+    \node[right = 0cm of c9, yshift=0.3cm] {Temporal rescaling};
 
@@
 
+%\todo{DISCUSS: planning/execution overlap?}
+
+\subsection{Discrete Planning} \label{discretePlanning}
+
+In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered voronoi cell $\cV_i(\psi)$.
+We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.
+
+We execute discrete planning if any of the following conditions is true:
+\begin{enumerate}
+    \item The original trajectory is not collision-free for the time horizon, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(\psi)) \cap \cO(\psi) \neq \emptyset$,
+    \item The first piece of the planned trajectory is outside robot $i$'s buffered voronoi cell, i.e., $\exists t\in [0, T^{K}_{i,1}] : \vf^{K}_{i,1}(t; T^{K}_{i,1}) \not\in \cV_i(\psi)$, or
+    \item The planned trajectory is not collision-free for the time horizon, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K}_i(t)) \cap \cO(\psi) \neq \emptyset$.
+\end{enumerate}
+The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles dynamic obstacles.
+
+Discrete planning uses a dynamic receding horizon approach.
+First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free with respect to both obstacles and other robots.
+Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
+If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage.
+Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
+In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
+Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path using a uniform velocity.
+However, to guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.
+
+An example is shown in Fig.~\ref{fig:swap2:discrete}. 
+Discrete planning is executed because the original trajectory (green dashed line) passes through an obstacle.
+The earliest time to avoid the obstacle $\tau'$ is found such that the green robot re-joins its original trajectory after the obstacle.
+A path that avoids both the static obstacle and the other (blue) robot is found (green dotted line) and has a total of six path segments.
+The first four ($l=4$) segments are used to place new guesses of B\'ezier control points (blue, green, red, and cyan circles).
+In this example, each curve has eight control points, although some of the points overlap.
+The duration for each B\'ezier curve $T^{K}_{i,j}$ is adjusted according to the path length; for example, the duration of the segment with the red control points ($T_{i,3}^K$) is approximately twice as long as the duration of the segment with the green control points ($T_{i,2}^K$).
+
+%\todo{need a statement that piece duration is at least delta t}
+
+%\todo{when is ct introduced now?}
+
+%WOLFGANG (text + pics)
+
 \begin{figure}
 \centering
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=.9\textwidth]{images/swap2_initial.pdf}
-\caption{Initial configuration.}
-\label{fig:swap2:initial}
-\end{subfigure} \hfill
-\begin{subfigure}[t]{0.45\textwidth}
-\centering
-\includegraphics[width=.9\textwidth]{images/swap2_final.pdf}
-\caption{Final configuration and executed trajectories.}
-\label{fig:swap2:final}
-\end{subfigure}
-\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
-The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
-Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
+\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
+\includegraphics[width=0.45\textwidth]{images/swap2_discrete.pdf}
+\label{fig:swap2:discrete}
 }
-\label{fig:swap2}
+\hfill
+\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
+\includegraphics[width=0.45\textwidth]{images/swap2_cont_red.pdf}
+\label{fig:swap2:cont}
+}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=1.0\textwidth]{images/swap2_discrete.pdf}
+% \caption{Discrete path around an obstacle and other robot back to the original trajectory.}
+% \label{fig:swap2:discrete}
+% \end{subfigure} \hfill
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=1.0\textwidth]{images/swap2_cont_red.pdf}
+% \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
+% \label{fig:swap2:cont}
+% \end{subfigure}
+\caption{
+Snapshot at $t=3.9$.
+}
+\label{fig:swap2_2}
 \end{figure}
 
-\subsection{Discrete Planning}
-
-WOLFGANG (text + pics)
+% \begin{figure}
+% \centering
+% \subfloat[Voronoi decomposition.]{
+% \includegraphics[width=0.48\textwidth]{images/swap2_voronoi.pdf}
+% \label{fig:swap2:voronoi}
+% }
+% % \begin{subfigure}[b]{0.48\textwidth}
+% % \centering
+% % \includegraphics[width=1.0\textwidth]{images/swap2_voronoi.pdf}
+% % \caption{Voronoi decomposition.}
+% % \label{fig:swap2:voronoi}
+% % \end{subfigure} \hfill
+% % \begin{subfigure}[b]{0.45\textwidth}
+% % \centering
+% % \includegraphics[scale=0.6]{images/swap2_cont_red.pdf}
+% % \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
+% % \label{fig:swap2:cont}
+% % \end{subfigure}
+% \caption{
+% %Snapshot at $t=3.9$.
+% }
+% \label{fig:swap2_3}
+% \end{figure}
 
@@
 
-\subsection{Continuous Optimization}
+\subsection{Continuous Optimization}\label{continuousOptimization}
+In this stage, a quadratic optimization problem is solved where variables are the control points of the pieces concatenated together.
+If discrete planning is not performed, initial variables are copied from the previous iteration, and durations are set uniformly to $\frac{min(\tau,T_i-\psi)}{l}$.
+If discrete planning is performed, initial variables and durations are calculated from the discrete path as explained in Section~\ref{discretePlanning}.
+The objective $\cC$ that we minimize is defined as
+\begin{align}
+    \cC = \sum_{e=1}^{\cE} \lambda_e\int_{0}^{T^K_i} \left\|\frac{d^e\vf^{K}_i(t)}{dt^e}\right\|^2dt + \sum_{j=1}^{l} \theta_j \left\|\vP^{K}_{i,j,d} - \vchi_{j}\right\|^2 \label{costFunction}
+\end{align}
+where $\vchi_j$ is the point we want piece $j$ to end at. Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
 
-BASKIN (math)
+The first term of $\cC$ is the combination of integrated squared derivatives with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
+The second term of $\cC$ penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
+In case discrete planning is performed, we require the end point of last piece to be in the final position of the discrete plan and do not constrain other pieces.
+If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
+This is an approximation we make for the cost function defined in Section~\ref{problemFormulation}.
+The construction of $H$ matrix defined in Section~\ref{trajectoryOptimization} for the first term is explained in \cite{crazyplanning-ieeetro}.
+The second term is a quadratic function of control points, hence it can be converted to an $H$ matrix and a $g$ vector as well.
 
-WOLFGANG (pics)
+For robot-to-robot collision avoidance, the buffered voronoi hyperplanes are computed according to equations \eqref{voronoiAlpha} and \eqref{voronoiBeta}.
+For each control point of the first piece, we add $m-1$ hyperspace constraints as
+\begin{align}
+    \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
+\end{align}
+
+These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
+As long as $T^{i,K}_1 \geq \delta t$ and all other robots stay inside their voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
+A sample buffered voronoi decomposition of the space is presented in Fig.~\ref{fig:swap2:voronoi}.
+
+Remember at current global time $\psi$, $\cO(\psi)$ represents the occupied space.
+For each piece $j$, we calculate a set of SVM hyperplanes where hyperplane $M_j^b$ separates the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$ using the method presented in Section~\ref{svmSection}.
+We shift these hyperplanes first towards to the obstacle than shift them back using the radius $r_i$ to account for the physical extend of the robot.
+We add hyperplane constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each $M_j^b$ where $b\in \{1,2,...O\}$, $O$ being the number of non-occupied cells.
+These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau$.
+Fig.~\ref{fig:swap2:cont} shows the effective set of SVM hyperspaces for a $4$ piece trajectory.
+
+After that we add continuity constraints that enforces continuity requirement between pieces.
+
+Lastly, we add initial point constraints that enforce 
+\begin{align*}
+\frac{d^j\vf^{K}_i}{dt^j}(0) &= \frac{d^j\vp_i}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
+\end{align*}
+
+All these constraints are linear as explained in Section~\ref{trajectoryOptimization}. Therefore, we indeed have a constructible quadratic optimization problem.
+
+For an instance of a problem in dimension $n$ where the trajectory has $l$ pieces of degree $d$, number of variables in the optimization is $l(d+1)n$.
+Therefore the dimensins of the matrix $H$ is $l(d+1)n\times l(d+1)n$ and the vector $\vg$ is $l(d+1)\times 1$.
+If there are $m$ robots in the environment, buffered voronoi decomposition imposes $(m-1)(d+1)$ linear constraints.
+If there number of obstacles in the environment is $\uptheta$, SVM seperations impose $\uptheta l (d+1)$ linear constraints.
+If maximum required continuity is $c$, continuity requirements impose $(c+1)nl$ linear constraints.
+Therefore the matrix $A$ has $(m-1)(d+1) + \uptheta l(d+1) + (c+1)nl$ rows in total.
+For example, in 2-dimensional space with $4$ robots where the trajectory has $4$ pieces of degree $7$, the environment is occupied with $10$ obstacles and $C^{2}$ continuity is required, the number of variables would be $64$, and the number of linear constraints would be $368$.
+
 % fig showing result from before (initial control points), hyperspaces (transparent, color-coded by piece), and resulting smooth trajectory (color-coded by piece).
 
-\subsection{Enforcing Dynamic Limits} % might be part of overview
-
-BASKIN (math)
+\subsection{Temporal Rescaling} % might be part of overview
+Since we use fixed durations for pieces and do not account for the dynamic limits of the robot during optimization, the resulting trajectory may violate dynamic limits of the robot.
+After trajectory optimization, we calculate the maximum magnitudes $\Gamma_j$ of $j^{th}$ derivatives of the curve, and check if for any $j$, $\Gamma_j > \gamma_j$, where $\gamma_j$ is the dynamic limit of the robot in $j^{th}$ derivation degree.
+If that is the case, we multiply durations $T^K_{i,j}$ of each piece by the same constant, and re-run the trajectory optimization with the same exact constraints using the previous result as the initial guess.
+If that is not the case, no temporal rescaling is needed and the trajectory is feasible.
 
@@
 \subsection{Theoretical Guarantees} %maybe
+\begin{enumerate}
+    \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
+The maximum phase shift between robots is $\delta t$.
+If the dynamic limit $\gamma_1$ for velocities is uniform between robots, we can account for the phase shift by shifting each voronoi hyperplane $H_i^j$ by $\gamma_i \delta t$.
+Notice that this is a pessimistic shift, that does not take robot $j$'s extend into account.
+We can do even better if the geometry of the robots are uniform.
+This update gives \emph{no robot collision guarantee} even there is phase shift during the execution.
+    \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
+    \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
+If we know the maximum velocity $\nu$ of the obstacles in the environment, we can avoid moving obstacles as well by shifting the SVM seperating hyperplanes by $\nu \delta t $.
+This update gives \emph{no obstacle collision guarantee} even the obstacles are moving.
+\end{enumerate}
 % see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
@@
 
-BASKIN
-
 \section{Evaluation}
 
-\cite{cvxgen}
-\cite{qpOASES}
-\cite{osqp}
+We implement our approach in C++.
+We use an occupancy grid as environment representation, because previous work has shown that such data structures can be updated in real-time on robots that are equipped with a LIDAR sensor or a RGB-D camera.
+In particular, OctoMap~\cite{octomap} is an octree-based 3D occupancy grid that can be run on UAVs at at least \SI{4}{Hz} update rate~\cite{replanning-eth}.
+OctoMaps are memory efficient, but update operations can show high execution time variance.
+For local replanning, occupancy grids using ringbuffers as datastructures have been shown to achieve near constant execution time~\cite{replanning-usenko}.
+Our implementation uses a simple pre-initialized 2D occupancy grid such that a physical robot implementation could leverage existing OctoMap or occupancy ringbuffer libraries easily.
+
+We use the CVXGEN-package~\cite{cvxgen} to generate small QPs to find separating hyperplanes between controlpoints and obstacles.
+As QP solvers we test with qpOASES~\cite{qpOASES} and OSQP~\cite{osqp}; both are open source and have been shown to work well in model predictive control scenarios.
 
@@
 % scalability: #curves, #obstacles, #robots (voronoi constraint), qp-solver
+% compare success rate with RVO2
+%    describe typical examples (inline with the introduction)
 
@@
 
-\subsection{Baskin}
-problem formulation, Preliminaries
-
-RVO2 baseline (see \url{http://gamma.cs.unc.edu/RVO2/documentation/2.0/using.html})
-
-\subsection{Wolfgang}
-%Bibliography
-%related work
-%intro
-
-proper occupancy grid (respecting the robots size during planning, not during occupancy grid construction).
+\todo{why are functions marked as vectors?}
 

### 2018-05-11 cvxgen/32pt4obspt/cvxgen/csolve.c
svm 32/4 seperator added

@@ -1,0 +1,180 @@
+/* Produced by CVXGEN, 2018-05-11 17:28:57 -0400.  */
+/* CVXGEN is Copyright (C) 2006-2017 Jacob Mattingley, jem@cvxgen.com. */
+/* The code in this file is Copyright (C) 2006-2017 Jacob Mattingley. */
+/* CVXGEN, or solvers produced by CVXGEN, cannot be used for commercial */
+/* applications without prior written permission from Jacob Mattingley. */
+
+/* Filename: csolve.c. */
+/* Description: mex-able file for running cvxgen solver. */
+#include "mex.h"
+#include "solver.h"
+Vars vars;
+Params params;
+Workspace work;
+Settings settings;
+void mexFunction(int nlhs, mxArray *plhs[], int nrhs, const mxArray *prhs[]) {
+  int i, j;
+  mxArray *xm, *cell, *xm_cell;
+  double *src;
+  double *dest;
+  double *dest_cell;
+  int valid_vars;
+  int steps;
+  int this_var_errors;
+  int warned_diags;
+  int prepare_for_c = 0;
+  int extra_solves;
+  const char *status_names[] = {"optval", "gap", "steps", "converged"};
+  mwSize dims1x1of1[1] = {1};
+  mwSize dims[1];
+  const char *var_names[] = {"w"};
+  const int num_var_names = 1;
+  /* Avoid compiler warnings of unused variables by using a dummy assignment. */
+  warned_diags = j = 0;
+  extra_solves = 0;
+  set_defaults();
+  /* Check we got the right number of arguments. */
+  if (nrhs == 0)
+    mexErrMsgTxt("Not enough arguments: You need to specify at least the parameters.\n");
+  if (nrhs > 1) {
+    /* Assume that the second argument is the settings. */
+    if (mxGetField(prhs[1], 0, "eps") != NULL)
+      settings.eps = *mxGetPr(mxGetField(prhs[1], 0, "eps"));
+    if (mxGetField(prhs[1], 0, "max_iters") != NULL)
+      settings.max_iters = *mxGetPr(mxGetField(prhs[1], 0, "max_iters"));
+    if (mxGetField(prhs[1], 0, "refine_steps") != NULL)
+      settings.refine_steps = *mxGetPr(mxGetField(prhs[1], 0, "refine_steps"));
[…]

### 2018-05-11 cvxgen/32pt4obspt/cvxgen/cvxsolve.m

@@ -1,0 +1,24 @@
+% Produced by CVXGEN, 2018-05-11 17:28:57 -0400.
+% CVXGEN is Copyright (C) 2006-2017 Jacob Mattingley, jem@cvxgen.com.
+% The code in this file is Copyright (C) 2006-2017 Jacob Mattingley.
+% CVXGEN, or solvers produced by CVXGEN, cannot be used for commercial
+% applications without prior written permission from Jacob Mattingley.
+
+% Filename: cvxsolve.m.
+% Description: Solution file, via cvx, for use with sample.m.
+function [vars, status] = cvxsolve(params, settings)
+A = params.A;
+H = params.H;
+cvx_begin
+  % Caution: automatically generated by cvxgen. May be incorrect.
+  variable w(3, 1);
+
+  minimize(quad_form(w, H));
+  subject to
+    A*w <= -1;
+cvx_end
+vars.w = w;
+status.cvx_status = cvx_status;
+% Provide a drop-in replacement for csolve.
+status.optval = cvx_optval;
+status.converged = strcmp(cvx_status, 'Solved');

### 2018-05-11 cvxgen/32pt4obspt/cvxgen/matrix_support.cpp

@@ -1,0 +1,113 @@
+/* Produced by CVXGEN, 2018-05-11 17:28:57 -0400.  */
+/* CVXGEN is Copyright (C) 2006-2017 Jacob Mattingley, jem@cvxgen.com. */
+/* The code in this file is Copyright (C) 2006-2017 Jacob Mattingley. */
+/* CVXGEN, or solvers produced by CVXGEN, cannot be used for commercial */
+/* applications without prior written permission from Jacob Mattingley. */
+
+/* Filename: matrix_support.c. */
+/* Description: Support functions for matrix multiplication and vector filling. */
+#include "solver.h"
+void solver_324::multbymA(double *lhs, double *rhs) {
+}
+void solver_324::multbymAT(double *lhs, double *rhs) {
+  lhs[0] = 0;
+  lhs[1] = 0;
+  lhs[2] = 0;
+}
+void solver_324::multbymG(double *lhs, double *rhs) {
+  lhs[0] = -rhs[0]*(params.A[0])-rhs[1]*(params.A[36])-rhs[2]*(params.A[72]);
+  lhs[1] = -rhs[0]*(params.A[1])-rhs[1]*(params.A[37])-rhs[2]*(params.A[73]);
+  lhs[2] = -rhs[0]*(params.A[2])-rhs[1]*(params.A[38])-rhs[2]*(params.A[74]);
+  lhs[3] = -rhs[0]*(params.A[3])-rhs[1]*(params.A[39])-rhs[2]*(params.A[75]);
+  lhs[4] = -rhs[0]*(params.A[4])-rhs[1]*(params.A[40])-rhs[2]*(params.A[76]);
+  lhs[5] = -rhs[0]*(params.A[5])-rhs[1]*(params.A[41])-rhs[2]*(params.A[77]);
+  lhs[6] = -rhs[0]*(params.A[6])-rhs[1]*(params.A[42])-rhs[2]*(params.A[78]);
+  lhs[7] = -rhs[0]*(params.A[7])-rhs[1]*(params.A[43])-rhs[2]*(params.A[79]);
+  lhs[8] = -rhs[0]*(params.A[8])-rhs[1]*(params.A[44])-rhs[2]*(params.A[80]);
[…]

### 2018-05-11 cvxgen/32pt4obspt/cvxgen/solver.h

@@ -1,0 +1,136 @@
+/* Produced by CVXGEN, 2018-05-11 17:28:57 -0400.  */
+/* CVXGEN is Copyright (C) 2006-2017 Jacob Mattingley, jem@cvxgen.com. */
+/* The code in this file is Copyright (C) 2006-2017 Jacob Mattingley. */
+/* CVXGEN, or solvers produced by CVXGEN, cannot be used for commercial */
+/* applications without prior written permission from Jacob Mattingley. */
+
+/* Filename: solver.h. */
+/* Description: Header file with relevant definitions. */
+#ifndef SOLVER_H
+#define SOLVER_H
+/* Uncomment the next line to remove all library dependencies. */
+/*#define ZERO_LIBRARY_MODE */
+#ifdef MATLAB_MEX_FILE
+/* Matlab functions. MATLAB_MEX_FILE will be defined by the mex compiler. */
+/* If you are not using the mex compiler, this functionality will not intrude, */
+/* as it will be completely disabled at compile-time. */
+#include "mex.h"
+#else
+#ifndef ZERO_LIBRARY_MODE
+#include <stdio.h>
+#endif
+#endif
+/* Space must be allocated somewhere (testsolver.c, csolve.c or your own */
+/* program) for the global variables vars, params, work and settings. */
+/* At the bottom of this file, they are externed. */
+#ifndef ZERO_LIBRARY_MODE
+#include <math.h>
+#define pm(A, m, n) printmatrix(#A, A, m, n, 1)
+#endif
+namespace solver_324 {
+typedef struct Params_t {
+  double H[3];
+  double A[108];
+} Params;
+typedef struct Vars_t {
+  double *w; /* 3 rows. */
+} Vars;
+typedef struct Workspace_t {
+  double h[36];
+  double s_inv[36];
+  double s_inv_z[36];
+  double *b;
+  double q[3];
+  double rhs[75];
+  double x[75];
+  double *s;
+  double *z;
+  double *y;
+  double lhs_aff[75];
+  double lhs_cc[75];
+  double buffer[75];
+  double buffer2[75];
+  double KKT[219];
+  double L[147];
+  double d[75];
+  double v[75];
+  double d_inv[75];
+  double gap;
+  double optval;
+  double ineq_resid_squared;
+  double eq_resid_squared;
+  double block_33[1];
+  /* Pre-op symbols. */
+  int converged;
+} Workspace;
+typedef struct Settings_t {
[…]

### 2018-05-11 cvxgen/32pt4obspt/cvxgen/testsolver.cpp

@@ -1,0 +1,162 @@
+/* Produced by CVXGEN, 2018-05-11 17:28:57 -0400.  */
+/* CVXGEN is Copyright (C) 2006-2017 Jacob Mattingley, jem@cvxgen.com. */
+/* The code in this file is Copyright (C) 2006-2017 Jacob Mattingley. */
+/* CVXGEN, or solvers produced by CVXGEN, cannot be used for commercial */
+/* applications without prior written permission from Jacob Mattingley. */
+
+/* Filename: testsolver.c. */
+/* Description: Basic test harness for solver.c. */
+#include "solver.h"
+Vars vars;
+Params params;
+Workspace work;
+Settings settings;
+#define NUMTESTS 0
+int main(int argc, char **argv) {
+  int num_iters;
+#if (NUMTESTS > 0)
+  int i;
+  double time;
+  double time_per;
+#endif
+  set_defaults();
+  setup_indexing();
+  load_default_data();
+  /* Solve problem instance for the record. */
+  settings.verbose = 1;
+  num_iters = solve();
+#ifndef ZERO_LIBRARY_MODE
+#if (NUMTESTS > 0)
+  /* Now solve multiple problem instances for timing purposes. */
+  settings.verbose = 0;
+  tic();
+  for (i = 0; i < NUMTESTS; i++) {
+    solve();
+  }
+  time = tocq();
+  printf("Timed %d solves over %.3f seconds.\n", NUMTESTS, time);
+  time_per = time / NUMTESTS;
+  if (time_per > 1) {
+    printf("Actual time taken per solve: %.3g s.\n", time_per);
+  } else if (time_per > 1e-3) {
+    printf("Actual time taken per solve: %.3g ms.\n", 1e3*time_per);
+  } else {
+    printf("Actual time taken per solve: %.3g us.\n", 1e6*time_per);
+  }
+#endif
+#endif
+  return 0;
+}
+void load_default_data(void) {
+  params.H[0] = 1.5507979025745755;
+  params.H[1] = 1.7081478226181048;
+  params.H[2] = 1.2909047389129444;
+  params.A[0] = 0.04331042079065206;
+  params.A[1] = 1.5717878173906188;
+  params.A[2] = 1.5851723557337523;
+  params.A[3] = -1.497658758144655;
+  params.A[4] = -1.171028487447253;
+  params.A[5] = -1.7941311867966805;
+  params.A[6] = -0.23676062539745413;
[…]

### 2018-05-11 svm_seperator.cpp

@@ -6,6 +6,7 @@
 #include <sstream>
 #include "svmcvxwrapper_2pt_4obs.h"
 #include "svmcvxwrapper_8pt_4obs.h"
+#include "svmcvxwrapper_32pt_4obs.h"
 #include <cassert>
 
 using namespace std;
@@ -85,6 +86,79 @@ vector<hyperplane> SvmSeperator::_8_4_seperate() {
     vectoreuc& obs4 = obs.pts[3];
 
     result.push_back(_8pt4obspt_svm(pt1, pt2, pt3, pt4, pt5, pt6, pt7, pt8, obs1, obs2, obs3, obs4));
+
+    auto& hp = result.back();
+    for (auto& pt : obs.pts) {
+      if (pt.dot(hp.normal) < hp.distance - 1e-6) {
+        std::stringstream sstr;
+        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        // throw runtime_error(sstr.str());
+        std::cerr << sstr.str() << std::endl;
+      }
+    }
+
+    for (auto& pt : pts) {
+      if (pt.dot(hp.normal) > hp.distance + 1e-6) {
+        std::stringstream sstr;
+        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        // throw runtime_error(sstr.str());
+        std::cerr << sstr.str() << std::endl;
+      }
+    }
+
+  }
+
+  return result;
+}
+
+vector<hyperplane> SvmSeperator::_32_4_seperate() {
+  assert(pts.size() == 32);
+  vector<hyperplane> result;
+  vectoreuc& pt1 = pts[0];
+  vectoreuc& pt2 = pts[1];
+  vectoreuc& pt3 = pts[2];
+  vectoreuc& pt4 = pts[3];
+  vectoreuc& pt5 = pts[4];
+  vectoreuc& pt6 = pts[5];
+  vectoreuc& pt7 = pts[6];
+  vectoreuc& pt8 = pts[7];
+  vectoreuc& pt9 = pts[8];
+  vectoreuc& pt10 = pts[9];
+  vectoreuc& pt11 = pts[10];
+  vectoreuc& pt12 = pts[11];
[…]

### 2018-05-11 svm_seperator.h

@@ -23,6 +23,7 @@ class SvmSeperator {
     vector<hyperplane> seperate();
     vector<hyperplane> _2_4_seperate();
     vector<hyperplane> _8_4_seperate();
+    vector<hyperplane> _32_4_seperate();
 };
 
 #endif

### 2018-05-11 svmcvxwrapper_32pt_4obs.cpp

@@ -1,0 +1,175 @@
+#include "svmcvxwrapper_32pt_4obs.h"
+#include "cvxgen/32pt4obspt/cvxgen/solver.h"
+#include <iostream>
+
+namespace solver_324 {
+
+solver_324::Vars vars;
+solver_324::Params params;
+solver_324::Workspace work;
+solver_324::Settings settings;
+
+}
+
+hyperplane _32pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
+                          const vectoreuc& pt3, const vectoreuc& pt4,
+                          const vectoreuc& pt5, const vectoreuc& pt6,
+                          const vectoreuc& pt7, const vectoreuc& pt8,
+                          const vectoreuc& pt9, const vectoreuc& pt10,
+                          const vectoreuc& pt11, const vectoreuc& pt12,
+                          const vectoreuc& pt13, const vectoreuc& pt14,
+                          const vectoreuc& pt15, const vectoreuc& pt16,
+                          const vectoreuc& pt17, const vectoreuc& pt18,
+                          const vectoreuc& pt19, const vectoreuc& pt20,
+                          const vectoreuc& pt21, const vectoreuc& pt22,
+                          const vectoreuc& pt23, const vectoreuc& pt24,
+                          const vectoreuc& pt25, const vectoreuc& pt26,
+                          const vectoreuc& pt27, const vectoreuc& pt28,
+                          const vectoreuc& pt29, const vectoreuc& pt30,
+                          const vectoreuc& pt31, const vectoreuc& pt32,
+                          const vectoreuc& obs1, const vectoreuc& obs2,
+                          const vectoreuc& obs3, const vectoreuc& obs4)
+{
+  solver_324::set_defaults();
+  solver_324::setup_indexing();
+
+  solver_324::params.H[0] = 1;
+  solver_324::params.H[1] = 1;
+  solver_324::params.H[2] = 0;
+
+  solver_324::params.A[0] = pt1.crds[0];
+  solver_324::params.A[1] = pt2.crds[0];
+  solver_324::params.A[2] = pt3.crds[0];
[…]

### 2018-05-12 discrete_search.hpp
Friday

@@ -174,8 +174,13 @@ private:
 
     // check if occupied by another robot
     for (const auto& otherRobot : m_otherRobots) {
-      double distSq = pow(otherRobot.first - coord.first, 2) + pow(otherRobot.second - coord.second, 2);
-      if (distSq < pow(2 * m_robotRadius, 2)) {
+      // double distSq = pow(otherRobot.first - coord.first, 2) + pow(otherRobot.second - coord.second, 2);
+      // if (distSq < pow(2 * m_robotRadius, 2)) {
+      //   return false;
+      // }
+
+      if (   fabs(coord.first - otherRobot.first) <= 2 * m_robotRadius
+          && fabs(coord.second - otherRobot.second) <= 2 * m_robotRadius) {
         return false;
       }
     }

### 2018-05-12 main.cpp

@@ -81,6 +81,7 @@ int main(int argc, char** argv) {
   const double v_max = jsn["v_max"];
   const double a_max = jsn["a_max"];
   const double lambda_hyperplanes = jsn["lambda_hyperplanes"];
+  const double scaling_multiplier = jsn["scaling_multiplier"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
 
@@ -91,9 +92,11 @@ int main(int argc, char** argv) {
 
   srand(time(NULL));
 
+  const double stoppingDistance = v_max * v_max / (2 * a_max);
+  std::cout << "stoppingDistance: " << stoppingDistance << std::endl;
+
 
   vector<trajectory> original_trajectories;
-  ofstream out(outputfile);
 
 
   for (auto & p : fs::directory_iterator(initial_trajectories_path)) {
@@ -223,6 +226,8 @@ int main(int argc, char** argv) {
   vector<vectoreuc> positions(trajectories.size());
   vector<vectoreuc> velocities(trajectories.size());
   vector<vectoreuc> accelerations(trajectories.size());
+  // vector<vectoreuc> jerks(trajectories.size());
+  // vector<vectoreuc> snaps(trajectories.size());
 
   double printdt = jsn["print_dt"];
 
@@ -245,6 +250,10 @@ int main(int argc, char** argv) {
     cout << "init vel: " << velocities[i]<< endl;
     accelerations[i] = trajectories[i].neval(0, 2);
     cout << "init acc: " << accelerations[i]<< endl;
+    // jerks[i] = trajectories[i].neval(0, 3);
+    // cout << "init jerk: " << jerks[i]<< endl;
+    // snaps[i] = trajectories[i].neval(0, 4);
+    // cout << "init snap: " << snaps[i]<< endl;
   }
 
   // add some pertubation at the beginning for first robot
@@ -281,7 +290,7 @@ int main(int argc, char** argv) {
     cerr << ct << " / " << total_t << endl;
 
     for(int i=0; i<original_trajectories.size(); i++ ) {
-      cout << "traj " << i << " start " << ct << " / " << total_times[i] << endl;
+      cerr << "traj " << i << " start " << ct << " / " << total_times[i] << endl;
       t_start = Time::now();
 
       // if (ct > 7 && i == 0) {
@@ -318,7 +327,7 @@ int main(int argc, char** argv) {
       /*calculate voronoi hyperplanes for robot i*/
[…]

### 2018-05-12 qp_optimize.h

@@ -205,7 +205,7 @@ private:
 class ConstraintBuilder
 {
 public:
-  static constexpr double EPS = 0.0;//1e-3;
+  static constexpr double EPS = 0;//1e-3;
 
   ConstraintBuilder(
     size_t dimension,
@@ -236,9 +236,11 @@ public:
       for (size_t i = 0; i < 8; ++i) {
         m_A(idx + d, column(piece, d) + i) = derivativeBeginning[derivative][i] / pow(T, derivative);
       }
-      std::cout << "addConstraint: " << idx +d << " (constraintBeginning " << piece << "," << derivative << ")" << std::endl;
-      m_lbA(idx + d) = value(d) - EPS / 2.0;
-      m_ubA(idx + d) = value(d) + EPS / 2.0;
+      std::stringstream sstr;
+      sstr << "(constraintBeginning piece: " << piece << ", derivative: " << derivative << ")";
+      m_info[idx + d] = sstr.str();
+      m_lbA(idx + d) = value(d);// - EPS / 2.0;
+      m_ubA(idx + d) = value(d);// + EPS / 2.0;
     }
   }
 
@@ -259,9 +261,13 @@ public:
       for (size_t i = 0; i < 8; ++i) {
         m_A(idx + d, column(piece, d) + i) = derivativeEnd[derivative][i] / pow(T, derivative);
       }
-      std::cout << "addConstraint: " << idx +d << " (constraintEnd " << piece << "," << derivative << ")" << std::endl;
-      m_lbA(idx + d) = value(d) - EPS / 2.0;
-      m_ubA(idx + d) = value(d) + EPS / 2.0;
+      // std::cout << "addConstraint: " << idx +d << " (constraintEnd " << piece << "," << derivative << ")" << std::endl;
+      std::stringstream sstr;
+      sstr << "(constraintEnd piece: " << piece << ", derivative: " << derivative << ")";
+      m_info[idx + d] = sstr.str();
+
+      m_lbA(idx + d) = value(d);// - EPS / 2.0;
+      m_ubA(idx + d) = value(d);// + EPS / 2.0;
     }
   }
 
@@ -286,9 +292,14 @@ public:
       for (size_t i = 0; i < 8; ++i) {
         m_A(idx + d, column(firstPiece+1, d) + i) = -derivativeBeginning[derivative][i] / pow(Tsecond, derivative);
       }
[…]

### 2018-05-12 svm_seperator.cpp

@@ -43,17 +43,18 @@ vector<hyperplane> SvmSeperator::_2_4_seperate() {
 
     auto& hp = result.back();
     for (auto& pt : obs.pts) {
-      if (pt.dot(hp.normal) < hp.distance - 1e-6) {
+      if (pt.dot(hp.normal) < hp.distance) {
         std::stringstream sstr;
-        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        sstr << "Couldn't find hyperplane (obs.pts) normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
     }
+
     for (auto& pt : pts) {
-      if (pt.dot(hp.normal) > hp.distance + 1e-6) {
+      if (pt.dot(hp.normal) > hp.distance) {
         std::stringstream sstr;
-        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        sstr << "Couldn't find hyperplane (pts) normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
@@ -89,18 +90,18 @@ vector<hyperplane> SvmSeperator::_8_4_seperate() {
 
     auto& hp = result.back();
     for (auto& pt : obs.pts) {
-      if (pt.dot(hp.normal) < hp.distance - 1e-6) {
+      if (pt.dot(hp.normal) < hp.distance) {
         std::stringstream sstr;
-        sstr << "Couldn't find hyperplane normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
+        sstr << "Couldn't find hyperplane (obs.pts) normal " << hp.normal << " dist: " << hp.distance << " pt: " << pt << " dot product: " << pt.dot(hp.normal);
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
     }
 
     for (auto& pt : pts) {
-      if (pt.dot(hp.normal) > hp.distance + 1e-6) {
[…]

### 2018-05-12 svm_seperator.h

@@ -24,6 +24,9 @@ class SvmSeperator {
     vector<hyperplane> _2_4_seperate();
     vector<hyperplane> _8_4_seperate();
     vector<hyperplane> _32_4_seperate();
+    const vector<vectoreuc>& getPts() const {
+      return pts;
+    }
 };
 
 #endif

### 2018-05-12 svmcvxwrapper_2pt_4obs.cpp

@@ -15,6 +15,10 @@ hyperplane _2pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
 {
 
     solver_24::set_defaults();
+    solver_24::settings.eps = 1e-8;
+    solver_24::settings.max_iters = 100;
+    solver_24::settings.resid_tol = 1e-8;
+    solver_24::settings.kkt_reg = 1e-4;
     solver_24::setup_indexing();
 
     solver_24::params.H[0] = 1;
@@ -52,7 +56,7 @@ hyperplane _2pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
 
     double nx = solver_24::vars.w[0];
     double ny = solver_24::vars.w[1];
-    double d = solver_24::vars.w[2] + solver_24::work.converged;
+    double d = solver_24::vars.w[2];// + (2*solver_24::work.converged - 1);
 
     vectoreuc normal(2);
     normal[0] = nx;

### 2018-05-12 svmcvxwrapper_32pt_4obs.cpp

@@ -31,6 +31,10 @@ hyperplane _32pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
                           const vectoreuc& obs3, const vectoreuc& obs4)
 {
   solver_324::set_defaults();
+  solver_324::settings.eps = 1e-8;
+  solver_324::settings.max_iters = 100;
+  solver_324::settings.resid_tol = 1e-8;
+  solver_324::settings.kkt_reg = 1e-4;
   solver_324::setup_indexing();
 
   solver_324::params.H[0] = 1;
@@ -155,12 +159,12 @@ hyperplane _32pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
 
   // std::cout << "8-4 converged: " << solver_84::work.converged << std::endl;
   if (!solver_324::work.converged) {
-      std::cerr << "32-4 not converged" << std::endl;
+      //std::cerr << "32-4 not converged" << std::endl;
   }
 
   double nx = solver_324::vars.w[0];
   double ny = solver_324::vars.w[1];
-  double d = solver_324::vars.w[2] + solver_324::work.converged;
+  double d = solver_324::vars.w[2];// + (2*solver_324::work.converged-1);// + solver_324::work.converged;
 
   vectoreuc normal(2);
   normal[0] = nx;

### 2018-05-12 svmcvxwrapper_8pt_4obs.cpp

@@ -19,6 +19,10 @@ hyperplane _8pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
                           const vectoreuc& obs3, const vectoreuc& obs4)
 {
   solver_84::set_defaults();
+  solver_84::settings.eps = 1e-8;
+  solver_84::settings.max_iters = 100;
+  solver_84::settings.resid_tol = 1e-8;
+  solver_84::settings.kkt_reg = 1e-4;
   solver_84::setup_indexing();
 
   solver_84::params.H[0] = 1;
@@ -70,12 +74,12 @@ hyperplane _8pt4obspt_svm(const vectoreuc& pt1, const vectoreuc& pt2,
 
   // std::cout << "8-4 converged: " << solver_84::work.converged << std::endl;
   if (!solver_84::work.converged) {
-      std::cerr << "8-4 not converged" << std::endl;
+      //std::cerr << "8-4 not converged" << std::endl;
   }
 
   double nx = solver_84::vars.w[0];
   double ny = solver_84::vars.w[1];
-  double d = solver_84::vars.w[2] + solver_84::work.converged;
+  double d = solver_84::vars.w[2];//  + (2*solver_84::work.converged-0.01);// + solver_84::work.converged;
 
   vectoreuc normal(2);
   normal[0] = nx;

### 2018-05-12 vectoreuc.cpp

@@ -53,7 +53,7 @@ vectoreuc vectoreuc::normalized() {
   return res;
 }
 
-double vectoreuc::dot(vectoreuc& rhs) {
+double vectoreuc::dot(vectoreuc& rhs) const {
   double res = 0;
   for(int i=0; i<crds.size(); i++) {
     res += crds[i] * rhs[i];

### 2018-05-12 vectoreuc.h

@@ -17,7 +17,7 @@ class vectoreuc {
     vectoreuc operator/(const double& s);
     vectoreuc normalized();
     double L2norm();
-    double dot(vectoreuc& rhs);
+    double dot(vectoreuc& rhs) const;
     friend ostream& operator<<(ostream& out, const vectoreuc& vec);
     void zero();
     vectoreuc operator*(double rhs);

### 2018-05-12 vis/vis.py

@@ -198,10 +198,10 @@ def animate(frame):
 
 
     hpIdx = 0
-    robot = 10
+    robot = 0
     if args.hyperplanes and "hyperplanes" in jsn and frame < len(jsn["hyperplanes"]) and jsn["hyperplanes"][frame] and robot < len(jsn["hyperplanes"][frame]) and jsn["hyperplanes"][frame][robot]:
       for hp in jsn["hyperplanes"][frame][robot]:
-        if hp and hp[3] == 1:
+        if hp: # and hp[3] == 0:
           (hpx,hpy) = genvoroxy(hp)
           (hpnx, hpny) = genvoronormal(hp)
           if hpIdx >= len(hyperplanes):
@@ -279,7 +279,7 @@ if __name__ == "__main__":
   colors = ['b', 'g', 'r', 'c', 'm', 'k'] * 10
 
   fig = plt.figure()
-  ax = plt.axes(xlim=(-2.4,2.6), ylim=(-0.8,2.1))
+  ax = plt.axes(xlim=(-4,4), ylim=(-4,4))
   ax.set_aspect('equal')
   # plt.axis('off')
   time_text = ax.text(0.02, 0.95, '', transform=ax.transAxes)

### 2018-05-12 vis/vis_static.py

@@ -20,7 +20,7 @@ if __name__ == "__main__":
   dt = jsn["dt"]
   t = np.arange(0, numFrames * dt, dt)
 
-  colors = ['b', 'g', 'r', 'c', 'm', 'k']
+  colors = ['b', 'g', 'r', 'c', 'm', 'k'] * 10
 
   gs = gridspec.GridSpec(5, 1)
   fig = plt.figure()

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
ros integration added

@@ -1,0 +1,984 @@
+#include "ros/ros.h"
+#include <iostream>
+#include <fstream>
+#include <experimental/filesystem>
+#include <vector>
+#include "csv/CSVparser.hpp"
+#include <algorithm>
+#include <cassert>
+#include <cstdarg>
+#include <utility>
+#include "vectoreuc.h"
+#include <chrono>
+#include "trajectory.h"
+#include "curve.h"
+#include "hyperplane.h"
+#include "obstacle.h"
+#include "cxxopts.hpp"
+#include "json.hpp"
+#include <chrono>
+#include <random>
+#include "svmoptimization.h"
+#include "utility.h"
+#include "occupancy_grid.h"
+#include "svm_seperator.h"
+#include "discrete_search.hpp"
+#include "create2_controller/TrajectoryState2D.h"
+#include "create2_controller/Vector2D.h"
+#include <tf/transform_listener.h>
+
+#include "qp_optimize.h"
+
+// different solvers
+#include <qpOASES.hpp>
+#include "osqp.h"
+
+using namespace std;
+
+namespace fs = std::experimental::filesystem::v1;
+using namespace std;
+
+
+typedef chrono::high_resolution_clock Time;
+typedef chrono::milliseconds ms;
+typedef chrono::duration<float> fsec;
+
+double linearInterpolation(double start, double end, size_t idx, size_t count)
+{
+  return start + (end - start) * idx / (count - 1);
+}
+
+vector<vectoreuc> positions;
+
+void getPositions(const tf::TransformListener& listener, int number_of_robots) {
+  tf::StampedTransform transform;
+
+  for(int i=1; i<=number_of_robots; i++) {
+    listener.lookupTransform("/world", "/create" + std::to_string(i), ros::Time(0), transform);
+    positions[i-1][0] = transform.getOrigin().x();
+    positions[i-1][1] = transform.getOrigin().y();
+  }
+}
+
+int main(int argc, char **argv) {
+  ros::init(argc, argv, "planner");
+  ros::NodeHandle nh;
+
+
+  create2_controller::TrajectoryState2D desired_state_msg;
+  ros::Publisher desired_state_publisher = nh.advertise<create2_controller::TrajectoryState2D>("desired_state", 1000);
+
+  tf::TransformListener transformlistener;
+
+  string config_path;
+  cxxopts::Options options("Trajectory Replanner", "trajectory replanner");
+  options.add_options()
[…]

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
spin

@@ -228,7 +228,7 @@ int main(int argc, char **argv) {
 
 
   for(double ct = 0; ct <= total_t && ros::ok() ; ct+=dt) {
-
+    ros::spinOnce();
 
     getPositions(transformlistener, number_of_robots);
 

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
successful single-robot test

@@ -50,13 +50,13 @@ double linearInterpolation(double start, double end, size_t idx, size_t count)
 
 vector<vectoreuc> positions;
 
-void getPositions(const tf::TransformListener& listener, int number_of_robots) {
+void getPositions(const tf::TransformListener& listener, const std::vector<std::string>& robots) {
   tf::StampedTransform transform;
 
-  for(int i=1; i<=number_of_robots; i++) {
-    listener.lookupTransform("/world", "/create" + std::to_string(i), ros::Time(0), transform);
-    positions[i-1][0] = transform.getOrigin().x();
-    positions[i-1][1] = transform.getOrigin().y();
+  for(int i=0; i<robots.size(); i++) {
+    listener.lookupTransform("/world", robots[i], ros::Time(0), transform);
+    positions[i][0] = transform.getOrigin().x();
+    positions[i][1] = transform.getOrigin().y();
   }
 }
 
@@ -85,6 +85,9 @@ int main(int argc, char **argv) {
 
   config_path = result["cfg"].as<string>();
 
+  ros::NodeHandle nl("~");
+  nl.param<std::string>("configFile", config_path, "../config.json");
+
   ifstream cfg(config_path);
 
   nlohmann::json jsn = nlohmann::json::parse(cfg);
@@ -106,9 +109,16 @@ int main(int argc, char **argv) {
   const double a_max = jsn["a_max"];
   const double lambda_hyperplanes = jsn["lambda_hyperplanes"];
   const double scaling_multiplier = jsn["scaling_multiplier"];
-  const int number_of_robots = jsn["number_of_robots"];
+  // const int number_of_robots = jsn["number_of_robots"];
+  const std::vector<std::string> robots = jsn["robots"];
+  const int number_of_robots = (int)robots.size();
   const int robot_id = jsn["robot_id"];
-
+  const double scale_traj = jsn["scale_traj"];
+  const float lambda_min_der = jsn["lambda_min_der"];
+  const float lambda_min_der_vel = jsn["lambda_min_der_vel"];
+  const float lambda_min_der_acc = jsn["lambda_min_der_acc"];
+  const float lambda_min_der_jerk = jsn["lambda_min_der_jerk"];
+  const float lambda_min_der_snap = jsn["lambda_min_der_snap"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
 
@@ -130,7 +140,7 @@ int main(int argc, char **argv) {
[…]

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
fix multi-robot crash

@@ -73,7 +73,7 @@ int main(int argc, char **argv) {
   string config_path;
   cxxopts::Options options("Trajectory Replanner", "trajectory replanner");
   options.add_options()
-    ("cfg", "Config file", cxxopts::value<std::string>()->default_value("../config.json"))
+    ("cfg", "Config file", cxxopts::value<std::string>()->default_value("/home/odroid/robustMotionExecution/mr-trajectory-replanning/ros_ws/src/planner/src/config.json"))
     ("help", "Display help page");
 
   auto result = options.parse(argc, argv);
@@ -86,7 +86,7 @@ int main(int argc, char **argv) {
   config_path = result["cfg"].as<string>();
 
   ros::NodeHandle nl("~");
-  nl.param<std::string>("configFile", config_path, "../config.json");
+  nl.param<std::string>("configFile", config_path, "/home/odroid/robustMotionExecution/mr-trajectory-replanning/ros_ws/src/planner/src/config.json");
 
   ifstream cfg(config_path);
 
@@ -217,6 +217,9 @@ int main(int argc, char **argv) {
 
 
   positions.resize(number_of_robots);
+  for(int i=0;i<number_of_robots; ++i) {
+    positions[i] = vectoreuc(2);
+  }
   positions[robot_id] = traj.eval(0);
   vectoreuc velocitydes = traj.neval(0,1);
   vectoreuc accelerationdes = traj.neval(0,2);

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
multicast receiver

@@ -14,8 +14,6 @@
 #include "curve.h"
 #include "hyperplane.h"
 #include "obstacle.h"
-#include "cxxopts.hpp"
-#include "json.hpp"
 #include <chrono>
 #include <random>
 #include "svmoptimization.h"
@@ -26,6 +24,9 @@
 #include "create2_controller/TrajectoryState2D.h"
 #include "create2_controller/Vector2D.h"
 #include <tf/transform_listener.h>
+#include <boost/asio.hpp>
+#include <array>
+#include <iterator>
 
 #include "qp_optimize.h"
 
@@ -38,6 +39,8 @@ using namespace std;
 namespace fs = std::experimental::filesystem::v1;
 using namespace std;
 
+using boost::asio::ip::udp;
+using boost::asio::ip::address;
 
 typedef chrono::high_resolution_clock Time;
 typedef chrono::milliseconds ms;
@@ -70,59 +73,78 @@ int main(int argc, char **argv) {
 
   tf::TransformListener transformlistener;
 
-  string config_path;
-  cxxopts::Options options("Trajectory Replanner", "trajectory replanner");
-  options.add_options()
-    ("cfg", "Config file", cxxopts::value<std::string>()->default_value("/home/odroid/robustMotionExecution/mr-trajectory-replanning/ros_ws/src/planner/src/config.json"))
-    ("help", "Display help page");
-
-  auto result = options.parse(argc, argv);
-
-  if(result.count("help")>0) {
-    cout << options.help() << endl;
-    return 0;
-  }
-
-  config_path = result["cfg"].as<string>();
-
   ros::NodeHandle nl("~");
-  nl.param<std::string>("configFile", config_path, "/home/odroid/robustMotionExecution/mr-trajectory-replanning/ros_ws/src/planner/src/config.json");
 
-  ifstream cfg(config_path);
+  string initial_trajectory_path;
+  nl.getParam("trajectory", initial_trajectory_path);
+  cout << initial_trajectory_path << endl;
+  
+  string obstacles_path;
+  nl.getParam("obstacles", obstacles_path);
 
-  nlohmann::json jsn = nlohmann::json::parse(cfg);
+  double dt;
+  nl.getParam("replan_period", dt);
 
-  string initial_trajectory_path = jsn["trajectory"];
-  string obstacles_path = jsn["obstacles"];
-  double dt = jsn["replan_period"];
[…]

### 2018-05-13 ros_ws/src/planner/src/planner.cpp
boost shrink

@@ -24,7 +24,9 @@
 #include "create2_controller/TrajectoryState2D.h"
 #include "create2_controller/Vector2D.h"
 #include <tf/transform_listener.h>
-#include <boost/asio.hpp>
+#include <boost/asio/ip/udp.hpp>
+#include <boost/asio/ip/address.hpp>
+#include <boost/asio/ip/multicast.hpp>
 #include <array>
 #include <iterator>
 

### 2018-05-14 qp_optimize.h
do not constraint first control point of first curve

@@ -311,21 +311,44 @@ public:
     double dist)
   {
     assert(piece < m_numPieces);
-    // one constraint per control point
-    size_t idx = addConstraints(8);
 
-    for (size_t cp = 0; cp < 8; ++cp) {
-      for (size_t d = 0; d < m_dimension; ++d) {
-        m_A(idx + cp, column(piece, d) + cp) = normal(d);
+    if (piece == 0) {
+      // one constraint per control point
+      size_t idx = addConstraints(7);
+
+      for (size_t cp = 1; cp < 8; ++cp) {
+        for (size_t d = 0; d < m_dimension; ++d) {
+          m_A(idx + cp - 1, column(piece, d) + cp) = normal(d);
+        }
+        // std::cout << "addConstraint: " << idx+cp << " (hyperplane " << piece << ")" << std::endl;
+        std::stringstream sstr;
+        sstr << "(hyperspace piece: " << piece << ", cp: " << cp << ")";
+        m_info[idx + cp - 1] = sstr.str();
+
+        m_lbA(idx + cp - 1) = std::numeric_limits<double>::lowest();
+        m_ubA(idx + cp - 1) = dist;// + 1e-3;// + EPS;
       }
-      // std::cout << "addConstraint: " << idx+cp << " (hyperplane " << piece << ")" << std::endl;
-      std::stringstream sstr;
-      sstr << "(hyperspace piece: " << piece << ", cp: " << cp << ")";
-      m_info[idx + cp] = sstr.str();
 
-      m_lbA(idx + cp) = std::numeric_limits<double>::lowest();
-      m_ubA(idx + cp) = dist;// + 1e-3;// + EPS;
+    } else {
+      // one constraint per control point
+      size_t idx = addConstraints(8);
+
+      for (size_t cp = 0; cp < 8; ++cp) {
+        for (size_t d = 0; d < m_dimension; ++d) {
+          m_A(idx + cp, column(piece, d) + cp) = normal(d);
+        }
+        // std::cout << "addConstraint: " << idx+cp << " (hyperplane " << piece << ")" << std::endl;
+        std::stringstream sstr;
+        sstr << "(hyperspace piece: " << piece << ", cp: " << cp << ")";
+        m_info[idx + cp] = sstr.str();
+
+        m_lbA(idx + cp) = std::numeric_limits<double>::lowest();
+        m_ubA(idx + cp) = dist;// + 1e-3;// + EPS;
+      }
     }
+
+
+
   }
 
   // adds bounds to the decision variables

### 2018-05-14 ros_ws/src/planner/src/planner.cpp
planner: improved behavior w/ respect to time

@@ -289,9 +289,17 @@ int main(int argc, char **argv) {
   }
 
 
+  ros::Time start = ros::Time::now();
 
-  for(double ct = 0; ct <= total_t && ros::ok() ; ct+=dt) {
+  // for(double ct = 0; ct <= total_t && ros::ok() ; ct+=dt) {
+  while (ros::ok()) {
     ros::spinOnce();
+    ros::Time now = ros::Time::now();
+    ros::Duration duration = now - start;
+    double ct = duration.toSec();
+    if (ct > total_t) {
+      break;
+    }
 
     getPositions(transformlistener, robots);
 
@@ -1021,9 +1029,9 @@ int main(int argc, char **argv) {
     cout << "optimization time: " << d.count() << "ms" << endl;
 
 
-    vectoreuc despos = traj.neval(dt, 0);
-    velocitydes = traj.neval(dt, 1);
-    accelerationdes = traj.neval(dt, 2);
+    vectoreuc despos = traj.neval(2*dt, 0);
+    velocitydes = traj.neval(2*dt, 1);
+    accelerationdes = traj.neval(2*dt, 2);
 
     desired_state_msg.position.x = despos[0];
     desired_state_msg.position.y = despos[1];

### 2018-05-14 main.cpp
add configuration for objective lambdas

@@ -81,6 +81,11 @@ int main(int argc, char** argv) {
   const double v_max = jsn["v_max"];
   const double a_max = jsn["a_max"];
   const double lambda_hyperplanes = jsn["lambda_hyperplanes"];
+  const double lambda_min_der = jsn["lambda_min_der"];
+  const double lambda_min_der_vel = jsn["lambda_min_der_vel"];
+  const double lambda_min_der_acc = jsn["lambda_min_der_acc"];
+  const double lambda_min_der_jerk = jsn["lambda_min_der_jerk"];
+  const double lambda_min_der_snap = jsn["lambda_min_der_snap"];
   const double scaling_multiplier = jsn["scaling_multiplier"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
@@ -793,8 +798,8 @@ int main(int argc, char** argv) {
       ObjectiveBuilder ob(problem_dimension, pieceDurations);
 
       double remaining_time = std::max(total_times[i] - ct, curve_count * dt * 1.1);
-      double factor = 1.0f / remaining_time;
-      ob.minDerivativeSquared(1 * factor, 0 * factor, 5e-3 * factor, 0 * factor);
+      double factor = lambda_min_der / remaining_time;
+      ob.minDerivativeSquared(lambda_min_der_vel * factor, lambda_min_der_acc * factor, lambda_min_der_jerk * factor, lambda_min_der_snap * factor);
 
       for (const auto& o : endCloseToObjectives) {
         ob.endCloseTo(o.piece, o.lambda, o.value);

### 2018-05-14 main.cpp
add config that we use for physical experiment

@@ -66,6 +66,7 @@ int main(int argc, char** argv) {
   nlohmann::json jsn = nlohmann::json::parse(cfg);
 
   string initial_trajectories_path = jsn["trajectories"];
+  float scale_traj = jsn["scale_traj"];
   string obstacles_path = jsn["obstacles"];
   double dt = jsn["replan_period"];
   int problem_dimension = jsn["problem_dimension"];
@@ -109,7 +110,7 @@ int main(int argc, char** argv) {
     trajectory trj;
     for(int i=0; i<file.rowCount(); i++) {
       double duration = stod(file[i][0]);
-      curve crv(duration, problem_dimension);
+      curve crv(duration * scale_traj, problem_dimension);
       for(int j=1; j<=problem_dimension * ppc; j+=problem_dimension) {
         vectoreuc cp(problem_dimension);
         for(int u=0; u<problem_dimension; u++) {

### 2018-05-15 ros_ws/src/planner/src/planner.cpp
add logfile and visualization tool

@@ -148,7 +148,10 @@ int main(int argc, char **argv) {
   string alg;
   nl.getParam("algorithm", alg);
 
+  string outFile;
+  nl.getParam("outFile", outFile);
 
+  std::ofstream out(outFile);
 
   srand(time(NULL));
 
@@ -203,12 +206,18 @@ int main(int argc, char **argv) {
 
   OG og(cell_size, -10, 10, -10, 10, obstacles);
 
+  out << "environment:" << endl;
+  out << "  robot_radius: " << robot_radius << endl;
+  out << "  cellSize: " << cell_size << endl;
+  out << "  obstacles:" << endl;
+
   vector<obstacle2D> cell_based_obstacles;
   for (size_t i = 0; i < og.max_i(); ++i) {
     for (size_t j = 0; j < og.max_j(); ++j) {
       OG::index idx(i, j);
       if (og.idx_occupied(idx)) {
         pair<double, double> coord = og.get_coordinates(idx);
+        out << "    - [" << coord.first << "," << coord.second << "]" << endl;
         // std::cout << "occ: " << coord.first << "," << coord.second << std::endl;
 
         obstacle2D o;
@@ -280,6 +289,7 @@ int main(int argc, char **argv) {
 
   std::array<char, 128> recv_buf;
 
+  ROS_INFO("Waiting for startTrajectory command!");
   while(true) {
     int len = socket.receive(boost::asio::buffer(recv_buf));
     string socketdata(recv_buf.data(), len);
@@ -287,9 +297,13 @@ int main(int argc, char **argv) {
     if(socketdata == "startTrajectory")
       break;
   }
+  socket.set_option(boost::asio::ip::multicast::leave_group(multicast_address));
+  socket.close();
 
 
   ros::Time start = ros::Time::now();
+
+  out << "iterations:" << endl;
 
   // for(double ct = 0; ct <= total_t && ros::ok() ; ct+=dt) {
   while (ros::ok()) {
@@ -301,10 +315,14 @@ int main(int argc, char **argv) {
       break;
     }
 
-    getPositions(transformlistener, robots);
-
     cerr << ct << " / " << total_t << endl;
+    out << "  - time: " << ct << endl;
 
+    getPositions(transformlistener, robots);
+    out << "    positions:" << endl;
+    for (size_t i = 0; i < number_of_robots; ++i) {
+      out << "      - [" << positions[i][0] << "," << positions[i][1] << "]" << endl;
+    }
 
[…]

### 2018-05-15 main.cpp
rvo2 vs rme compare added

@@ -59,9 +59,12 @@ int main(int argc, char** argv) {
     return 0;
   }
 
+
   config_path = result["cfg"].as<string>();
 
   ifstream cfg(config_path);
+
+  nlohmann::json compareStats;
 
   nlohmann::json jsn = nlohmann::json::parse(cfg);
 
@@ -240,6 +243,7 @@ int main(int argc, char** argv) {
   output_json["dt"] = printdt;
   output_json["robot_radius"] = robot_radius;
   output_json["number_of_robots"] = original_trajectories.size();
+  compareStats["number_of_robots"] = original_trajectories.size();
   int steps_per_cycle = (dt / printdt)+0.5;
   int output_iter = 0;
 
@@ -288,6 +292,14 @@ int main(int argc, char** argv) {
   std::chrono::time_point<std::chrono::high_resolution_clock> t_start, t_start_a_star, t_end_a_star, t_start_svm, t_end_svm, t_start_qp, t_end_qp;
 
   double everyone_reached = false;
+
+  vector<double> max_opt_times(original_trajectories.size(), -1);
+  vector<double> average_opt_times(original_trajectories.size(), 0);
+  vector<int> opt_counts(original_trajectories.size(), 0);
+  vector<int> obstacle_crash_counts(original_trajectories.size(), 0);
+  vector<int> obstacle_no_crash_counts(original_trajectories.size(), 0);
+  vector<int> robot_crash_counts(original_trajectories.size(), 0);
+  vector<int> robot_no_crash_counts(original_trajectories.size(), 0);
 
   for(double ct = 0; ct <= total_t /*+ 5*/ /*!everyone_reached*/ ; ct+=dt) {
 
@@ -1154,6 +1166,9 @@ int main(int argc, char** argv) {
       total_time_for_opt += d.count();
       total_count_for_opt++;
       cout << "optimization time: " << d.count() << "ms" << endl;
+      average_opt_times[i]+=d.count();
+      opt_counts[i]++;
+      max_opt_times[i] = max((double)d.count(), max_opt_times[i]);
       outStats << "," << d.count()
                << "," << chrono::duration_cast<ms>(t_end_a_star - t_start_a_star).count()
                << "," << chrono::duration_cast<ms>(t_end_svm - t_start_svm).count()
@@ -1185,6 +1200,38 @@ int main(int argc, char** argv) {
     for(int v = 0; v < steps_per_cycle; v++) {
       for(int i=0; i<trajectories.size(); i++) {
[…]

### 2018-05-15 obstacle.cpp

@@ -94,6 +94,15 @@ bool obstacle2D::point_inside(vectoreuc& pt) {
   return true;
 }
 
+bool obstacle2D::point_inside(vectoreuc& pt, double shift) {
+  for(int i=0; i<chplanes.size(); i++) {
+    if(chplanes[i].dist(pt) < -shift) {
+      return false;
+    }
+  }
+  return true;
+}
+
 double obstacle2D::closest_distance(vectoreuc& pt) {
   double mindist = numeric_limits<double>::infinity();
   for(int i=0; i<chplanes.size(); i++) {

### 2018-05-15 obstacle.h

@@ -20,6 +20,7 @@ class obstacle2D {
     void convex_hull();
     void ch_planes(double shift);
     bool point_inside(vectoreuc& pt);
+    bool point_inside(vectoreuc& pt, double shift);
     double closest_distance(vectoreuc& pt); // should be called only when point is inside
     double biggest_negative_distance(vectoreuc& pt); // should be called only when point is outside
 };

### 2018-05-15 rvo2_main.cpp

@@ -49,6 +49,8 @@ int main(int argc, char** argv) {
 
   ifstream cfg(config_path);
 
+
+  nlohmann::json compareStats;
   nlohmann::json jsn = nlohmann::json::parse(cfg);
 
   string initial_trajectories_path = jsn["trajectories"];
@@ -66,6 +68,8 @@ int main(int argc, char** argv) {
   const double cell_size = jsn["cell_size"];
   const double v_max = jsn["v_max"];
   const double a_max = jsn["a_max"];
+
+  const bool enable_discrete = jsn["rvo2_enable_discrete"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
 
@@ -172,6 +176,7 @@ int main(int argc, char** argv) {
   output_json["dt"] = dt;//printdt;
   output_json["robot_radius"] = robot_radius;
   output_json["number_of_robots"] = original_trajectories.size();
+  compareStats["number_of_robots"] = original_trajectories.size();
   int steps_per_cycle = (dt / printdt)+0.5;
   int output_iter = 0;
 
@@ -182,6 +187,15 @@ int main(int argc, char** argv) {
       output_json["originals"][i]["y"].push_back(eu[1]);
     }
   }
+
+
+  vector<double> max_opt_times(original_trajectories.size(), -1);
+  vector<double> average_opt_times(original_trajectories.size(), 0);
+  vector<int> opt_counts(original_trajectories.size(), 0);
+  vector<int> obstacle_crash_counts(original_trajectories.size(), 0);
+  vector<int> obstacle_no_crash_counts(original_trajectories.size(), 0);
+  vector<int> robot_crash_counts(original_trajectories.size(), 0);
+  vector<int> robot_no_crash_counts(original_trajectories.size(), 0);
 
   // RVO2
   RVO::RVOSimulator sim;
@@ -213,9 +227,11 @@ int main(int argc, char** argv) {
   // Process obstacles so that they are accounted for in the simulation.
   sim.processObstacles();
 
+  std::chrono::time_point<std::chrono::high_resolution_clock> t_start, t_start_a_star, t_end_a_star, t_start_svm, t_end_svm, t_start_qp, t_end_qp;
   // main loop
   for(double ct = 0; ct <= total_t /*+ 5*/ /*!everyone_reached*/ ; ct+=dt) {
     for(int i=0; i<trajectories.size(); i++) {
+      t_start = Time::now();
       std::cout << "ct: " << ct << ", i: " << i << std::endl;
[…]

### 2018-05-15 vectoreuc.cpp

@@ -40,6 +40,7 @@ vectoreuc vectoreuc::operator/(const double& s) {
   return res;
 }
 
+
 vectoreuc vectoreuc::normalized() {
   vectoreuc res(crds.size());
   double length = 0;

### 2018-05-15 vis/compare.py

@@ -1,0 +1,177 @@
+import numpy as np
+import argparse
+
+import matplotlib.pyplot as plt
+from matplotlib import colors
+
+import json
+
+width = 0.35
+
+parser = argparse.ArgumentParser(description="compare stats")
+parser.add_argument('--rvo2', dest='rvo2')
+parser.add_argument('--rme', dest='rme')
+
+args = parser.parse_args()
+
+rvo2 = json.load(open(args.rvo2))
+rme = json.load(open(args.rme))
+
+if(rvo2["number_of_robots"] != rme["number_of_robots"]):
+    exit("Different number of robots")
+
+
+
+
+
+
+
+fig = plt.figure()
+ind = np.arange(rvo2["number_of_robots"])
+
+
+avg_cycles_rme = list(rme["average_cycle_times"])
+avg_cycles_rvo2 = list(rvo2["average_cycle_times"])
+ax = fig.add_subplot(231)
+
+
+rects1 = ax.bar(ind, avg_cycles_rme, width, color="royalblue")
+rects2 = ax.bar(ind+width, avg_cycles_rvo2, width, color="black")
+
+
+ax.set_ylabel('avg. cycle time')
+ax.set_xlabel('robot id')
+ax.set_title('Average Cycle Times')
+
+ax.set_xticks(ind+width/2)
+tpl = ()
+for i in range(1, rvo2["number_of_robots"]+1):
+    tpl += (i,)
+
+ax.set_xticklabels(tpl)
+ax.legend((rects1[0], rects2[0]), ("rme", "rvo2"))
+
+
+maximum_cycles_rme = list(rme["maximum_cycle_times"])
+maximum_cycles_rvo2 = list(rvo2["maximum_cycle_times"])
+ax2 = fig.add_subplot(232)
+rects3 = ax2.bar(ind, maximum_cycles_rme, width, color="royalblue")
+rects4 = ax2.bar(ind+width, maximum_cycles_rvo2, width, color="black")
+
+
+ax2.set_ylabel('max. cycle time')
+ax2.set_xlabel('robot id')
+ax2.set_title('Maximum Cycle Times')
+
+ax2.set_xticks(ind+width/2)
+tpl = ()
+for i in range(1, rvo2["number_of_robots"]+1):
+    tpl += (i,)
+
+ax2.set_xticklabels(tpl)
+ax2.legend((rects3[0], rects4[0]), ("rme", "rvo2"))
+
+
+
+
[…]

### 2018-05-15 main.cpp
rvo2 config

@@ -437,7 +437,7 @@ int main(int argc, char** argv) {
       bool original_traj_occupied = og.occupied(original_trajectories[i], robot_radius, ct, min(ct+hor, total_times[i]));
 
       bool discretePath = false;
-      if (planned_traj_occupied /*|| goal_occupied*/ || voronoi_violated || original_traj_occupied) {
+      if (planned_traj_occupied || /*goal_occupied ||*/ voronoi_violated || original_traj_occupied) {
         // the trajectory is now on top of an obstacle => discrete re-planning!
         bool discretePlanningNeeded = true;
 

### 2018-05-16 main.cpp
test fixes

@@ -91,6 +91,7 @@ int main(int argc, char** argv) {
   const double lambda_min_der_jerk = jsn["lambda_min_der_jerk"];
   const double lambda_min_der_snap = jsn["lambda_min_der_snap"];
   const double scaling_multiplier = jsn["scaling_multiplier"];
+  const double additional_time = jsn["additional_time"];
 
   bool enable_voronoi = jsn["enable_voronoi"];
 
@@ -204,6 +205,7 @@ int main(int argc, char** argv) {
       }
     }
   }
+  cout << "obs count: " << cell_based_obstacles.size() << endl;
   SvmSeperator svm(&cell_based_obstacles);
 
 /*
@@ -301,7 +303,7 @@ int main(int argc, char** argv) {
   vector<int> robot_crash_counts(original_trajectories.size(), 0);
   vector<int> robot_no_crash_counts(original_trajectories.size(), 0);
 
-  for(double ct = 0; ct <= total_t /*+ 5*/ /*!everyone_reached*/ ; ct+=dt) {
+  for(double ct = 0; ct <= total_t + additional_time/*+ 5*/ && !everyone_reached ; ct+=dt) {
 
     outStats << ct;
 
@@ -810,7 +812,7 @@ int main(int argc, char** argv) {
       // construct QP matrices
       ObjectiveBuilder ob(problem_dimension, pieceDurations);
 
-      double remaining_time = std::max(total_times[i] - ct, curve_count * dt * 1.1);
+      double remaining_time = std::max(total_times[i] - ct, curve_count * dt * 10.1);
       double factor = lambda_min_der / remaining_time;
       ob.minDerivativeSquared(lambda_min_der_vel * factor, lambda_min_der_acc * factor, lambda_min_der_jerk * factor, lambda_min_der_snap * factor);
 
@@ -1050,7 +1052,7 @@ int main(int argc, char** argv) {
         if (simpleStatus != 0) {
 
           //std::cerr << "MPC failed" << endl;
-          qpOASES::QProblem qp2(numVars, numConstraints, qpOASES::HST_SEMIDEF);
+          /*qpOASES::QProblem qp2(numVars, numConstraints, qpOASES::HST_SEMIDEF);
           qpOASES::Options opts2;
           opts2.setToReliable();
           opts2.printLevel = qpOASES::PL_LOW;
@@ -1067,7 +1069,7 @@ int main(int argc, char** argv) {
             set_max_time ? &cputime : NULL,
             y.data());
 
[…]

### 2018-05-16 svm_seperator.cpp

@@ -41,7 +41,7 @@ vector<hyperplane> SvmSeperator::_2_4_seperate() {
 
     result.push_back(_2pt4obspt_svm(pt1, pt2, obs1, obs2, obs3, obs4));
 
-    auto& hp = result.back();
+    /*auto& hp = result.back();
     for (auto& pt : obs.pts) {
       if (pt.dot(hp.normal) < hp.distance) {
         std::stringstream sstr;
@@ -58,7 +58,7 @@ vector<hyperplane> SvmSeperator::_2_4_seperate() {
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
-    }
+    }*/
 
   }
 
@@ -88,7 +88,7 @@ vector<hyperplane> SvmSeperator::_8_4_seperate() {
 
     result.push_back(_8pt4obspt_svm(pt1, pt2, pt3, pt4, pt5, pt6, pt7, pt8, obs1, obs2, obs3, obs4));
 
-    auto& hp = result.back();
+    /*auto& hp = result.back();
     for (auto& pt : obs.pts) {
       if (pt.dot(hp.normal) < hp.distance) {
         std::stringstream sstr;
@@ -105,7 +105,7 @@ vector<hyperplane> SvmSeperator::_8_4_seperate() {
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
-    }
+    }*/
 
   }
 
@@ -161,7 +161,7 @@ vector<hyperplane> SvmSeperator::_32_4_seperate() {
                                     pt25, pt26, pt27, pt28, pt29, pt30, pt31, pt32,
                                     obs1, obs2, obs3, obs4));
 
-    auto& hp = result.back();
+    /*auto& hp = result.back();
     for (auto& pt : obs.pts) {
       if (pt.dot(hp.normal) < hp.distance) {
         std::stringstream sstr;
@@ -178,7 +178,7 @@ vector<hyperplane> SvmSeperator::_32_4_seperate() {
         // throw runtime_error(sstr.str());
         std::cerr << sstr.str() << std::endl;
       }
-    }
+    }*/
 
   }
 

### 2018-05-16 paper/paper.tex
paper draft1

@@
 \usepackage{graphicx}
+%\usepackage{nicefrac}
 
@@
 % 
-\title{Distributed Realtime Trajectory Replanning for Robust Motion Execution in Multi-Robot Systems}
+\title{Distributed Real-time Trajectory Replanning for Robust Motion Execution}% in Multi-Robot Systems}
 
 %
-\titlerunning{Distributed Realtime Trajectory Replanning}  % abbreviated title (for running head)
+%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
 %                                     also used for the TOC unless
@@
 \begin{abstract}
-\keywords{trajectory planning, collision avoidance, multi-robot systems}
+We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, or robots breaking down.
+Robots do not communicate with each other and only need to be able to sense the other robots' positions and the obstacles.
+At the low-level, we use buffered voronoi cells as multi-robot collision avoidance strategy.
+At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
+The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
+Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
+We demonstrate our approach in simulation and on real robots, showcasing that it can operate in real-time.
+%\keywords{trajectory planning, collision avoidance, multi-robot systems}
 \end{abstract}
@@
 
-We propose robust motion execution as a framework that take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
-Consider the example in Fig.~\ref{fig:swap2:initial}, where two robots are tasked with swapping their position.
-The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the right location.
-Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories (see Fig.~\ref{fig:swap2:final}).
+We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
+Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their position.
+The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the correct location.
+Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories.
 Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.
@@
 \begin{figure}
-\centering
-\subfloat[Initial configuration.]{
-\includegraphics[width=0.48\textwidth]{images/swap2_initial.pdf}
-\label{fig:swap2:initial}
-}
+%\centering
+%\subfloat[Initial configuration and pre-planned trajectories.]{
+\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
+%\label{fig:swap2:initial}
+%}
 \hfill
-\subfloat[Final configuration and executed trajectories.]{
-\includegraphics[width=0.48\textwidth]{images/swap2_final.pdf}
-\label{fig:swap2:final}
-}
+%\subfloat[Final configuration and executed trajectories.]{
+\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
+%\label{fig:swap2:final}
+%}
 %\begin{subfigure}[t]{0.48\textwidth}
@@
 %\end{subfigure}
-\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
+\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
 The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
-Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
+Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the pre-planned trajectory (b).
 }
@@
 
-Robust motion execution is an extension of cooperative collision avoidance where our objective is to stay close to the originally planned trajectories as much as possible.
+Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
 In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
@@
 
-\todo{perhaps write some more about what experiments we did, after we have the material}
+%\todo{perhaps write some more about what experiments we did, after we have the material}
 
@@
     %\{\vp_i\}&:\text{ set of positions of all robots},\\
-    R_i(\vp)&:\text{ physical extend of robot $i$ at position $\vp$}, and\\
+    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
     \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
@@
 
-At time $t$ each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
+At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
+We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
 However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
@@
 Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
-\begin{align*}
+\begin{align}
+\begin{split}
     \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
@@
     \text{where } & t\in [0,T_i].
-\end{align*}
+\end{split}
+\label{eq:problem:opt}
+\end{align}
 
@@
 
+We now introduce important mathematical concepts and notation.
+
 \subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
@@
 The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
-\begin{align}
-    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
-    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
-\end{align}
+\begin{equation}
+    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
+    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
+    \label{voronoiAlphaBeta}
+\end{equation}
+% \begin{align}
+%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
+%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
+% \end{align}
 
@@
 For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most.
-We are using this fact in order to guarantee robot-to-robot collision avoidance.
+We use this property in order to avoid robot-to-robot collisions.
 
-The hyperspace $\cS_i^j$ has the following definition:
-\begin{align}
-    \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
-\end{align}
+Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$:
+\begin{equation}
+    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \text{ , where } \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}.
+    \label{voronoiEquation}
+\end{equation}
 
-Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
-\begin{align}
-    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
-\end{align}
+% \begin{align}
+%     \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
+% \end{align}
+
+% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
+% \begin{align}
+%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
+% \end{align}
 
@@
 \begin{align}
-    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
+    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
 \end{align}
 
-The curve starts at $\vP_0$ and ends at $\vP_d$.
-It does not interpolate the control points, but uses them to guide the curve.
-A B\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}.
-This is called the \emph{convex hull property of B\'ezier curves}.
-We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.
+The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve.
+A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
+%This is called the \emph{convex hull property of B\'ezier curves}.
+We use this property to avoid robot-to-obstacle collisions.
 
 We use splines as trajectories where each piece is a B\'ezier curve.
-Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at time step $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of $j^{th}$ piece, $\vf^{K}_{i,j}(t; T^{K}_{i,j})$ denotes the $j^{th}$ piece of the trajectory, $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of $j^{th}$ piece, and $P^{K}_{i,j,\rho}[u]$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $\rho \in \{0,1,...,d\}$, and $u \in \{1,2,...,n\}$.
+Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at iteration $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece, $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory, and $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $t\in[0, T^{K}_{i,j}]$, $j \in \{1,2,\ldots,l\}$ and $\rho \in \{0,1,\ldots,d\}$.
 
-\subsection{Support Vector Machine}\label{svmSection}
-A support vector machine is a supervised learning method that is used to classify data into several classes.
-In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
-The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
-The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
-\begin{align*}
-    \text{minimize}\ \ \  &\|\vw\|\\
-    \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
-\end{align*}
-We use SVMs to define collision free convex subspaces that are obstacle-free.
-\subsection{Trajectory Optimization} \label{trajectoryOptimization}
-A part of our replanning approach utilizes quadratic programming for trajectory optimization using control points of curves as decision variables.
+% \subsection{Support Vector Machine}\label{svmSection}
+% A support vector machine is a supervised learning method that is used to classify data into several classes.
+% In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
+% The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
+% The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
+% \begin{align*}
+%     \text{minimize}\ \ \  &\|\vw\|\\
+%     \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
+% \end{align*}
+% We use SVMs to define collision free convex subspaces that are obstacle-free.
+
+\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
+A part of our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
+The decision variables $\vx$ are all B\'ezier curve control points concatenated.
 The overall structure of our quadratic optimization problem is as follows:
-\begin{align*}
+\begin{align}
+\begin{split}
     \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
-    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA
+    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
     % &\vlb \leq \vx \leq \vub
-\end{align*}
+\end{split}
+\end{align}
 %, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.
@@
 There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
+An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative.
+A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
+We take the vector difference of those values and require it to be equal to $\vzero$.
+A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
+The construction of the QP is discussed in previous work~\cite{crazyplanning-ieeetro}.
 
-\begin{description}
-\item [Initial Point Constraints]
-An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
-This requires $n$ linear constraints on the control points, $n$ being the dimension we are working in.
+% There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
 
-\item[Continuity Constraints]
-A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ in the end to be equal to the curve $j+1$ in the beginning in any order of derivation.
-We take the vector difference of those values and require it to be equal to $\vzero$.
-This requires $n$ linear constraints on the control points.
+% \begin{description}
+% \item [Initial Point Constraints]
+% An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
+% This requires $n$ linear constraints on the control points. %, $n$ being the dimension we are working in.
 
-\item[Hyperspace Constraints]
-A hyperspace constraint requires a point of a curve to be on a specific side of a hyperplane.
-Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires $1$ linear constraint on the control points.
-\end{description}
+% \item[Continuity Constraints]
+% A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
+% We take the vector difference of those values and require it to be equal to $\vzero$.
+% This requires $n$ linear constraints on the control points.
+
+% \item[Hyperspace Constraints]
+% A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
+% Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires one linear constraint for each relevant control point.
+% \end{description}
+
+% The construction of the QP is discussed in more detail in previous work~\cite{crazyplanning-ieeetro}.
 
@@
 
-\subsection{Approach Overview}
-Our approach has three major components: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot.
+%\subsection{Approach Overview}
+Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
+The planning horizon $\tau'$ is automatically adjusted, but a user can provide the desired planning horizon $\tau$.
+In the following, we assume that the robots are spherical with a uniform radius $r_s$.
+%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.
 
-In each iteration $K$, each robot executes the flow chart outlined in Fig.
-~\ref{fig:flowchart}.
-Replanning is done at a fixed period of $\delta t$ and results in a trajectory $f^K_i(t)$ that is defined for $t\in [0,\tau]$, safe to execute up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.
-
+We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
 In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
@@
 We use this discrete path as an initial guess in trajectory optimization.
-If discrete planning is not required, we skip discrete search, and directly use the control points of the previous plan as the initial variables.
+If discrete planning is not required, we use the control points of the previous plan as the initial guess.
 
-Depending on whether discrete search is done or not, we construct the objective matrix $H$ and objective vector $g$ for trajectory optimization in a slightly different way.
-Exact difference in construction processes is explained in ~\ref{continuousOptimization}.
+We construct a QP with hard constraints for trajectory optimization in a slightly different way, depending if discrete planning was executed or not.
+In both cases, buffered voronoi cells are used to ensure collision-free operation for up to $\delta t$ and collisions with static obstacles are avoided for the planning horizon.
 
-Than, we compute the $A$ matrix that represents continuity, hyperspace, and initial point constraints.
-Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles.
-Since quadratic optimization requires constraints to be linear and dynamic limits can't be represented as linear constraints, we check dynamic limit violations not during trajectory optimization but in the temporal rescaling stage that runs after optimization.
-As long as dynamic limits are violated, we increase durations of pieces and do the optimization again until dynamic limits are not violated.
-In the end, we have a trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
+Dynamic limits cannot be represented as linear constraints in our QP.
+Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
+As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving the QP.
+
+At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
 
 \begin{figure}
+\centering
 %\begin{adjustbox}{width=\textwidth,caption={bla}}
-\resizebox{\textwidth}{!}{
+\resizebox{0.9\textwidth}{!}{
 % \footnotesize
 \begin{tikzpicture}[node distance = 2cm]
-    \node (discrete) [decision, text width=2cm] {need discrete replanning?};
-    \node (discretesearch) [process, right of=discrete, xshift=1.2cm, yshift = 1cm, text width = 2cm] {discrete search};
-    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {discrete objective builder};
-    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {continuous objective builder};
-    \node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
-    {constraint builder};
-    \node (trajopt) [process, right of=constraintbuild, xshift = 1cm, text width = 2cm] {trajectory optimization};
-    \node (dynamiclimits) [decision, right of=trajopt, xshift = 1.5cm, text width = 2cm] {dynamic limits violated?};
-    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
+    \node (discrete) [decision, text width=2cm] {Discrete replanning required?};
+    \node (discretesearch) [process, right of=discrete, xshift=1.5cm, yshift = 1cm, text width = 2cm] {Discrete Search};
+    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {Construct QP};
+    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {Construct QP};
+    %\node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
+    %{constraint builder};
+    \node (trajopt) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width = 2.5cm] {Trajectory Optimization};
+    \node (dynamiclimits) [decision, right of=trajopt, xshift = 2.0cm, text width = 2cm] {Dynamic limits violated?};
+    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {Rescaling};
     %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};
@@
 
-    \draw [arrow] (discrete) -- node[anchor=south] {yes} (discretesearch);
-    \draw [arrow] (discrete) -- node[anchor=north] {no} (contobjbuild);
+    \draw [arrow] (discrete) -- node[anchor=south] {Yes} (discretesearch);
+    \draw [arrow] (discrete) -- node[anchor=north] {No} (contobjbuild);
     \draw [arrow] (discretesearch) -- (discobjbuild);
-    \draw [arrow] (discobjbuild) -- (constraintbuild);
-    \draw [arrow] (contobjbuild) -- (constraintbuild);
-    \draw [arrow] (constraintbuild) -- (trajopt);
+    \draw [arrow] (discobjbuild) -- (trajopt);
+    \draw [arrow] (contobjbuild) -- (trajopt);
+    %\draw [arrow] (constraintbuild) -- (trajopt);
     \draw [arrow] (trajopt) -- (dynamiclimits);
-    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {no} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {start next iteration} -|   (discrete);
-    \draw [arrow] (dynamiclimits) -- node[anchor=east] {yes} (rescale);
+    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Start next iteration} -|   (discrete);
+    \draw [arrow] (dynamiclimits) -- node[anchor=east] {Yes} (rescale);
     \draw [arrow] (rescale) -| (trajopt);
 
-    \node[right = 0cm of c1, yshift=0.3cm] {Discrete planning};
-    \node[right = 0cm of c5, yshift=0.3cm] {Continuous optimization};
-    \node[right = 0cm of c9, yshift=0.3cm] {Temporal rescaling};
+    \node[right = 0cm of c1, yshift=0.3cm] {Discrete Planning (\ref{discretePlanning})};
+    \node[right = 0cm of c5, yshift=0.3cm] {Continuous Optimization (\ref{continuousOptimization})};
+    \node[right = 0cm of c9, yshift=0.3cm] {Temporal Rescaling (\ref{temporalRescaling})};
 
@@
 
-We execute discrete planning if any of the following conditions is true:
+Robot $i$ executes discrete planning if any of the following conditions is true:
 \begin{enumerate}
-    \item The original trajectory is not collision-free for the time horizon, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(\psi)) \cap \cO(\psi) \neq \emptyset$,
-    \item The first piece of the planned trajectory is outside robot $i$'s buffered voronoi cell, i.e., $\exists t\in [0, T^{K}_{i,1}] : \vf^{K}_{i,1}(t; T^{K}_{i,1}) \not\in \cV_i(\psi)$, or
-    \item The planned trajectory is not collision-free for the time horizon, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K}_i(t)) \cap \cO(\psi) \neq \emptyset$.
+    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
+    \item The first piece of the previously planned trajectory is outside the robot's buffered voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
+    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
 \end{enumerate}
-The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles dynamic obstacles.
+The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles numeric issues and dynamic obstacles.
 
@@
 In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
-Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path using a uniform velocity.
+Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path with constant speed.
 However, to guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.
 
-An example is shown in Fig.~\ref{fig:swap2:discrete}. 
+An example is shown in Fig.~\ref{fig:swap2_2} (a). 
 Discrete planning is executed because the original trajectory (green dashed line) passes through an obstacle.
@@
 
-%\todo{need a statement that piece duration is at least delta t}
-
-%\todo{when is ct introduced now?}
-
-%WOLFGANG (text + pics)
-
 \begin{figure}
 \centering
-\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
+%\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
 \includegraphics[width=0.45\textwidth]{images/swap2_discrete.pdf}
-\label{fig:swap2:discrete}
-}
+%\label{fig:swap2:discrete}
+%}
 \hfill
-\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
+%\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
 \includegraphics[width=0.45\textwidth]{images/swap2_cont_red.pdf}
-\label{fig:swap2:cont}
-}
+%\label{fig:swap2:cont}
+%}
 % \begin{subfigure}[t]{0.48\textwidth}
@@
 \caption{
-Snapshot at $t=3.9$.
+Example at $t=\SI{3.9}{s}$.
+Discrete path around an obstacle and other robot back to the original trajectory (a).
+Continuous trajectory split into four pieces and respective hyperspaces (b).
 }
@@
 \subsection{Continuous Optimization}\label{continuousOptimization}
-In this stage, a quadratic optimization problem is solved where variables are the control points of the pieces concatenated together.
-If discrete planning is not performed, initial variables are copied from the previous iteration, and durations are set uniformly to $\frac{min(\tau,T_i-\psi)}{l}$.
+We compute a new trajectory by formulating a quadratic optimization problem where the decision variables are the control points of the pieces concatenated together.
+If discrete planning is not performed, initial guesses of the decision variables are copied from the previous iteration, and the durations $T^{K}_{i,j}$ are set uniformly to $\frac{\min(\tau,T_i-\psi)}{l}$.
 If discrete planning is performed, initial variables and durations are calculated from the discrete path as explained in Section~\ref{discretePlanning}.
-The objective $\cC$ that we minimize is defined as
+The objective that we minimize is defined as
 \begin{align}
-    \cC = \sum_{e=1}^{\cE} \lambda_e\int_{0}^{T^K_i} \left\|\frac{d^e\vf^{K}_i(t)}{dt^e}\right\|^2dt + \sum_{j=1}^{l} \theta_j \left\|\vP^{K}_{i,j,d} - \vchi_{j}\right\|^2 \label{costFunction}
+    \sum_{e=1}^{\cE} \lambda_e\int_{0}^{T^K_i} \left\|\frac{d^e\vf^{K}_i(t)}{dt^e}\right\|^2dt + \sum_{j=1}^{l} \theta_j \left\|\vP^{K}_{i,j,d} - \vchi_{j}\right\|^2 \label{costFunction}
 \end{align}
-where $\vchi_j$ is the point we want piece $j$ to end at. Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
+where $\vchi_j$ is the point we want piece $j$ to end at.
+%Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
 
-The first term of $\cC$ is the combination of integrated squared derivatives with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
-The second term of $\cC$ penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
-In case discrete planning is performed, we require the end point of last piece to be in the final position of the discrete plan and do not constrain other pieces.
-If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
-This is an approximation we make for the cost function defined in Section~\ref{problemFormulation}.
-The construction of $H$ matrix defined in Section~\ref{trajectoryOptimization} for the first term is explained in \cite{crazyplanning-ieeetro}.
-The second term is a quadratic function of control points, hence it can be converted to an $H$ matrix and a $g$ vector as well.
+The first term of the objective is the combination of integrated squared derivatives with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
+The second term of the objective penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
+In case discrete planning is performed, we attempt to keep the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value,  $\vchi_l = P^K_{i,l,d}$, and $\theta_j = 0, \forall j < l$.
+If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
+%If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
+This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
+Matrix $H$ (see Section~\ref{trajectoryOptimization}) can be constructed for the first term of our objective~\cite{crazyplanning-ieeetro}.
+%The construction of matrix $H$, as defined in Section~\ref{trajectoryOptimization}, for the first term of our objective function is explained in \cite{crazyplanning-ieeetro}.
+The second term is a quadratic function of the control points; hence it is straightforward to construct the $H$ matrix and the $\vg$ vector.
 
-For robot-to-robot collision avoidance, the buffered voronoi hyperplanes are computed according to equations \eqref{voronoiAlpha} and \eqref{voronoiBeta}.
-For each control point of the first piece, we add $m-1$ hyperspace constraints as
-\begin{align}
-    \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
-\end{align}
+For robot-to-robot collision avoidance, the buffered voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
+% . For each control point of the first piece, we add $m-1$ hyperspace constraints as
+% \begin{align}
+%     \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
+% \end{align}
+These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
+As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
 
-These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
-As long as $T^{i,K}_1 \geq \delta t$ and all other robots stay inside their voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
-A sample buffered voronoi decomposition of the space is presented in Fig.~\ref{fig:swap2:voronoi}.
+For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO(\psi)$ for each curve piece $j$.
+Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$ that can, for example, be computed using support vector machines~\cite{SVM}.
+We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
+We add hyperspace constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each hyperplane $M_j^b$
+These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau'$.
+In case discrete planning was executed, we additionally treat other robots as static obstacles.
+Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for a $l=4$ trajectory.
 
-Remember at current global time $\psi$, $\cO(\psi)$ represents the occupied space.
-For each piece $j$, we calculate a set of SVM hyperplanes where hyperplane $M_j^b$ separates the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$ using the method presented in Section~\ref{svmSection}.
-We shift these hyperplanes first towards to the obstacle than shift them back using the radius $r_i$ to account for the physical extend of the robot.
-We add hyperplane constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each $M_j^b$ where $b\in \{1,2,...O\}$, $O$ being the number of non-occupied cells.
-These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau$.
-Fig.~\ref{fig:swap2:cont} shows the effective set of SVM hyperspaces for a $4$ piece trajectory.
+Moreover, we add continuity constraints that enforces continuity requirement between pieces and initial point constraints.
 
-After that we add continuity constraints that enforces continuity requirement between pieces.
+All constraints are linear and the constraint matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
+The number of decision variables in our QP is $l(d+1)n$.
+Let $\uptheta'$ describe the number of considered static obstacles, i.e., $\uptheta'$ is equal to $\uptheta + (m-1)$ if discrete planning was performed and $\uptheta$ otherwise.
+We add $(m-1)(d+1) + \uptheta' l(d+1) + (c+1)nl$ linear constraints, where the terms refer to the voronoi hyperspace, obstacle hyperspace, and continuity constraints, respectively.
+For our example in Fig.~\ref{fig:swap2_2}, we have $n=2$, $m=2$, $d=7$, $l=4$, and $c=2$. Thus, we have 64 decision variables and $8 + 128 + 24$ linear constraints.
 
-Lastly, we add initial point constraints that enforce 
-\begin{align*}
-\frac{d^j\vf^{K}_i}{dt^j}(0) &= \frac{d^j\vp_i}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
-\end{align*}
+% Lastly, we add initial point constraints that enforce 
+% \begin{align*}
+% \frac{d^j\vf^{K}_i}{dt^j}(0) &= \frac{d^j\vp_i}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
+% \end{align*}
 
-All these constraints are linear as explained in Section~\ref{trajectoryOptimization}. Therefore, we indeed have a constructible quadratic optimization problem.
+% All these constraints are linear as explained in Section~\ref{trajectoryOptimization}. Therefore, we indeed have a constructible quadratic optimization problem.
 
-For an instance of a problem in dimension $n$ where the trajectory has $l$ pieces of degree $d$, number of variables in the optimization is $l(d+1)n$.
-Therefore the dimensins of the matrix $H$ is $l(d+1)n\times l(d+1)n$ and the vector $\vg$ is $l(d+1)\times 1$.
-If there are $m$ robots in the environment, buffered voronoi decomposition imposes $(m-1)(d+1)$ linear constraints.
-If there number of obstacles in the environment is $\uptheta$, SVM seperations impose $\uptheta l (d+1)$ linear constraints.
+% For an instance of a problem in dimension $n$ where the trajectory has $l$ pieces of degree $d$, the number of variables in the optimization is $l(d+1)n$.
+% %Therefore the dimensions of the matrix $H$ is $l(d+1)n\times l(d+1)n$ and the vector $\vg$ is $l(d+1)\times 1$.
+% If there are $m$ robots in the environment, buffered voronoi decomposition imposes $(m-1)(d+1)$ linear constraints.
+% If there number of obstacles in the environment is $\uptheta$, SVM seperations impose $\uptheta l (d+1)$ linear constraints.
 If maximum required continuity is $c$, continuity requirements impose $(c+1)nl$ linear constraints.
 Therefore the matrix $A$ has $(m-1)(d+1) + \uptheta l(d+1) + (c+1)nl$ rows in total.
-For example, in 2-dimensional space with $4$ robots where the trajectory has $4$ pieces of degree $7$, the environment is occupied with $10$ obstacles and $C^{2}$ continuity is required, the number of variables would be $64$, and the number of linear constraints would be $368$.
+% For example, in 2-dimensional space with $4$ robots where the trajectory has $4$ pieces of degree $7$, the environment is occupied with $10$ obstacles and $C^{2}$ continuity is required, the number of variables would be $64$, and the number of linear constraints would be $368$.
 
@@
 
-\subsection{Temporal Rescaling} % might be part of overview
-Since we use fixed durations for pieces and do not account for the dynamic limits of the robot during optimization, the resulting trajectory may violate dynamic limits of the robot.
-After trajectory optimization, we calculate the maximum magnitudes $\Gamma_j$ of $j^{th}$ derivatives of the curve, and check if for any $j$, $\Gamma_j > \gamma_j$, where $\gamma_j$ is the dynamic limit of the robot in $j^{th}$ derivation degree.
-If that is the case, we multiply durations $T^K_{i,j}$ of each piece by the same constant, and re-run the trajectory optimization with the same exact constraints using the previous result as the initial guess.
-If that is not the case, no temporal rescaling is needed and the trajectory is feasible.
+\subsection{Temporal Rescaling}  \label{temporalRescaling} % might be part of overview
+Since we use fixed durations of the pieces and do not account for the dynamic limits of the robot during optimization, the resulting trajectory may violate the dynamic limits of the robot.
+After trajectory optimization, we calculate the maximum magnitudes $\Gamma_j$ of $j^{th}$ derivatives of the curve, and check if there exists a $j$ such that $\Gamma_j > \gamma_j$, where $\gamma_j$ is the dynamic limit of the robot in $j^{th}$ derivation degree.
+If that is the case, we uniformly scale the piece durations $T^K_{i,j}$, and re-run the trajectory optimization with the same exact constraints using the previous result as the initial guess.
+If the dynamic limits are not violated, no temporal rescaling is needed and the trajectory is feasible.
 
@@
 \subsection{Theoretical Guarantees} %maybe
-\begin{enumerate}
-    \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
+To provide formal guarantees, we make the following assumptions:
+First, the robots have first-order integrator dynamics (and thus $c=0$);
+second, the execution of the robots in synchronous;
+third, robots execute trajectories perfectly;
+fourth, robot trajectories are initially valid up to time $\tau$; and
+fifth, obstacles are static.
+
+For robot-robot collision avoidance our approach uses buffered voronois cells and retains the same theoretical guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
+\begin{lemma}
+If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
+\end{lemma}
+
+For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, and then that the resulting QP is feasible.
+
+\begin{lemma}
+\label{lemma:hyperplanes}
+In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle.
+\end{lemma}
+\begin{proof}
+We consider two cases.
+In the first case, discrete planning was successfully executed in iteration $K$.
+Therefore, the discrete planner has found a collision free discrete path that separates the robot from all other obstacles and robots. 
+Because the initially guessed control points are set on top of this path, the corresponding hyperplanes $M_j^b$ must exist.
+
+In the second case, discrete planning was not executed (or failed to produce a path).
+In that case, we use the computed control points from the previous iteration $K-1$.
+By our assumption, the initial trajectories are valid up to time $\tau$.
+Thus, by induction, the previous iteration had a valid trajectory. This trajectory is still valid, since the obstacles cannot move and therefore new hyperplanes $M_j^b$ must exist.\qed
+\end{proof}
+
+\begin{lemma}
+In each iteration $K$, the constructed QP is feasible.
+\end{lemma}
+\begin{proof}
+We consider each of the three types of constraints that could render the QP infeasible.
+Hyperspace constraints can be fulfilled, because all hyperplanes exist according to Lemma~\ref{lemma:hyperplanes}.
+Initial point constraints are limited to one constraint by our assumption that $c=0$.
+Since the previous iteration $K-1$ produced a valid trajectory and the robot executed the trajectory perfectly, the initial point must be feasible.
+We have $l-1$ continuity constraints that constrain the position of the last control point of curve $j$ to be identical to the first control point of curve $j+1$.
+Those control points are already equal to each other for the initially guessed control points, no matter if discrete planning was executed or not.
+%In case discrete planning was successfully executed, the last and first control points share a corner of the discrete path.
+%In case discrete planning was not executed, the initially guessed control points are based on the result of the previous iteration $K-1$.
+Because those points do not violate any of the other constraints, the continuity constraints must be feasible.\qed
+\end{proof}
+
+All lemmas together show that our approach is collision free under the stated assumptions.
+Similar to other work, there are no formal liveness guarantees and there might be deadlocks~\cite{bufferedVoronoiCells}.
+Our approach also works in practice for robots with higher-order dynamics, if robot execution is asynchronous, or trajectories are not executed perfectly, although there is no formal guarantee.
+%This can be achieved by choosing larger safety radii~\cite{bufferedVoronoiCells}.
+
+%%%%
+
+% Our approach uses buffered voronoi cells and retains the same theoretical robot-robot collision guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
+% If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
+
+% We note that this only holds under two assumptions:
+% first, the robots have first-order integrator dynamics, and second, the execution of the robot is synchronous.
+% The first problem can be mitigated in practice by choosing larger safety radii~\cite{bufferedVoronoiCells}.
+% We propose to address the second problem by shifting the voronoi hyperplanes by $\delta t \gamma_1$ to account for the worst-case phase shift in the robots' execution cycle.
+
+% For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, assuming perfect trajectory execution:
+
+% \todo{need to remove third condition in discrete planning?}
+% % assume c=0 for proof
+
+% \begin{enumerate}
+%     \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
 The maximum phase shift between robots is $\delta t$.
@@
 This update gives \emph{no robot collision guarantee} even there is phase shift during the execution.
-    \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
-    \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
+%     \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
+%     \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
 If we know the maximum velocity $\nu$ of the obstacles in the environment, we can avoid moving obstacles as well by shifting the SVM seperating hyperplanes by $\nu \delta t $.
 This update gives \emph{no obstacle collision guarantee} even the obstacles are moving.
-\end{enumerate}
+% \end{enumerate}
 % see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
@@
 
-We implement our approach in C++.
+We implement our approach in C\texttt{++}.
 We use an occupancy grid as environment representation, because previous work has shown that such data structures can be updated in real-time on robots that are equipped with a LIDAR sensor or a RGB-D camera.
@@
 OctoMaps are memory efficient, but update operations can show high execution time variance.
-For local replanning, occupancy grids using ringbuffers as datastructures have been shown to achieve near constant execution time~\cite{replanning-usenko}.
-Our implementation uses a simple pre-initialized 2D occupancy grid such that a physical robot implementation could leverage existing OctoMap or occupancy ringbuffer libraries easily.
+For local replanning, occupancy grids using ring buffers as data structures have been shown to achieve near constant execution time~\cite{replanning-usenko}.
+Our implementation uses a simple pre-initialized 2D occupancy grid such that future implementations could leverage existing OctoMap or occupancy ring buffer libraries.
 
-We use the CVXGEN-package~\cite{cvxgen} to generate small QPs to find separating hyperplanes between controlpoints and obstacles.
+We use the CVXGEN-package~\cite{cvxgen} to generate small QPs to find separating hyperplanes between control points and obstacles.
 As QP solvers we test with qpOASES~\cite{qpOASES} and OSQP~\cite{osqp}; both are open source and have been shown to work well in model predictive control scenarios.
@@
 \subsection{Simulation}
-% scalability: #curves, #obstacles, #robots (voronoi constraint), qp-solver
-% compare success rate with RVO2
+We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) running Ubuntu 16.04.
+
+% table1: scalability: #curves, #obstacles, #robots (voronoi constraint), qp-solver
+% (one example (16 case or generate larger w/ 32))
+In a first experiment, we test the scalability of our method in terms of the number of curves $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
+Our results are summarized in Tables~\ref{tab:curveCountScalability}, \ref{tab:obstacleCountScalability} and \ref{tab:robotCountScalability}, where $t_{avg}$ is the average time that qpOASES takes per iteration.
+Our algorithm scales well with the number of robots.
+In terms of number of curves, our algorithm has almost the same performance up to $l=10$. For the simulations and physical experiments we did, we never needed more than $l=4$.
+The bottleneck of our algorithm is the number of occupied cells in the occupancy grid.
+However, as it can be seen in Table~\ref{tab:obstacleCountScalability}, our algorithm still has real-time capability when considering hundreds of occupied cells, assuming a \SI{10}{Hz} execution.
+When we use OSQP instead of qpOASES, our implementation takes significantly more time if we consider many obstacles.
+For example, when we do experiment $9$ using OSQP, it takes \SI{297}{ms} on average.
+
+\begin{table}[!htb]% 
+\begin{minipage}{.3\textwidth}
+    \centering
+    \begin{tabular}{|l|c|c|c|c|r|}
+        \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         1 & $1$ & $0$ & $4$ &$10$\\ \hline
+         2 & $4$ & $0$ & $4$ & $10$\\ \hline
+         3 & $8$ & $0$ & $4$ & $15$\\ \hline
+         4 & $10$ & $0$ & $4$ & $13$ \\ \hline
+         5 & $12$ & $0$ & $4$ & $27$ \\ \hline
+         6 & $16$ & $0$ & $4$ & $107$ \\ \hline
+         \multicolumn{5}{c}{}\\
+    \end{tabular}
+    \caption{Runtime with varying curve count $l$.}
+    \label{tab:curveCountScalability}
+\end{minipage}
+\hfill
+\begin{minipage}{.3\textwidth}
+    \centering
+    \begin{tabular}{|l|c|c|c|c|r|}
+        \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         7 & $4$ & $2$ & $4$ &$9$\\ \hline
+         8 & $4$ & $4$ & $4$ & $9$ \\ \hline
+         9 & $4$ & $62$ & $4$ & $28$ \\ \hline
+         10 & $4$ & $196$ & $4$ & $47$  \\ \hline
+         11 & $4$ & $213$ & $4$ & $69$  \\ \hline
+         12 & $4$ & $1250$ & $4$ & $253$  \\ \hline
+         \multicolumn{5}{c}{}\\
+    \end{tabular}
+    \caption{Runtime with varying occupied cells $\uptheta$.}
+    \label{tab:obstacleCountScalability}
+\end{minipage}
+\hfill
+\begin{minipage}{.3\textwidth}
+    \centering
+    \begin{tabular}{|l|c|c|c|c|r|}
+        \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         13 & $4$ & $5$ & $2$ &$10$\\ \hline
+         14 & $4$ & $5$ & $4$ &$9$\\ \hline
+         15 & $4$ & $5$ & $8$ & $10$ \\ \hline
+         16 & $4$ & $5$ & $16$ & $13$ \\ \hline
+         17 & $4$ & $5$ & $32$ & $15$  \\ \hline
+         18 & $4$ & $5$ & $64$ & $14$  \\ \hline
+         \multicolumn{5}{c}{}\\
+    \end{tabular}
+    \caption{Runtime with varying robot count $m$.}
+    \label{tab:robotCountScalability}
+\end{minipage}
+\end{table}
+
+We also compare our method (RME) to two different ORCA variants.
+We use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i(\psi)'$ if $\vp(\psi)\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp(\psi)}{\delta t}$ otherwise.
+In order to improve the behavior with obstacles, we combine ORCA in a different set of experiments with our discrete planning method (denoted as ORCA*).
+We use $l=4$ as the number of curves, and $d+1=8$ as the degree of B\'ezier curves.
+For RME we use $\delta t = \SI{0.1}{s}$ and for the ORCA variants $\delta t = \SI{0.01}{s}$.
+All algorithms are given more time (less than $20$ seconds in each case) than the original plans to complete because of the introduction of new obstacles to the environment.
+The results are summarized in Table~\ref{tab:rvo2Comparison}.
+Our method takes more time in computation, however is significantly better at avoiding collisions.
+All robots using RME reach their destinations, while robots using ORCA can get stuck as seen in all examples.
+Also, robots using ORCA are in invalid configurations (collisions) as much as 49\% of the time, while robots using RME are almost never in invalid configurations.
+Invalid configurations in RME can occur because of numerical problems.
+We also note that ORCA does not provide the same smoothness guarantees ($c=0$, i.e., velocities can jump between iterations) and that it requires to sense the other robot's velocities instead of positions only.
+A video showing some examples is available at \url{TODO}.
+
+\begin{table}
+%1 -> swap4, obsdiamond, +2 seconds
+%2 -> swapCircle6, swapCircle6, +3 seconds
+%3 -> swapCircle8, 3obstacles, +2 seconds (31 seconds original)
+%4 -> swapCircle16, obsdiamond, +12 seconds (22 seconds original)
+%5 -> swapCircle16, 3obstacles, +19 seconds (22 seconds original)
+    \centering
+    \begin{tabular}{ |l|  c|  c | c | c | c| c| c| c| c| c| r| }
+      \cline{4-12}
+       \multicolumn{3}{c|}{} & \multicolumn{3}{c| }{ORCA} & \multicolumn{3}{c| }{ORCA*} & \multicolumn{3}{c|}{RME}\\ \hline
+      \# & $m$ &  $\uptheta$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ \\ \hline
+      $1$ & $4$ & $2$ & $<1$ & $62$ & $2$ & $<1$ & $99$ & $3$ & $9$ & $100$ & $4$\\ \hline
+      $2$ & $6$ & $5$ & $<1$ & $63$ & $4$ & $<1$ & $72$ & $3$ & $11$ & $98$ & $6$\\ \hline
+      $3$ & $8$ & $5$ & $<1$ & $60$ & $5$ & $<1$ & $69$ & $8$ & $10$ & $99$ & $8$\\ \hline
+      $4$ & $16$ & $2$ & $<1$ & $58$ & $14$ & $<1$ & $58$ & $13$ & $11$ & $100$ & $16$\\ \hline
+      $5$ & $16$ & $5$ & $<1$ & $51$ & $13$ & $<1$ & $57$ & $11$ & $14$ & $98$ & $16$\\ \hline
+      \multicolumn{12}{c}{} \\
+    \end{tabular}
+    \caption{Comparison of RME with ORCA and ORCA* with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destination eventually ($s$).
+    %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
+    %$t_{avg}$ is the average time of computation in each iteration, $v_{min}$ is the minimum percentage of being in a collision-free (valid) configuration among all robots, and $s$ is the number of robots that reach to their destinations in the end.
+    }
+    \label{tab:rvo2Comparison}
+\end{table}
+% could talk about nlopt/ipopt "issues"; or: other subsection (e.g, other approaches)
+\subsection{Physical Robots}
+We implement our approach on six differential drive robots (iRobot Create2) that are equipped with one of ODROID C1+ or ODROID XU4 single-board computers.
+Those computers run Ubuntu 16.04 with ROS Kinetic, but C1+ has very limited computation capabilities (ARM Cortex-A5, max. \SI{10}{W}).
+The robots are arranged in a circle (\SI{2}{m} radius) and are tasked with swapping sides.
+We plan the original trajectories with one static obstacle using a centralized planner~\cite{crazyplanning-heterogeneous}.
+Each robot receives the position information of all other robots using a motion capture system.
+Trajectory tracking controller and our algorithm run on-board at a frequency of \SI{10}{Hz}.
+
+We conduct several experiments and add an additional obstacle, change the robots initial position, disturb the robots during run-time, or artificially stop one of the robots.
+In all cases robots successfully avoid collisions and in many cases they reach their final destination within the originally planned time limit.
+We also saw a few cases where robots got into a deadlock, which we attribute to the fact that the robots, unlike the simulation, cannot execute very low velocity commands.
+A video of our experiment is available at \url{TODO}.
+
+% \todo{screenshot?}
+%\todo{add url}
+
 %    describe typical examples (inline with the introduction)
-
-% could talk about nlopt/ipopt "issues"; or: other subsection (e.g, other approaches)
-
-\subsection{Physical Robots}
+% potentially add picture real vs sim?
 
@@
 Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
-Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi partition shifted by the physical extent of the robot. 
+Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
 Safety barrier certificates achieves collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
 All approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
-Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVO), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}).
+Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}).
 
-Our realtime planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
+Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
 Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
@@
 Using a discrete plan (generated by RRT*), polynomial trajectories can be generated using a quadratic program~\cite{richterISRR}.
-In this case a unconstrained QP-formulation might be used, but obstacles cannot be directly taken into account.
+In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
 Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
@@
 
+We present robust motion execution, a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
+Our approach does not require communication between the robots and provides formal collision guarantees for simple robot models.
+We use a novel planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
+We demonstrate in simulation and on physical robots that we can generate smooth trajectories in real-time, while avoiding collisions and deadlocks more successfully compared to ORCA.
+
+In future work we would like to conduct additional experiments with flying robots, handle dynamic obstacles, and consider the ability of robots to communicate to improve their plans.
+
+% future work
+% * how to get out of invalid states "as safe as possible"
+% * dynamic obstacles (w/ upper velocity bound)
+% * physical experiment w/ sensing
+% * 3D (drones w/ downwash)
+% * allow some communication (e.g., exchange planned control points) => can performance be improved?
+
 %
@@
 
-\section{TODO}
+% \section{TODO}
 
-\todo{why are functions marked as vectors?}
+% \todo{why are functions marked as vectors?}
+% %\todo{constraints are also slightly different for discrete vs. continuous}
+% %\todo{if discrete planning fails, we might not be able to compute separating hyperplanes!}
+% %\todo{$tau'$ so far only defined if discrete stage is executed!}
+
+% %BASKIN:
+% % * ros planning node
+% % * statistics python script for #robots succeed and #time invalid state (collision with other robots or obstacles)
+% * "evaluation framework"/automation to generate evaluation results
+
+% %WOLFGANG
+% % * traj controller C++ node for creates (including custom messages)
+% % * add realistic 6-robot example case
+% % * update sections 4.2 onwards
+%  * add video export to vis.py
+
+%Sunday:
+% * Meet at 10m warehouse
+% * test & tune create2 traj controller
+% * test planner
+% * record 4 videos (6 to 8 robots):
+%   * normal execution
+%   * execution w/ added obstacle
+%   * execution w/ motion manually disturbed
+%   * execution w/ robot(s) breaking in middle
 

### 2018-05-16 vis/vis.py
add option to export video

@@ -272,15 +272,36 @@ if __name__ == "__main__":
   parser.add_argument('--no-hyperplanes', dest='hyperplanes', action='store_false')
   parser.set_defaults(hyperplanes=True)
 
+  parser.add_argument('--video', dest='video', default=None, help="output video file (or leave empty to show on screen)")
+
   args = parser.parse_args()
 
   jsn = json.load(open(args.file))
 
   colors = ['b', 'g', 'r', 'c', 'm', 'k'] * 10
 
-  fig = plt.figure()
-  ax = plt.axes(xlim=(-4,4), ylim=(-4,4))
-  ax.set_aspect('equal')
+  # fig = plt.figure()
+  # ax = plt.axes(xlim=(-4,4), ylim=(-4,4))
+  # ax.set_aspect('equal')
+  xmin = -2.5
+  xmax = 2.5
+  ymin = -1.0
+  ymax = 2.5
+
+  aspect = (xmax - xmin) / (ymax - ymin)
+
+  if args.video:
+    fig = plt.figure(frameon=False, figsize=(6 * aspect, 6))
+    ax = fig.add_subplot(111, aspect='equal')
+    fig.subplots_adjust(left=0,right=1,bottom=0,top=1, wspace=None, hspace=None)
+  else:
+    fig = plt.figure()
+    ax = plt.axes(xlim=(-4,4), ylim=(-4,4))
+    ax.set_aspect('equal')
+
+  plt.xlim(xmin, xmax)
+  plt.ylim(ymin, ymax)
+
   # plt.axis('off')
   time_text = ax.text(0.02, 0.95, '', transform=ax.transAxes)
   trajectories = dict()
@@ -393,8 +414,16 @@ if __name__ == "__main__":
   step = False
   frameId = 0
   numFrames = len(jsn["points"])
-  # fig.canvas.mpl_connect('button_press_event', onClick)
-  fig.canvas.mpl_connect('key_press_event', onKey)
-  anim = animation.FuncAnimation(fig, animate, init_func=init,frames=frameGen,interval=jsn["dt"]*1000,blit=args.blit,repeat=True)
 
-  plt.show()
+  if args.video:
+    SPEED = 1
+    anim = animation.FuncAnimation(fig, animate, init_func=init, frames=range(0, numFrames, args.frameinc))
+    anim.save(
+      args.video,
+      "ffmpeg",
+      fps=1.0 / jsn["dt"] / args.frameinc * SPEED,
[…]

### 2018-05-17 vis/vis.py
plot discrete path correctly even if frameinc is != 10

@@ -192,7 +192,7 @@ def animate(frame):
         for i in robots:
           if i < len(jsn["discrete_plan"][frame]) and jsn["discrete_plan"][frame][i]:
             discrete_plans[i].set_data(jsn["discrete_plan"][frame][i]["x"], jsn["discrete_plan"][frame][i]["y"])
-    else:
+    elif frame % 10 == 0:
         for i in robots:
             discrete_plans[i].set_data([], [])
 

### 2018-05-17 rvo2_main.cpp
updated rvo2 discrete planning

@@ -369,7 +369,7 @@ int main(int argc, char** argv) {
             current_discrete_path_length += sqrt(pow(corners[j].first - corners[j-1].first, 2) +
                                                  pow(corners[j].second - corners[j-1].second, 2));
 
-            if ((pt - curPos).L2norm() > 0.2) {
+            if ((pt - curPos).L2norm() > cell_size / sqrt(2)) {
               // attempt to reach next goal point by the desired time
               double timeToReach = current_discrete_path_length / total_discrete_path_length * discrete_horizon;
               vectoreuc vel = (pt - curPos) / timeToReach;

### 2018-05-17 vis/vis.py

@@ -192,6 +192,8 @@ def animate(frame):
         for i in robots:
           if i < len(jsn["discrete_plan"][frame]) and jsn["discrete_plan"][frame][i]:
             discrete_plans[i].set_data(jsn["discrete_plan"][frame][i]["x"], jsn["discrete_plan"][frame][i]["y"])
+          else:
+            discrete_plans[i].set_data([], [])
     elif frame % 10 == 0:
         for i in robots:
             discrete_plans[i].set_data([], [])
@@ -283,10 +285,10 @@ if __name__ == "__main__":
   # fig = plt.figure()
   # ax = plt.axes(xlim=(-4,4), ylim=(-4,4))
   # ax.set_aspect('equal')
-  xmin = -2.5
-  xmax = 2.5
-  ymin = -1.0
-  ymax = 2.5
+  xmin = -5
+  xmax = 4
+  ymin = -4
+  ymax = 4
 
   aspect = (xmax - xmin) / (ymax - ymin)
 

### 2018-05-17 paper/paper.tex
paper draft2

@@
                 shadows, shapes.geometric, shapes.misc}
+\usepackage[utf8]{inputenc}
+
+\inputencoding{utf8}
 
@@
 %
-\author{Baskin Senbaslar \and Wolfgang H\"onig \and
+\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
 Nora Ayanian}
@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\tocauthor{Baskin Senbaslar, Wolfgang H\"onig, Nora Ayanian}
+\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
 %
@@
 \begin{abstract}
-We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, or robots breaking down.
-Robots do not communicate with each other and only need to be able to sense the other robots' positions and the obstacles.
-At the low-level, we use buffered voronoi cells as multi-robot collision avoidance strategy.
+We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
+Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
+At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
 At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
@@
 Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
-We demonstrate our approach in simulation and on real robots, showcasing that it can operate in real-time.
+We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
 %\keywords{trajectory planning, collision avoidance, multi-robot systems}
@@
 Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
-However, all such solutions assume that the resulting trajectories can be executed approximately perfectly, which is in particular not true for teams of hundreds of robots that have to operate persistently.
+All such solutions assume that the resulting trajectories can be executed approximately perfectly, which is not true for teams of hundreds of robots that have to operate persistently.
 
-We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
-Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their position.
-The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the correct location.
-Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories.
-Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.
+We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, robots breaking down, or external disturbances.
+Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their positions.
+The pre-planned trajectories are collision-free, but neither considers the new obstacle nor that the fact that blue robot does not start at its correct location.
+Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories.
+Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and the obstacles around them.
 
@@
 Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
-At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
+At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with a dynamic receding horizon approach.
 The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.
@@
     R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
-    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
+    \gamma_j&: \text{ dynamic limit of the robot for $j^{th}$ derivation degree}.%\\
     %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
@@
 We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
-However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
+Robots cannot communicate with each other and are unaware of the other robots' trajectories.
 %Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
-Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
+Each robot $i$ needs to execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
 \begin{align}
@@
     &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
-    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
+    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
     &\vf_i(t)\text{ is collision free, and}\\ 
-    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
+    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j\text{ for all desired $j$s},\\
     \text{where } & t\in [0,T_i].
@@
 
-We approximately solve this problem using a dynamic receding horizon approach.
-At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position.
-We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.
+We approximately solve this problem iteratively using a dynamic receding horizon approach.
+At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
+%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.
 
@@
 
-We now introduce important mathematical concepts and notation.
+We now introduce important mathematical concepts and notations we use.
 
 \subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
-Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
+Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
 \begin{align}
@@
 
-The set of all buffered voronoi cells is called the buffered voronoi decomposition of the space.
-For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most.
+% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
+For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside at most one of the buffered Voronoi cells.
 We use this property in order to avoid robot-to-robot collisions.
 
-Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$:
+Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$ as follows:
 \begin{equation}
@@
 
-Thus, we can compute the buffered voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.
+Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.
 
@@
 
-The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve.
+The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
 A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
@@
 We use splines as trajectories where each piece is a B\'ezier curve.
-Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at iteration $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece, $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory, and $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $t\in[0, T^{K}_{i,j}]$, $j \in \{1,2,\ldots,l\}$ and $\rho \in \{0,1,\ldots,d\}$.
+Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece where $j \in \{1,2,\ldots,l\}$.
+$\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$.
+$\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $\rho \in \{0,1,\ldots,d\}$.
 
@@
 An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative.
-A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
-We take the vector difference of those values and require it to be equal to $\vzero$.
-A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
-The construction of the QP is discussed in previous work~\cite{crazyplanning-ieeetro}.
+This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
+A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
+We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
+A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane.
+If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points.
+All 3 types of constraints are linear in control points, and the exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.
 
@@
 Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
-The planning horizon $\tau'$ is automatically adjusted, but a user can provide the desired planning horizon $\tau$.
+The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
 In the following, we assume that the robots are spherical with a uniform radius $r_s$.
@@
 We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
-In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
-If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
-We use this discrete path as an initial guess in trajectory optimization.
-If discrete planning is not required, we use the control points of the previous plan as the initial guess.
+%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
+%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
+%We use this discrete path as an initial guess in trajectory optimization.
+%If discrete planning is not required, we use the control points of the previous plan as the initial guess.
 
-We construct a QP with hard constraints for trajectory optimization in a slightly different way, depending if discrete planning was executed or not.
-In both cases, buffered voronoi cells are used to ensure collision-free operation for up to $\delta t$ and collisions with static obstacles are avoided for the planning horizon.
+%We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
+%In both cases, buffered Voronoi cells are used to ensure collision-free operation for up to time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.
 
-Dynamic limits cannot be represented as linear constraints in our QP.
-Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
-As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving the QP.
+%Dynamic limits cannot be represented as linear constraints in our QP.
+%Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
+%As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving of the QP.
 
-At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
+%At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
+We execute this trajectory for a period of $\delta t$ and replan for the next iteration.
 
@@
 
-In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered voronoi cell $\cV_i(\psi)$.
+In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i(\psi)$.
 We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.
 
-Robot $i$ executes discrete planning if any of the following conditions is true:
+Robot $i$ executes discrete planning if any of the following conditions are true:
 \begin{enumerate}
     \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
-    \item The first piece of the previously planned trajectory is outside the robot's buffered voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
+    \item The first piece of the previously planned trajectory is outside the robot's buffered Voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
     \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
 \end{enumerate}
-The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles numeric issues and dynamic obstacles.
+The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear and robots move towards each other a lot, and the third condition handles numeric issues and dynamic obstacles.
 
 Discrete planning uses a dynamic receding horizon approach.
-First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free with respect to both obstacles and other robots.
+First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free at time $\psi + \tau'$ with respect to both obstacles and other robots.
 Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
-If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage.
+If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage and construct QP as if discrete planning was not required.
 Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
 In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
-Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path with constant speed.
-However, to guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.
+Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at $\vo_i(\psi+\tau')$ if we followed the discrete path with constant speed.
+To guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.
 
@@
 
-The first term of the objective is the combination of integrated squared derivatives with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
+The first term of the objective is the combination of integrated squared derivatives up to degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro}.
+It minimizes the energy through curve.
+%richterISRR
 The second term of the objective penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
-In case discrete planning is performed, we attempt to keep the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value,  $\vchi_l = P^K_{i,l,d}$, and $\theta_j = 0, \forall j < l$.
+In case discrete planning is performed, we attempt to get to the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value, enforcing $\vP^K_{i,l,d} = \vchi_l$, and $\theta_j = 0, \forall j < l$.
 If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
 %If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
-This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
+%This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
 Matrix $H$ (see Section~\ref{trajectoryOptimization}) can be constructed for the first term of our objective~\cite{crazyplanning-ieeetro}.
@@
 
-For robot-to-robot collision avoidance, the buffered voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
+For robot-to-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
 % . For each control point of the first piece, we add $m-1$ hyperspace constraints as
@@
 These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
-As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
+As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
 
 For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO(\psi)$ for each curve piece $j$.
-Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$ that can, for example, be computed using support vector machines~\cite{SVM}.
+Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$.
+That can, for example, be computed using support vector machines~\cite{SVM}.
 We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
@@
 In case discrete planning was executed, we additionally treat other robots as static obstacles.
-Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for a $l=4$ trajectory.
+Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for our example.
 
-Moreover, we add continuity constraints that enforces continuity requirement between pieces and initial point constraints.
+Moreover, we add continuity constraints that enforce continuity requirement between pieces.
+Then, we add initial point constraints that enforce continuity requirements in the beginning that ensures continuity between iterations.
 
-All constraints are linear and the constraint matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
+All constraints are linear and matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
 The number of decision variables in our QP is $l(d+1)n$.
 Let $\uptheta'$ describe the number of considered static obstacles, i.e., $\uptheta'$ is equal to $\uptheta + (m-1)$ if discrete planning was performed and $\uptheta$ otherwise.
-We add $(m-1)(d+1) + \uptheta' l(d+1) + (c+1)nl$ linear constraints, where the terms refer to the voronoi hyperspace, obstacle hyperspace, and continuity constraints, respectively.
-For our example in Fig.~\ref{fig:swap2_2}, we have $n=2$, $m=2$, $d=7$, $l=4$, and $c=2$. Thus, we have 64 decision variables and $8 + 128 + 24$ linear constraints.
+We add $(m-1)(d+1) + \uptheta' l(d+1) + (c+1)nl$ linear constraints, where the terms refer to the Voronoi hyperspace, obstacle hyperspace, and continuity constraints, respectively.
+For our example in Fig.~\ref{fig:swap2_2}, we have $n=2$, $m=2$, $d=7$, $l=4$, and $c=2$. Thus, we have 64 decision variables and $8 + 128 + 24 = 160$ linear constraints.
 
@@
 \subsection{Theoretical Guarantees} %maybe
-To provide formal guarantees, we make the following assumptions:
-First, the robots have first-order integrator dynamics (and thus $c=0$);
-second, the execution of the robots in synchronous;
-third, robots execute trajectories perfectly;
-fourth, robot trajectories are initially valid up to time $\tau$; and
-fifth, obstacles are static.
 
-For robot-robot collision avoidance our approach uses buffered voronois cells and retains the same theoretical guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
-\begin{lemma}
-If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
-\end{lemma}
+For robot-robot collision avoidance our approach uses buffered Voronois cells and retains the same theoretical guarantee, that we first restate here:
+If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision-free.
 
-For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, and then that the resulting QP is feasible.
+However, this has only been proven in the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
+We cannot provide formal guarantees under arbitrary disturbances.
+However, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
 
-\begin{lemma}
-\label{lemma:hyperplanes}
-In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle.
-\end{lemma}
-\begin{proof}
-We consider two cases.
-In the first case, discrete planning was successfully executed in iteration $K$.
-Therefore, the discrete planner has found a collision free discrete path that separates the robot from all other obstacles and robots. 
-Because the initially guessed control points are set on top of this path, the corresponding hyperplanes $M_j^b$ must exist.
+Similar to other work, there are no formal liveness guarantees and there might be deadlocks~\cite{bufferedVoronoiCells}.
+Nevertheless, our approach works in practice for robots with higher-order dynamics, if robot execution is asynchronous, or trajectories are not executed perfectly.
 
-In the second case, discrete planning was not executed (or failed to produce a path).
-In that case, we use the computed control points from the previous iteration $K-1$.
-By our assumption, the initial trajectories are valid up to time $\tau$.
-Thus, by induction, the previous iteration had a valid trajectory. This trajectory is still valid, since the obstacles cannot move and therefore new hyperplanes $M_j^b$ must exist.\qed
-\end{proof}
+%%%%%%%%%%
 
-\begin{lemma}
-In each iteration $K$, the constructed QP is feasible.
-\end{lemma}
-\begin{proof}
-We consider each of the three types of constraints that could render the QP infeasible.
-Hyperspace constraints can be fulfilled, because all hyperplanes exist according to Lemma~\ref{lemma:hyperplanes}.
-Initial point constraints are limited to one constraint by our assumption that $c=0$.
-Since the previous iteration $K-1$ produced a valid trajectory and the robot executed the trajectory perfectly, the initial point must be feasible.
-We have $l-1$ continuity constraints that constrain the position of the last control point of curve $j$ to be identical to the first control point of curve $j+1$.
-Those control points are already equal to each other for the initially guessed control points, no matter if discrete planning was executed or not.
-%In case discrete planning was successfully executed, the last and first control points share a corner of the discrete path.
-%In case discrete planning was not executed, the initially guessed control points are based on the result of the previous iteration $K-1$.
-Because those points do not violate any of the other constraints, the continuity constraints must be feasible.\qed
-\end{proof}
+% To provide formal guarantees, we make the following assumptions:
+% First, the robots have first-order integrator dynamics (and thus $c=0$);
+% second, the execution of the robots in synchronous;
+% third, robots execute trajectories perfectly;
+% fourth, robot trajectories are initially valid up to time $\tau$; and
+% fifth, obstacles are static.
 
-All lemmas together show that our approach is collision free under the stated assumptions.
-Similar to other work, there are no formal liveness guarantees and there might be deadlocks~\cite{bufferedVoronoiCells}.
-Our approach also works in practice for robots with higher-order dynamics, if robot execution is asynchronous, or trajectories are not executed perfectly, although there is no formal guarantee.
-%This can be achieved by choosing larger safety radii~\cite{bufferedVoronoiCells}.
+% For robot-robot collision avoidance our approach uses buffered Voronois cells and retains the same theoretical guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
+% \begin{lemma}
+% If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
+% \end{lemma}
 
-%%%%
+% For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, and then that the resulting QP is feasible.
 
-% Our approach uses buffered voronoi cells and retains the same theoretical robot-robot collision guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
-% If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
+% \begin{lemma}
+% \label{lemma:hyperplanes}
+% In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle.
+% \end{lemma}
+% \begin{proof}
+% We consider two cases.
+% In the first case, discrete planning was successfully executed in iteration $K$.
+% Therefore, the discrete planner has found a collision free discrete path that separates the robot from all other obstacles and robots. 
+% Because the initially guessed control points are set on top of this path, the corresponding hyperplanes $M_j^b$ must exist.
 
-% We note that this only holds under two assumptions:
-% first, the robots have first-order integrator dynamics, and second, the execution of the robot is synchronous.
-% The first problem can be mitigated in practice by choosing larger safety radii~\cite{bufferedVoronoiCells}.
-% We propose to address the second problem by shifting the voronoi hyperplanes by $\delta t \gamma_1$ to account for the worst-case phase shift in the robots' execution cycle.
+% In the second case, discrete planning was not executed (or failed to produce a path).
+% In that case, we use the computed control points from the previous iteration $K-1$.
+% By our assumption, the initial trajectories are valid up to time $\tau$.
+% Thus, by induction, the previous iteration had a valid trajectory. This trajectory is still valid, since the obstacles cannot move and therefore new hyperplanes $M_j^b$ must exist.\qed
+% \end{proof}
 
-% For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, assuming perfect trajectory execution:
+% \begin{lemma}
+% In each iteration $K$, the constructed QP is feasible.
+% \end{lemma}
+% \begin{proof}
+% We consider each of the three types of constraints that could render the QP infeasible.
+% Hyperspace constraints can be fulfilled, because all hyperplanes exist according to Lemma~\ref{lemma:hyperplanes}.
+% Initial point constraints are limited to one constraint by our assumption that $c=0$.
+% Since the previous iteration $K-1$ produced a valid trajectory and the robot executed the trajectory perfectly, the initial point must be feasible.
+% We have $l-1$ continuity constraints that constrain the position of the last control point of curve $j$ to be identical to the first control point of curve $j+1$.
+% Those control points are already equal to each other for the initially guessed control points, no matter if discrete planning was executed or not.
+% %In case discrete planning was successfully executed, the last and first control points share a corner of the discrete path.
+% %In case discrete planning was not executed, the initially guessed control points are based on the result of the previous iteration $K-1$.
+% Because those points do not violate any of the other constraints, the continuity constraints must be feasible.\qed
+% \end{proof}
 
-% \todo{need to remove third condition in discrete planning?}
-% % assume c=0 for proof
+% All lemmas together show that our approach is collision free under the stated assumptions.
+% Similar to other work, there are no formal liveness guarantees and there might be deadlocks~\cite{bufferedVoronoiCells}.
+% Our approach also works in practice for robots with higher-order dynamics, if robot execution is asynchronous, or trajectories are not executed perfectly, although there are no formal guarantees.
+% %This can be achieved by choosing larger safety radii~\cite{bufferedVoronoiCells}.
 
-% \begin{enumerate}
-%     \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
+% %%%%
+
+% % Our approach uses buffered voronoi cells and retains the same theoretical robot-robot collision guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
+% % If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
+
+% % We note that this only holds under two assumptions:
+% % first, the robots have first-order integrator dynamics, and second, the execution of the robot is synchronous.
+% % The first problem can be mitigated in practice by choosing larger safety radii~\cite{bufferedVoronoiCells}.
+% % We propose to address the second problem by shifting the voronoi hyperplanes by $\delta t \gamma_1$ to account for the worst-case phase shift in the robots' execution cycle.
+
+% % For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, assuming perfect trajectory execution:
+
+% % \todo{need to remove third condition in discrete planning?}
+% % % assume c=0 for proof
+
+% % \begin{enumerate}
+% %     \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
 The maximum phase shift between robots is $\delta t$.
@@
 This update gives \emph{no robot collision guarantee} even there is phase shift during the execution.
-%     \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
-%     \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
+% %     \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
+% %     \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
 If we know the maximum velocity $\nu$ of the obstacles in the environment, we can avoid moving obstacles as well by shifting the SVM seperating hyperplanes by $\nu \delta t $.
 This update gives \emph{no obstacle collision guarantee} even the obstacles are moving.
-% \end{enumerate}
-% see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
-% might be able to account for possible faceshift
+% % \end{enumerate}
+% % see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
+% % might be able to account for possible faceshift
 
@@
 \subsection{Simulation}
-We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) running Ubuntu 16.04.
+We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) with Ubuntu 16.04 operating system.
 
@@
 % (one example (16 case or generate larger w/ 32))
-In a first experiment, we test the scalability of our method in terms of the number of curves $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
+In the first experiment, we test the scalability of our method in terms of the number of curves $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
 Our results are summarized in Tables~\ref{tab:curveCountScalability}, \ref{tab:obstacleCountScalability} and \ref{tab:robotCountScalability}, where $t_{avg}$ is the average time that qpOASES takes per iteration.
@@
          \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
-         1 & $1$ & $0$ & $4$ &$10$\\ \hline
+         %1 & $1$ & $0$ & $4$ &$10$\\ \hline
          2 & $4$ & $0$ & $4$ & $10$\\ \hline
@@
          \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
-         7 & $4$ & $2$ & $4$ &$9$\\ \hline
+         %7 & $4$ & $2$ & $4$ &$9$\\ \hline
          8 & $4$ & $4$ & $4$ & $9$ \\ \hline
@@
          \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
-         13 & $4$ & $5$ & $2$ &$10$\\ \hline
+         %13 & $4$ & $5$ & $2$ &$10$\\ \hline
          14 & $4$ & $5$ & $4$ &$9$\\ \hline
@@
 
-We also compare our method (RME) to two different ORCA variants.
-We use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i(\psi)'$ if $\vp(\psi)\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp(\psi)}{\delta t}$ otherwise.
+We also compare our method (RME) to two ORCA variants.
+We use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp(\psi)\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp(\psi)}{\delta t}$ otherwise.
 In order to improve the behavior with obstacles, we combine ORCA in a different set of experiments with our discrete planning method (denoted as ORCA*).
@@
 For RME we use $\delta t = \SI{0.1}{s}$ and for the ORCA variants $\delta t = \SI{0.01}{s}$.
-All algorithms are given more time (less than $20$ seconds in each case) than the original plans to complete because of the introduction of new obstacles to the environment.
+All algorithms are given more time (no more than $20$ seconds in each case) than the original plans to complete because of the introduction of new obstacles to the environment.
 The results are summarized in Table~\ref{tab:rvo2Comparison}.
@@
 Also, robots using ORCA are in invalid configurations (collisions) as much as 49\% of the time, while robots using RME are almost never in invalid configurations.
-Invalid configurations in RME can occur because of numerical problems.
+Invalid configurations in RME occur because of numerical problems particularly in seperating hyperplane calculations between robots and obstacles.
 We also note that ORCA does not provide the same smoothness guarantees ($c=0$, i.e., velocities can jump between iterations) and that it requires to sense the other robot's velocities instead of positions only.
@@
 \begin{table}
-%1 -> swap4, obsdiamond, +2 seconds
-%2 -> swapCircle6, swapCircle6, +3 seconds
-%3 -> swapCircle8, 3obstacles, +2 seconds (31 seconds original)
-%4 -> swapCircle16, obsdiamond, +12 seconds (22 seconds original)
-%5 -> swapCircle16, 3obstacles, +19 seconds (22 seconds original)
     \centering
@@
       $1$ & $4$ & $2$ & $<1$ & $62$ & $2$ & $<1$ & $99$ & $3$ & $9$ & $100$ & $4$\\ \hline
-      $2$ & $6$ & $5$ & $<1$ & $63$ & $4$ & $<1$ & $72$ & $3$ & $11$ & $98$ & $6$\\ \hline
-      $3$ & $8$ & $5$ & $<1$ & $60$ & $5$ & $<1$ & $69$ & $8$ & $10$ & $99$ & $8$\\ \hline
-      $4$ & $16$ & $2$ & $<1$ & $58$ & $14$ & $<1$ & $58$ & $13$ & $11$ & $100$ & $16$\\ \hline
+      $2$ & $6$ & $5$ & $<1$ & $66$ & $5$ & $<1$ & $63$ & $5$ & $10$ & $100$ & $6$\\ \hline
+      $3$ & $8$ & $5$ & $<1$ & $59$ & $5$ & $<1$ & $71$ & $8$ & $10$ & $98$ & $8$\\ \hline
+      $4$ & $16$ & $2$ & $<1$ & $57$ & $14$ & $<1$ & $57$ & $13$ & $11$ & $100$ & $16$\\ \hline
       $5$ & $16$ & $5$ & $<1$ & $51$ & $13$ & $<1$ & $57$ & $11$ & $14$ & $98$ & $16$\\ \hline
@@
     \end{tabular}
-    \caption{Comparison of RME with ORCA and ORCA* with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destination eventually ($s$).
+    \caption{Comparison of RME with ORCA and ORCA* with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destinations eventually ($s$).
     %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
@@
 Each robot receives the position information of all other robots using a motion capture system.
-Trajectory tracking controller and our algorithm run on-board at a frequency of \SI{10}{Hz}.
+A trajectory tracking controller and our algorithm run on-board at a frequency of \SI{10}{Hz}.
 
@@
 
-Our method is closely related to cooperative collision avoidance.
-Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
-They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
-A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
-Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered voronoi cells, and safety barrier certificates.
+% Our method is closely related to cooperative collision avoidance.
+% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
+% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
+% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
+% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
+Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
 Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
-Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
+%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
+Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
 Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
 Safety barrier certificates achieves collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
-All approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
-Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}).
+%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
+Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.
 
-Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
-Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
-The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
-The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search.
+%Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
+%Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
+%The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
+%The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search.
 Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
-Our robust motion execution uses the same optimization framework to generate trajectories, although with a different cost function.
-We also use discrete search to quickly get out of local minima, but, unlike previous work, do so in a distributed manner.
+Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
+Similar to previous work we use discrete search to quickly get out of local minima, but do so in a distributed manner.
 
 While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
-Using a discrete plan (generated by RRT*), polynomial trajectories can be generated using a quadratic program~\cite{richterISRR}.
-In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
-Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
+%Using a discrete plan (generated by RRT*), polynomial trajectories can be generated using a quadratic program~\cite{richterISRR}.
+%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
+%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
 Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
 In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
-In contrast, our formulation uses a hard constraint and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
+In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
+%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
 The optimization can use a discrete plan as initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.

### 2018-05-18 rvo2_main.cpp
rvo2: ensure that obstacles are added in ccw vertex order

@@ -155,8 +155,9 @@ int main(int argc, char** argv) {
         pt[0] = coord.first - cell_size / 2.0;
         pt[1] = coord.second + cell_size / 2.0;
         o.add_pt(pt);
-        o.convex_hull();
-        o.ch_planes(/*shift*/0);
+        // This function sorts the points internally => do not call!
+        // o.convex_hull();
+        // o.ch_planes(/*shift*/0);
         cell_based_obstacles.push_back(o);
       }
     }

### 2018-05-19 discrete_search.hpp
Friday

@@ -68,7 +68,7 @@ public:
   {
 
     if (!stateValid(goal)) {
-      std::cerr << "GOAL not valid!" << std::endl;
+      std::cerr << "GOAL not valid! goal: " << goal.x << " " << goal.y  << std::endl;
     }
   }
 

### 2018-05-19 main.cpp

@@ -484,9 +484,18 @@ int main(int argc, char** argv) {
                 occupiedByOtherRobot = true;
                 break;
               }
+
+              if (   fabs(coord.first - otherRobot.first) <= 2 * robot_radius
+                  && fabs(coord.second - otherRobot.second) <= 2 * robot_radius) {
+                occupiedByOtherRobot = true;
+                break;
+              }
             }
 
-            if (!occupiedByOtherRobot) {
+            bool occupiedByObstacle = og.occupied(goalPos[0], goalPos[1], robot_radius);
+
+
+            if (!occupiedByObstacle && !occupiedByOtherRobot) {
               goal.x = goalIdx.i;
               goal.y = goalIdx.j;
               discrete_horizon = t - ct;

### 2018-05-19 rvo2_main.cpp

@@ -54,6 +54,7 @@ int main(int argc, char** argv) {
   nlohmann::json jsn = nlohmann::json::parse(cfg);
 
   string initial_trajectories_path = jsn["trajectories"];
+  float scale_traj = jsn["scale_traj"];
   string obstacles_path = jsn["obstacles"];
   double dt = jsn["replan_period"];
   dt/=10;
@@ -87,7 +88,7 @@ int main(int argc, char** argv) {
     trajectory trj;
     for(int i=0; i<file.rowCount(); i++) {
       double duration = stod(file[i][0]);
-      curve crv(duration, problem_dimension);
+      curve crv(duration*scale_traj, problem_dimension);
       for(int j=1; j<=problem_dimension * ppc; j+=problem_dimension) {
         vectoreuc cp(problem_dimension);
         for(int u=0; u<problem_dimension; u++) {
@@ -141,7 +142,7 @@ int main(int argc, char** argv) {
         output_json["occupied_cells"]["x"].push_back(coord.first);
         output_json["occupied_cells"]["y"].push_back(coord.second);
 
-        obstacle2D o;
+        obstacle2D o, o2;
         vectoreuc pt(problem_dimension);
         pt[0] = coord.first - cell_size / 2.0;
         pt[1] = coord.second - cell_size / 2.0;
@@ -156,8 +157,8 @@ int main(int argc, char** argv) {
         pt[1] = coord.second + cell_size / 2.0;
         o.add_pt(pt);
         // This function sorts the points internally => do not call!
-        // o.convex_hull();
-        // o.ch_planes(/*shift*/0);
+        o.convex_hull();
+        o.ch_planes(/*shift*/0);
         cell_based_obstacles.push_back(o);
       }
     }
@@ -221,8 +222,9 @@ int main(int argc, char** argv) {
   // Add (polygonal) obstacle(s), specifying vertices in counterclockwise order.
   for (auto& obs : cell_based_obstacles) {
     std::vector<RVO::Vector2> vertices;
-    for (auto& pt : obs.pts) {
-      vertices.push_back(RVO::Vector2(pt[0], pt[1]));
+    for(int i=obs.ch.size()-2; i>=0 ; i--) {
+      int pt = obs.ch[i];
+      vertices.push_back(RVO::Vector2(obs.pts[pt][0], obs.pts[pt][1]));
     }
     sim.addObstacle(vertices);
   }
@@ -275,16 +277,25 @@ int main(int argc, char** argv) {
 
[…]

### 2018-05-19 vis/vis.py

@@ -10,6 +10,8 @@ from matplotlib.patches import Rectangle
 import numpy as np
 
 
+step = False
+
 def frameGen():
   global frameId
   global numFrames
@@ -141,6 +143,8 @@ def animate(frame):
     global step
     global x
     global y
+    global anim_running
+    global anim
 
     for i in robots:
         x[i].append(jsn["points"][frame][i][0])

### 2018-05-23 paper/paper.tex

@@
 
-\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,
-                shadows, shapes.geometric, shapes.misc}
+\usepackage{xcolor}
+\newcommand{\Nora}[1] {\textbf{\textcolor{red}{#1}}}
+
+\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,shadows, shapes.geometric, shapes.misc}
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\cO}{\mathcal{O}}
+\newcommand{\cH}{\mathcal{H}}
 
@@
 \newcommand{\R}{\mathbb{R}} % real numbers
+\renewcommand{\th}{^{\text{th}}}
 
@@
 \begin{abstract}
-We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
+We propose a method for robust motion execution that can be applied to a wide range  of  trajectory execution tasks. 
+It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
 Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
@@
 \section{Introduction}
-Motion planning for multi-robot systems is widely used and in particular important in cases where many robots have to interact with each other in confined spaces, potentially with many obstacles around.
+Motion planning for multi-robot systems is widely used and in particular important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles around.
 Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
 Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
-All such solutions assume that the resulting trajectories can be executed approximately perfectly, which is not true for teams of hundreds of robots that have to operate persistently.
+However, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.
 
-We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, robots breaking down, or external disturbances.
-Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their positions.
-The pre-planned trajectories are collision-free, but neither considers the new obstacle nor that the fact that blue robot does not start at its correct location.
-Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories.
-Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and the obstacles around them.
+We propose a method for robust motion execution that can be applied to wide range of trajectory execution tasks.
+It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or other external disturbances.
+Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
+Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
+Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
+Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense their neighbors' positions and the obstacles around them.
 
@@
 \caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
-The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
-Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the pre-planned trajectory (b).
+The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
+Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory (b).
 }
@@
 
-Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
-In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
-Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
-At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with a dynamic receding horizon approach.
-The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.
+Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
+In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
+Our method relies on the \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
+We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
+The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.
+
+We show in simulations that our method avoids collisions and deadlocks more successfully compared to ORCA~\cite{orca}.
+Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.
 
 %\todo{perhaps write some more about what experiments we did, after we have the material}
+
+% \begin{tabular}{l||l}
+% \hline % global
+% $m$ & number of robots\\
+% $n$ & problem dimension\\
+% $c$ & order of derivative up to which smoothness is required \\
+% $\gamma_k$ & dynamic limit of each robot for the $k\th$ derivative of its trajectory\\
+% %$\Gamma_k$ & \\
+% %$r_s$ & radius\\
+% $R(\vp), r_s$ & space that robot occupies at position $\vp$ (sphere with radius $r_s$)\\
+% $\psi$ & current time\\
+% $\uptheta, \uptheta'$ & number of static obstacles\\
+% \hline % per robot
+% $\vo_i(t), t\in[0, T_i]$     &  original trajectory of robot $i$\\
+% $\vp_i(t)$ & position of robot $i$ at time $t$\\
+% $\cO_i$ & obstacles\\
+% %$\vf_i(t)$ & \\
+% $\cV_i$ & voronoi cell\\
+% $\cS_i^j$ & \\
+% $\cH_i^j, \valpha_i^j, \beta_i^j$ & hyperplane robot-robot\\
+% $M_j^b$ & hyperplane robot-obstacle\\
+% %$H$, $A$, $lbA$, $ubA$, $g$ & QP\\
+% $K$ & iteration\\
+% \hline % algorithm
+% $l$ & pieces\\
+% $d$ & degree\\
+% $\lambda_i, \theta_j$ & QP\\
+% $\tau, \tau'$ & \\
+% $\delta t$ & \\
+% $\vf^{K}_i(t)$ & duration $T^{K}_i$ \\
+% $\vf^{K}_{i,j}(t), t\in[0, T^{K}_{i,j}]$ & $j\th$ piece\\
+% $\vP^{K}_{i,j,\rho}$ & denotes the $\rho\th$ control point\\
+% \end{tabular}
 
@@
 % issues: no live-lock guarantee
-
-We consider a group of $m$ robots and each robot $i$ is given the following:
+The general problem we would like to solve can be formulated as follows. 
+Consider a group of $m$ robots. Each robot $i$ is given the following:
 \begin{align*}
-    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
+    \vo_i(t)&:\text{ original trajectory of $i\th$ robot where time } t\in[0,T_i],\\
     %ct&:\text{ current global time},\\
@@
     %\tau&: \text{time horizon},\\ 
-    c&:\text{ derivative up to which smoothness is required},\\
+    c&:\text{ order of derivative up to which smoothness is required},\\
     %\cO&:\text{ free space representation of the environment},\\
     %\{\vp_i\}&:\text{ set of positions of all robots},\\
-    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
-    \gamma_j&: \text{ dynamic limit of the robot for $j^{th}$ derivation degree}.%\\
-    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
+    R(\vp)&:\text{ collision model of a robot at position $\vp$ (sphere with radius $r_s$), and}\\
+    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
+    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
 \end{align*}
 
-At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
-We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
-Robots cannot communicate with each other and are unaware of the other robots' trajectories.
+Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of its neighbors as well as the current occupied space $\cO_i$ around it.
+We represent $\cO_i$ as a set of $\uptheta$ convex obstacles; our approach can accommodate for different sensing modalities, including LIDAR and RGB-D cameras.
+%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
+Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
 %Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
-Each robot $i$ needs to execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
+Each robot $i$ must execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
 \begin{align}
@@
     &\vf_i(t)\text{ is collision free, and}\\ 
-    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j\text{ for all desired $j$s},\\
+    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
     \text{where } & t\in [0,T_i].
@@
 
-We approximately solve this problem iteratively using a dynamic receding horizon approach.
+We solve this problem approximately, using a dynamic receding horizon approach iteratively.
 At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
@@
 %     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
-%     &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
+%     &\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
 %     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
@@
 
-We now introduce important mathematical concepts and notations we use.
+This section introduces important mathematical concepts and notation that will be used throughout the paper.
 
-\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
-Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
+\subsection{Buffered Voronoi Cell} \label{bufferedVoronoi}
+Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_s \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
 \begin{align}
-    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
+    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_s\leq 0 \right\}, \label{voronoi_cell_definition}
 \end{align}
-where $\|\vp\|$ is the L2-norm of vector $\vp$.
+where $\|\vp\|$ is the L2-norm of the vector $\vp$.
 
-The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
+The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ bounded by hyperplane $\cH_i^j$ that separates point $\vp_i$ from $\vp_j$.
+$\cH_i^j$ has normal $\valpha_i^j \in \R^n$ and distance $\beta_i^j\in \R$ along $\valpha_i^j$ such that
 \begin{equation}
     \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
-    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
+    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s.
     \label{voronoiAlphaBeta}
@@
 %     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
-%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
+%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s. \label{voronoiBeta}
 % \end{align}
@@
 % The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
-For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside at most one of the buffered Voronoi cells.
+For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside of at most one of the buffered Voronoi cells.
 We use this property in order to avoid robot-to-robot collisions.
@@
 
-Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.
+Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.
 
-\subsection{B\'ezier Curves} \label{bezierCurves}
-A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
+\subsection{B\'ezier Curve} \label{bezierCurves}
+A degree $d$ B\'ezier curve $\vf(t)$ implicitly parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
 \begin{align}
-    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
+    \vf(t) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
 \end{align}
@@
 The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
-A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
+A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein};
 %This is called the \emph{convex hull property of B\'ezier curves}.
-We use this property to avoid robot-to-obstacle collisions.
+we leverage this property to avoid robot-to-obstacle collisions.
 
 We use splines as trajectories where each piece is a B\'ezier curve.
-Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece where $j \in \{1,2,\ldots,l\}$.
-$\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$.
-$\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $\rho \in \{0,1,\ldots,d\}$.
+Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j\th$ piece where $j \in \{1,2,\ldots,l\}$.
+$\vf^{K}_{i,j}(t)$ denotes the $j\th$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$.
+$\vP^{K}_{i,j,\rho}$ denotes the $\rho\th$ control point of the $j\th$ piece where $\rho \in \{0,1,\ldots,d\}$.
 
@@
 \subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
-A part of our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
-The decision variables $\vx$ are all B\'ezier curve control points concatenated.
+Our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
+The decision variables $\vx$ are the concatenated B\'ezier curve control points.
 The overall structure of our quadratic optimization problem is as follows:
@@
 If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points.
-All 3 types of constraints are linear in control points, and the exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.
+All 3 types of constraints are linear in control points.
+The construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.
 
@@
 %\subsection{Approach Overview}
-Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
+Replanning is done at a fixed period of $\delta t$.
+In each iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $f^K_i(t)$.
 The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
-In the following, we assume that the robots are spherical with a uniform radius $r_s$.
+
+% In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i$.
+% We also assume that we have a current representation of the occupied space ($\cO_i$).
+Even if we use the complete occupation map in our examples, our method also works for local maps which can be constructed in practice by using LIDAR or RGB-D sensors.
+
 %The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.
 
-We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
+We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot (see Fig.~\ref{fig:flowchart}).
+
 %In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
@@
 
-%At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
+At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c\th$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
 We execute this trajectory for a period of $\delta t$ and replan for the next iteration.
@@
 
-In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i(\psi)$.
-We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.
-
 Robot $i$ executes discrete planning if any of the following conditions are true:
 \begin{enumerate}
-    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
-    \item The first piece of the previously planned trajectory is outside the robot's buffered Voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
-    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
+    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R(\vo_i(t)) \cap \cO_i \neq \emptyset$,
+    \item The first piece of the previously planned trajectory is outside the robot's buffered Voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i$, or
+    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R(\vf^{K-1}_i(t)) \cap \cO_i \neq \emptyset$.
 \end{enumerate}
-The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear and robots move towards each other a lot, and the third condition handles numeric issues and dynamic obstacles.
+The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second condition handles cases where previously unknown robots appear and cases where robots are close and moving towards each other, and the third condition handles dynamic obstacles and numerical issues that resulted in a trajectory with collisions in the previous iteration.
+The main reason of these numerical issues is explained in Section~\ref{simulationSection}.
 
@@
 First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free at time $\psi + \tau'$ with respect to both obstacles and other robots.
-Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
-If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage and construct QP as if discrete planning was not required.
+Second, we use a discrete graph search to find a path from the robot's current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
+If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage and construct the QP as if discrete planning was not required.
 Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
@@
 
-An example is shown in Fig.~\ref{fig:swap2_2} (a). 
+An example is shown in Fig.~\ref{fig:swap2_2} (a), with parameters $l=4$ and $d=7$.
 Discrete planning is executed because the original trajectory (green dashed line) passes through an obstacle.
-The earliest time to avoid the obstacle $\tau'$ is found such that the green robot re-joins its original trajectory after the obstacle.
-A path that avoids both the static obstacle and the other (blue) robot is found (green dotted line) and has a total of six path segments.
-The first four ($l=4$) segments are used to place new guesses of B\'ezier control points (blue, green, red, and cyan circles).
-In this example, each curve has eight control points, although some of the points overlap.
-The duration for each B\'ezier curve $T^{K}_{i,j}$ is adjusted according to the path length; for example, the duration of the segment with the red control points ($T_{i,3}^K$) is approximately twice as long as the duration of the segment with the green control points ($T_{i,2}^K$).
+We find the earliest time $\tau'$ such that $R(\vo_g(\psi+\tau'))$ does not intersect with the obstacle and the blue robot where $g$ is the green robot.
+% such that the green robot re-joins its original trajectory after the obstacle.
+The discrete planner is then used to find a path  (green dotted line) that avoids both the static obstacle and the other (blue) robot, with a total of six path segments.
+The first four segments ($l=4$) are used to place new guesses of B\'ezier control points (blue, green, red, and cyan circles).
+Notice that since $d=7$, each curve has eight control points, while some of the points are overlapping.
+The duration $T^{K}_{i,j}$ for each B\'ezier curve is adjusted linearly according to its segment length; for example, the duration of the segment with the red control points ($T_{i,3}^K$) is approximately twice as long as the duration of the segment with the green control points ($T_{i,2}^K$).
 
@@
 \subsection{Continuous Optimization}\label{continuousOptimization}
-We compute a new trajectory by formulating a quadratic optimization problem where the decision variables are the control points of the pieces concatenated together.
+We compute a new trajectory by formulating a quadratic optimization problem where the decision variables are the concatenated control points of the pieces.
+The parameters $d$ and $l$ of the pieces (see Section~\ref{bezierCurves}) are provided by the user.
 If discrete planning is not performed, initial guesses of the decision variables are copied from the previous iteration, and the durations $T^{K}_{i,j}$ are set uniformly to $\frac{\min(\tau,T_i-\psi)}{l}$.
@@
 \begin{align}
-    \sum_{e=1}^{\cE} \lambda_e\int_{0}^{T^K_i} \left\|\frac{d^e\vf^{K}_i(t)}{dt^e}\right\|^2dt + \sum_{j=1}^{l} \theta_j \left\|\vP^{K}_{i,j,d} - \vchi_{j}\right\|^2 \label{costFunction}
+    \sum_{e=1}^{\cE} \lambda_e\int_{0}^{T^K_i} \left\|\frac{d^e\vf^{K}_i(t)}{dt^e}\right\|^2dt + \sum_{j=1}^{l} \theta_j \left\|\vP^{K}_{i,j,d} - \vchi_{j}\right\|^2, \label{costFunction}
 \end{align}
-where $\vchi_j$ is the point we want piece $j$ to end at.
+where $\vchi_j$ is the point  where we want piece $j$ to end.
 %Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
-
-The first term of the objective is the combination of integrated squared derivatives up to degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro}.
-It minimizes the energy through curve.
+The first term of the objective minimizes the energy along the trajectory, and is the combination of integrated squared derivatives up to degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro}.
 %richterISRR
-The second term of the objective penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
-In case discrete planning is performed, we attempt to get to the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value, enforcing $\vP^K_{i,l,d} = \vchi_l$, and $\theta_j = 0, \forall j < l$.
+The second term of the objective penalizes deviation from the given end points for each piece of the trajectory with different weights $\theta_j$.
+In case discrete planning is performed, we attempt to get to the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value, enforcing $\vP^K_{i,l,d} = \vchi_l$, and $\theta_j = 0,\,\forall j < l$.
 If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
@@
 %This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
-Matrix $H$ (see Section~\ref{trajectoryOptimization}) can be constructed for the first term of our objective~\cite{crazyplanning-ieeetro}.
+The matrix $H$ (see Section~\ref{trajectoryOptimization}) for the first term of our objective can be constructed as in our previous work~\cite{crazyplanning-ieeetro}.
 %The construction of matrix $H$, as defined in Section~\ref{trajectoryOptimization}, for the first term of our objective function is explained in \cite{crazyplanning-ieeetro}.
@@
 
-For robot-to-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
+For robot-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
 % . For each control point of the first piece, we add $m-1$ hyperspace constraints as
@@
 These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
-As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
+As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-robot collision will occur up to time $\delta t$.
 
-For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO(\psi)$ for each curve piece $j$.
-Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$.
-That can, for example, be computed using support vector machines~\cite{SVM}.
+For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO_i$ for each curve piece $j$.
+Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j\th$ piece from the $b\th$ obstacle obtained from $\cO_i$ (these can be computed, e.g., using support vector machines~\cite{SVM}).
 We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
-We add hyperspace constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each hyperplane $M_j^b$
-These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau'$.
+We add hyperspace constraints as before, requiring control points of the $j\th$ piece in the non-occupied side of each hyperplane $M_j^b$.
+These constraints ensure that no robot-obstacle constraint will occur up to time $\tau'$.
 In case discrete planning was executed, we additionally treat other robots as static obstacles.
-Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for our example.
+Fig.~\ref{fig:swap2_2}(b) shows the effective set of hyperspaces for our example.
 
-Moreover, we add continuity constraints that enforce continuity requirement between pieces.
-Then, we add initial point constraints that enforce continuity requirements in the beginning that ensures continuity between iterations.
+Moreover, we add continuity constraints that enforce the continuity requirement between pieces and initial point constraints that enforce continuity requirements between iterations.
 
-All constraints are linear and matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
+All constraints are linear and matrix $A$ and its bounds can be constructed as in Section~\ref{trajectoryOptimization}.
 The number of decision variables in our QP is $l(d+1)n$.
@@
 Since we use fixed durations of the pieces and do not account for the dynamic limits of the robot during optimization, the resulting trajectory may violate the dynamic limits of the robot.
-After trajectory optimization, we calculate the maximum magnitudes $\Gamma_j$ of $j^{th}$ derivatives of the curve, and check if there exists a $j$ such that $\Gamma_j > \gamma_j$, where $\gamma_j$ is the dynamic limit of the robot in $j^{th}$ derivation degree.
+After trajectory optimization, we calculate the maximum magnitudes $\Gamma_k$ of the $k\th$ derivatives of the curve, and check if there exists a $k$ such that $\Gamma_k > \gamma_k$, where $\gamma_k$ is the dynamic limit of the robot in the $k\th$ derivation degree.
 If that is the case, we uniformly scale the piece durations $T^K_{i,j}$, and re-run the trajectory optimization with the same exact constraints using the previous result as the initial guess.
@@
 
-For robot-robot collision avoidance our approach uses buffered Voronois cells and retains the same theoretical guarantee, that we first restate here:
-If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision-free.
+For robot-robot collision avoidance our approach uses buffered Voronoi cells and retains the same theoretical guarantee, that we restate here:
+if robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision free.
 
-However, this has only been proven in the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
+However, this guarantee has only been proven for the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
 We cannot provide formal guarantees under arbitrary disturbances.
@@
 % \label{lemma:hyperplanes}
-% In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle.
+% In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j\th$ piece from the $b\th$ obstacle.
 % \end{lemma}
@@
 
-\section{Evaluation}
+\section{Evaluation} \label{evaluationSection}
 
@@
 We use an occupancy grid as environment representation, because previous work has shown that such data structures can be updated in real-time on robots that are equipped with a LIDAR sensor or a RGB-D camera.
-In particular, OctoMap~\cite{octomap} is an octree-based 3D occupancy grid that can be run on UAVs at at least \SI{4}{Hz} update rate~\cite{replanning-eth}.
+In particular, OctoMap~\cite{octomap} is an octree-based 3D occupancy grid that can be run on UAVs with at least \SI{4}{Hz} update rate~\cite{replanning-eth}.
 OctoMaps are memory efficient, but update operations can show high execution time variance.
@@
 
-\subsection{Simulation}
-We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) with Ubuntu 16.04 operating system.
+\subsection{Simulation}\label{simulationSection}
+We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) with Ubuntu 16.04 as operating system.
 
@@
 When we use OSQP instead of qpOASES, our implementation takes significantly more time if we consider many obstacles.
-For example, when we do experiment $9$ using OSQP, it takes \SI{297}{ms} on average.
+For example, when we do experiment $7$ using OSQP, it takes \SI{297}{ms} on average.
 
@@
          %1 & $1$ & $0$ & $4$ &$10$\\ \hline
-         2 & $4$ & $0$ & $4$ & $10$\\ \hline
-         3 & $8$ & $0$ & $4$ & $15$\\ \hline
-         4 & $10$ & $0$ & $4$ & $13$ \\ \hline
-         5 & $12$ & $0$ & $4$ & $27$ \\ \hline
-         6 & $16$ & $0$ & $4$ & $107$ \\ \hline
+         1 & $4$ & $0$ & $4$ & $10$\\ \hline
+         2 & $8$ & $0$ & $4$ & $15$\\ \hline
+         3 & $10$ & $0$ & $4$ & $13$ \\ \hline
+         4 & $12$ & $0$ & $4$ & $27$ \\ \hline
+         5 & $16$ & $0$ & $4$ & $107$ \\ \hline
          \multicolumn{5}{c}{}\\
@@
          %7 & $4$ & $2$ & $4$ &$9$\\ \hline
-         8 & $4$ & $4$ & $4$ & $9$ \\ \hline
-         9 & $4$ & $62$ & $4$ & $28$ \\ \hline
-         10 & $4$ & $196$ & $4$ & $47$  \\ \hline
-         11 & $4$ & $213$ & $4$ & $69$  \\ \hline
-         12 & $4$ & $1250$ & $4$ & $253$  \\ \hline
+         6 & $4$ & $4$ & $4$ & $9$ \\ \hline
+         7 & $4$ & $62$ & $4$ & $28$ \\ \hline
+         8 & $4$ & $196$ & $4$ & $47$  \\ \hline
+         9 & $4$ & $213$ & $4$ & $69$  \\ \hline
+         10 & $4$ & $1250$ & $4$ & $253$  \\ \hline
          \multicolumn{5}{c}{}\\
@@
          %13 & $4$ & $5$ & $2$ &$10$\\ \hline
-         14 & $4$ & $5$ & $4$ &$9$\\ \hline
-         15 & $4$ & $5$ & $8$ & $10$ \\ \hline
-         16 & $4$ & $5$ & $16$ & $13$ \\ \hline
-         17 & $4$ & $5$ & $32$ & $15$  \\ \hline
-         18 & $4$ & $5$ & $64$ & $14$  \\ \hline
+         11 & $4$ & $5$ & $4$ &$9$\\ \hline
+         12 & $4$ & $5$ & $8$ & $10$ \\ \hline
+         13 & $4$ & $5$ & $16$ & $13$ \\ \hline
+         14 & $4$ & $5$ & $32$ & $15$  \\ \hline
+         15 & $4$ & $5$ & $64$ & $14$  \\ \hline
          \multicolumn{5}{c}{}\\
@@
 
+% experiments 17, 19 and physical
+\begin{figure}
+\centering
+%\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
+\includegraphics[width=0.18\textwidth]{images/ex_16.pdf}
+%\label{fig:swap2:discrete}
+%}
+\hfill
+%\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
+\includegraphics[width=0.4\textwidth]{images/ex_17.pdf}
+%\label{fig:swap2:cont}
+%}
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=1.0\textwidth]{images/swap2_discrete.pdf}
+% \caption{Discrete path around an obstacle and other robot back to the original trajectory.}
+% \label{fig:swap2:discrete}
+% \end{subfigure} \hfill
+% \begin{subfigure}[t]{0.48\textwidth}
+% \centering
+% \includegraphics[width=1.0\textwidth]{images/swap2_cont_red.pdf}
+% \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
+% \label{fig:swap2:cont}
+% \end{subfigure}
+\hfill
+\includegraphics[width=0.40\textwidth]{images/ex_18.pdf}
+\hfill
+\includegraphics[width=0.40\textwidth]{images/ex_19.pdf}
+\caption{
+TODO
+}
+\label{fig:swap2_2}
+\end{figure}
+
 We also compare our method (RME) to two ORCA variants.
 We use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp(\psi)\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp(\psi)}{\delta t}$ otherwise.
-In order to improve the behavior with obstacles, we combine ORCA in a different set of experiments with our discrete planning method (denoted as ORCA*).
-We use $l=4$ as the number of curves, and $d+1=8$ as the degree of B\'ezier curves.
+In order to improve the behavior with obstacles, we combine ORCA in a different set of experiments with our discrete planning method (denoted as DS+ORCA).
+We use $l=4$ as the number of curves, and $d=7$ as the degree of B\'ezier curves.
 For RME we use $\delta t = \SI{0.1}{s}$ and for the ORCA variants $\delta t = \SI{0.01}{s}$.
-All algorithms are given more time (no more than $20$ seconds in each case) than the original plans to complete because of the introduction of new obstacles to the environment.
+All algorithms are given more time than the original plans to complete because of the introduction of new obstacles to the environment.
 The results are summarized in Table~\ref{tab:rvo2Comparison}.
@@
 All robots using RME reach their destinations, while robots using ORCA can get stuck as seen in all examples.
-Also, robots using ORCA are in invalid configurations (collisions) as much as 49\% of the time, while robots using RME are almost never in invalid configurations.
+Also, robots using ORCA appear in invalid configurations (collisions) as much as 49\% of the time, while robots using RME are almost never in invalid configurations.
 Invalid configurations in RME occur because of numerical problems particularly in seperating hyperplane calculations between robots and obstacles.
@@
 A video showing some examples is available at \url{TODO}.
-
 \begin{table}
     \centering
-    \begin{tabular}{ |l|  c|  c | c | c | c| c| c| c| c| c| r| }
-      \cline{4-12}
-       \multicolumn{3}{c|}{} & \multicolumn{3}{c| }{ORCA} & \multicolumn{3}{c| }{ORCA*} & \multicolumn{3}{c|}{RME}\\ \hline
-      \# & $m$ &  $\uptheta$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ & $t_{avg}(ms)$ & $\text{v}_{min}(\%)$ & $s$ \\ \hline
-      $1$ & $4$ & $2$ & $<1$ & $62$ & $2$ & $<1$ & $99$ & $3$ & $9$ & $100$ & $4$\\ \hline
-      $2$ & $6$ & $5$ & $<1$ & $66$ & $5$ & $<1$ & $63$ & $5$ & $10$ & $100$ & $6$\\ \hline
-      $3$ & $8$ & $5$ & $<1$ & $59$ & $5$ & $<1$ & $71$ & $8$ & $10$ & $98$ & $8$\\ \hline
-      $4$ & $16$ & $2$ & $<1$ & $57$ & $14$ & $<1$ & $57$ & $13$ & $11$ & $100$ & $16$\\ \hline
-      $5$ & $16$ & $5$ & $<1$ & $51$ & $13$ & $<1$ & $57$ & $11$ & $14$ & $98$ & $16$\\ \hline
+    \begin{tabular}{ |l|  c|c|  p{30mm} | c | c | c| c| c| c| c| c| r| }
+      \cline{5-13}
+       \multicolumn{4}{c|}{} & \multicolumn{3}{c| }{ORCA} & \multicolumn{3}{c| }{DS+ORCA} & \multicolumn{3}{c|}{RME}\\ \hline
+      \# & $m$ &  $\uptheta$ & description&  $t_{avg}(ms)$ & ? & $s$ & $t_{avg}(ms)$ & ? & $s$ & $t_{avg}(ms)$ & ? & $s$ \\ \hline
+      $16$ & $2$ & $4$ & \noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$2$ robots tries to swap  positions with an obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $0$ & $<1$ & $ $ & $2$ & $8$ & $ $ & $2$\\ \hline
+      $17$ & $4$ & $12$ & \noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$4$ robots tries to swap positions with a u-shaped obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $0$ & $<1$ & $ $ & $4$ & $11$ & $ $ & $4$\\ \hline
+      $18$ & $16$ & $12$ &\noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$16$ robots tries to swap positions with a u-shaped obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $15$ & $<1$ & $ $ & $15$ & $14$ & $ $ & $16$\\ \hline
+      $19$ & $16$ & $9$ &\noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$16$ robots tries to swap positions with $3$ obstacles in the middle\vspace{.2\baselineskip}}& $<1$ & $ $ & $13$ & $<1$ & $ $ & $14$ & $16$ & $ $ & $16$\\ \hline
+      $20$ & $16$ & $5$ &desc& $<1$ & $ $ & $13$ & $<1$ & $ $ & $12$ & $14$ & $ $ & $16$\\ \hline
       \multicolumn{12}{c}{} \\
     \end{tabular}
-    \caption{Comparison of RME with ORCA and ORCA* with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destinations eventually ($s$).
+    \caption{Comparison of RME with ORCA and DS+ORCA with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destinations eventually ($s$).
     %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
@@
 %The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
-Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.
+Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)
 
@@
 
-We present robust motion execution, a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
-Our approach does not require communication between the robots and provides formal collision guarantees for simple robot models.
+We present a method for robust motion execution that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
+Our approach does not require communication between the robots.
 We use a novel planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.

### 2018-08-28 paper/paper.tex
updated paper

@@
 \usepackage{graphicx}
+\usepackage{hyperref}
 %\usepackage{nicefrac}
@@
 \newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}
+\newcommand{\changed}[1]{\textcolor{purple}{#1}}
 
@@
 %
-% Robust Motion Execution
-% 
-\title{Distributed Real-time Trajectory Replanning for Robust Motion Execution}% in Multi-Robot Systems}
-
-%
-%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
+% Robust Trajectory Execution
+% 
+\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}% in Multi-Robot Systems}
+
+% Distributed Real-time Trajectory Replanning for Robust Trajectory Execution
+% Robust Trajectory Execution for Distributed Multi-Robot Systems
+% Robust Trajectory Execution for Distributed UGV Teams
+% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Planning
+% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Replanning
+% Robust Trajectory Execution for Distributed Multi-Robot Teams Using Real-time Replanning
+
+%
+\titlerunning{Robust Trajectory Execution for Multi-Robot Teams}  % abbreviated title (for running head)
 %                                     also used for the TOC unless
@@
 \begin{abstract}
-We propose a method for robust motion execution that can be applied to a wide range  of  trajectory execution tasks. 
-It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
+Robust trajectory execution is an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
+We propose an algorithm for robust trajectory execution that compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, imperfect motion execution, and external disturbances.
 Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
-At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
 At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
-The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
+The discrete planner helps to avoid local minima, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
 Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
-We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
+At the low-level, we use buffered Voronoi cells as a multi-robot collision avoidance strategy.
+Compared to ORCA, our approach supports higher-order dynamic limits and avoids deadlocks better.
+We demonstrate our approach in simulation and on physical robots, showing that it can operate in real time.
 %\keywords{trajectory planning, collision avoidance, multi-robot systems}
@@
 \section{Introduction}
-Motion planning for multi-robot systems is widely used and in particular important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles around.
+Motion planning for multi-robot systems is particularly important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles.
 Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
-Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
-However, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.
-
-We propose a method for robust motion execution that can be applied to wide range of trajectory execution tasks.
-It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or other external disturbances.
-Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
-Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
-Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
-Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense their neighbors' positions and the obstacles around them.
+Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives such as total energy used~\cite{crazyplanning-ieeetro};
+however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.
+
+To compensate for changes in the environment or imperfect execution, one might apply cooperative collision avoidance strategies, such as ORCA~\cite{orca}, at runtime.
+However, such algorithms often operate locally and do not take the pre-planned trajectories into account.
+Robust trajectory execution, on the other hand, avoids future collision more effectively because it directly considers pre-planned trajectories.
+Consider the example in Fig.~\ref{fig:swap2}(a), where two robots must swap positions.
+The pre-planned trajectories are collision-free, but they do not consider the newly introduced obstacle and the blue robot does not start at its correct location.
+However, the pre-planned trajectories can be used as guidance for replanning.
+In this example, robots can get stuck if a local cooperative collision avoidance strategy is applied.
+%We propose robust trajectory execution as an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
+%Our algorithm compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
+%Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
+%Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
+Using our method, the robots can successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
+Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense other robots' positions and the obstacles around them.
 
@@
 %\end{subfigure}
-\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
+\caption{(a) Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines).
 The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
-Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory (b).
+(b) Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory.
 }
@@
 
-Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
+Robust trajectory execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
 In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
-Our method relies on the \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
+Our method relies on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
 We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
 The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.
-
-We show in simulations that our method avoids collisions and deadlocks more successfully compared to ORCA~\cite{orca}.
+%We also apply our dynamic receding horizon approach to ORCA and show that it helps to avoid deadlocks more effectively in that case, although the ORCA-based solution does not support higher-order dynamic limits.
+
+% The contributions of this work are
+The main contribution of this work is a novel distributed algorithm for robust trajectory execution that considers higher-order dynamic limits.
+It also compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
+%It also compensates for environmental changes and imperfect trajectory execution.
+We show in simulations that our method avoids deadlocks better than ORCA~\cite{orca}.
 Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.
@@
 
+\section{Related Work}
+\label{sec:relatedWork}
+
+% Our method is closely related to cooperative collision avoidance.
+% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
+% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
+% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
+% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
+Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
+Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
+%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
+Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
+Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
+Safety barrier certificates achieve collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
+%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
+Our robust trajectory execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)
+
+%Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
+%Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
+%The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
+%The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search.
+Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
+Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
+Similar to previous work we use discrete search to quickly get out of local minima, but do so in a distributed manner.
+
+While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
+%Polynomial trajectories can be generated using a QP~\cite{richterISRR} without taking obstacles directly into account.
+%QP-based formulations on B-splines or B\'ezier curves have been used to consider obstacles in form of linear hard constraints~\cite{flores,tang}.
+%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
+%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
+Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
+In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
+In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
+%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
+The optimization can use a discrete plan as an initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
+In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.
+
+% multi-robot:
+% BVC, RVO, barrier certificate
+
+% stanford paper
+
+% tu munich paper
+%\cite{replanning-usenko}
+
+% t-ro paper (& other traj opt papers)
+%\cite{crazyplanning-ieeetro}
+%\cite{tang}
+%\cite{flores}
+
+% other traj opt:
+%\cite{replanning-eth}
+%\cite{richterISRR}
+
 \section{Problem Formulation} \label{problemFormulation}
@@
 \begin{align*}
-    \vo_i(t)&:\text{ original trajectory of $i\th$ robot where time } t\in[0,T_i],\\
+    \vo_i(t)&:\text{ original trajectory $(\R\to \R^n)$ of $i\th$ robot where time } t\in[0,T_i],\\
     %ct&:\text{ current global time},\\
@@
     %\{\vp_i\}&:\text{ set of positions of all robots},\\
-    R(\vp)&:\text{ collision model of a robot at position $\vp$ (sphere with radius $r_s$), and}\\
+    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\ %(we use a sphere with }
+     %     & \text{radius $r_s$, but $R(\vp)$ can be any convex shape), and}\\
     \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
@@
 
-Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of its neighbors as well as the current occupied space $\cO_i$ around it.
-We represent $\cO_i$ as a set of $\uptheta$ convex obstacles; our approach can accommodate for different sensing modalities, including LIDAR and RGB-D cameras.
+Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of other robots as well as the current occupied space $\cO_i$ around it\footnote{Since our approach can accommodate many sensing modalities, we do not provide a specific sensing capability in the general problem.}.
+We represent $\cO_i$ as a set of $\uptheta$ convex obstacles.
 %, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
@@
 %Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
-Each robot $i$ must execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
+Each robot $i$ must execute a trajectory $\vf_i(t)$, where $\vf_i(t)$ is a solution to the following optimization problem:
 \begin{align}
@@
     &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
-    &\vf_i(t)\text{ is collision free, and}\\ 
+    &\vf_i(t)\text{ is collision-free, and}\\ 
     &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
@@
 We solve this problem approximately, using a dynamic receding horizon approach iteratively.
-At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
+At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to the user-provided period $\delta t$.
+We set $R(\vp)$ to a sphere with radius $r_s$ centered at $\vp$.
 %We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.
@@
 
-This section introduces important mathematical concepts and notation that will be used throughout the paper.
+This section introduces important mathematical concepts and notations that will be used throughout the paper.
 
@@
 \end{align}
-where $\|\vp\|$ is the L2-norm of the vector $\vp$.
+where $\|\vp\|$ is the L$^{2}$-norm of the vector $\vp$.
 
@@
 % \end{align}
-
 Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.
@@
 
-We use splines as trajectories where each piece is a B\'ezier curve.
+We use splines as trajectories with user-specified number of pieces ($l$) and degree ($d$), where each piece is a degree $d$ B\'ezier curve.
 Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j\th$ piece where $j \in \{1,2,\ldots,l\}$.
@@
 
-A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
+A quadratic cost function is represented using the matrix $H$ and the vector $\vg$. 
+The quadratic cost function we use is described in Section~\ref{continuousOptimization}.
+
+The constraints are represented using the matrix $A$ with vectors $\vlbA$ and $\vubA$.
 Notice that all constraints should be linear in the decision variables.
-
 There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
-An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative.
+An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector in a specified degree of differentiation.
 This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
@@
 If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points.
-All 3 types of constraints are linear in control points.
-The construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.
+All three types of constraints are linear in control points.
+The exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.
 
@@
 Replanning is done at a fixed period of $\delta t$.
-In each iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $f^K_i(t)$.
+In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory \changed{$\vf^K_i(t)$}.
 The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
@@
 
-%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
-%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
-%We use this discrete path as an initial guess in trajectory optimization.
-%If discrete planning is not required, we use the control points of the previous plan as the initial guess.
-
-%We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
-%In both cases, buffered Voronoi cells are used to ensure collision-free operation for up to time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.
-
-%Dynamic limits cannot be represented as linear constraints in our QP.
-%Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
-%As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving of the QP.
-
-At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c\th$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.
+In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
+If discrete planning is required, we execute a discrete search that results in a discrete path that is collision-free but not smooth.
+We use this discrete path as an initial guess in trajectory optimization.
+If discrete planning is not required, we use the control points of the previous plan as the initial guess.
+
+We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
+In both cases, buffered Voronoi cells are used to ensure collision-free operation for time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.
+
+Dynamic limits cannot be represented as linear constraints in our QP.
+Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
+While dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, and since the initial point constraints are violated when the durations are increased, we re-solve the QP.
+
+At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$; is continuous up to the $c\th$ derivative; obeys the dynamic limits of the robot; tries to stay close to the original trajectory; and is a good starting point for the next iteration.
 We execute this trajectory for a period of $\delta t$ and replan for the next iteration.
@@
 %\begin{adjustbox}{width=\textwidth,caption={bla}}
-\resizebox{0.9\textwidth}{!}{
+\resizebox{1.0\textwidth}{!}{
 % \footnotesize
@@
     \draw [arrow] (trajopt) -- (dynamiclimits);
-    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Start next iteration} -|   (discrete);
+    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Execute for $\delta t$ and start next iteration} -|   (discrete);
     \draw [arrow] (dynamiclimits) -- node[anchor=east] {Yes} (rescale);
@@
 
-Robot $i$ executes discrete planning if any of the following conditions are true:
+Robot $i$ executes discrete planning if any of the following conditions are true, where $\psi=K\delta t$ is the current time:
 \begin{enumerate}
@@
 \end{enumerate}
-The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second condition handles cases where previously unknown robots appear and cases where robots are close and moving towards each other, and the third condition handles dynamic obstacles and numerical issues that resulted in a trajectory with collisions in the previous iteration.
-The main reason of these numerical issues is explained in Section~\ref{simulationSection}.
+The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot.
+The second condition handles cases where previously unknown robots appear and cases where robots are close and moving towards each other.
+\changed{The third condition handles dynamic obstacles, and  also infeasibilities and numerical issues that resulted in a trajectory with collisions in the previous iteration.
+Sections~\ref{theoreticalGuarantees} and Section~\ref{simulationSection} detail reasons for infeasibilities and  numerical issues, respectively.}
+%The reason for infeasibilities is explained in Section~\ref{theoreticalGuarantees} and the reason for numerical issues is explained in Section~\ref{simulationSection}.}
 
@@
 %\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
-\includegraphics[width=0.45\textwidth]{images/swap2_discrete.pdf}
+\includegraphics[width=0.49\textwidth]{images/swap2_discrete.pdf}
 %\label{fig:swap2:discrete}
@@
 %\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
-\includegraphics[width=0.45\textwidth]{images/swap2_cont_red.pdf}
+\includegraphics[width=0.49\textwidth]{images/swap2_cont_red.pdf}
 %\label{fig:swap2:cont}
@@
 Example at $t=\SI{3.9}{s}$.
-Discrete path around an obstacle and other robot back to the original trajectory (a).
-Continuous trajectory split into four pieces and respective hyperspaces (b).
+(a) Discrete path around an obstacle and other robot back to the original trajectory.
+(b) Continuous trajectory split into four pieces and respective hyperspaces.
 }
@@
 \subsection{Continuous Optimization}\label{continuousOptimization}
-We compute a new trajectory by formulating a quadratic optimization problem where the decision variables are the concatenated control points of the pieces.
+We compute a new trajectory by formulating a quadratic program where the decision variables are the concatenated control points of the pieces.
 The parameters $d$ and $l$ of the pieces (see Section~\ref{bezierCurves}) are provided by the user.
@@
 If discrete planning is performed, initial variables and durations are calculated from the discrete path as explained in Section~\ref{discretePlanning}.
-The objective that we minimize is defined as
+The objective that we minimize is defined 
 \begin{align}
@@
 %Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
-The first term of the objective minimizes the energy along the trajectory, and is the combination of integrated squared derivatives up to degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro}.
-%richterISRR
+The first term of the objective minimizes the energy along the trajectory, and is the combination of integrated squared derivatives up to user provided degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
 The second term of the objective penalizes deviation from the given end points for each piece of the trajectory with different weights $\theta_j$.
@@
 
-For robot-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
+For robot-to-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
 % . For each control point of the first piece, we add $m-1$ hyperspace constraints as
@@
 These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
-As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-robot collision will occur up to time $\delta t$.
-
-For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO_i$ for each curve piece $j$.
-Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j\th$ piece from the $b\th$ obstacle obtained from $\cO_i$ (these can be computed, e.g., using support vector machines~\cite{SVM}).
+As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.
+
+For robot-to-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO_i$ for each curve piece $j$.
+Let $M_j^b$ be the hyperplane that seperates the initially guessed control points of the $j\th$ piece from the $b\th$ convex obstacle obtained from $\cO_i$ (these can be computed, e.g., using support vector machines~\cite{SVM}).
 We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
 We add hyperspace constraints as before, requiring control points of the $j\th$ piece in the non-occupied side of each hyperplane $M_j^b$.
-These constraints ensure that no robot-obstacle constraint will occur up to time $\tau'$.
+These constraints ensure that no robot-to-obstacle collision will occur up to time $\tau'$.
 In case discrete planning was executed, we additionally treat other robots as static obstacles.
@@
 
-Moreover, we add continuity constraints that enforce the continuity requirement between pieces and initial point constraints that enforce continuity requirements between iterations.
+Moreover, we add continuity constraints that enforce the continuity requirements between pieces and initial point constraints that enforce continuity requirements between iterations.
 
@@
 
-\subsection{Theoretical Guarantees} %maybe
-
-For robot-robot collision avoidance our approach uses buffered Voronoi cells and retains the same theoretical guarantee, that we restate here:
-if robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision free.
-
+\subsection{Theoretical Guarantees} \label{theoreticalGuarantees}
+
+\changed{For robot-to-robot collision avoidance our approach uses buffered Voronoi cells which has the following theoretical guarantee:}
+if robots start in a collision-free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision-free.
 However, this guarantee has only been proven for the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
-We cannot provide formal guarantees under arbitrary disturbances.
-However, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
+\changed{The QP in our formulation has additional constraints that can cause it to be infeasible.
+However, in this case, we can simply fallback to the QP formulation of the BVC approach, thus retain the same theoretical guarantee.}
+
+Formal guarantees under arbitrary disturbances \changed{and higher order dynamics cannot be provided}.
+\changed{In fact, our QP can fail if it is not feasible to satisfy all safety and continuity constraints under the given dynamic limits.}
+\changed{However, our empirical evaluation presented in Section~\ref{simulationSection} shows that the QP rarely fails and even if it does, the robots do not collide with each other and the obstacles since the QP becomes feasible in the following iterations.}
+\changed{In addition}, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
 
@@
 We implement our approach in C\texttt{++}.
-We use an occupancy grid as environment representation, because previous work has shown that such data structures can be updated in real-time on robots that are equipped with a LIDAR sensor or a RGB-D camera.
-In particular, OctoMap~\cite{octomap} is an octree-based 3D occupancy grid that can be run on UAVs with at least \SI{4}{Hz} update rate~\cite{replanning-eth}.
+We use an occupancy grid as the environment representation, because previous work has shown that such data structures can be updated in real-time on robots that are equipped with a LIDAR sensor or an RGB-D camera.
+In particular, OctoMap~\cite{octomap} is an octree-based 3D occupancy grid that can be run on unmanned aerial vehicles with at least \SI{4}{Hz} update rate~\cite{replanning-eth}.
 OctoMaps are memory efficient, but update operations can show high execution time variance.
 For local replanning, occupancy grids using ring buffers as data structures have been shown to achieve near constant execution time~\cite{replanning-usenko}.
-Our implementation uses a simple pre-initialized 2D occupancy grid such that future implementations could leverage existing OctoMap or occupancy ring buffer libraries.
+Our implementation uses a simple pre-initialized 2D occupancy grid.
 
 We use the CVXGEN-package~\cite{cvxgen} to generate small QPs to find separating hyperplanes between control points and obstacles.
-As QP solvers we test with qpOASES~\cite{qpOASES} and OSQP~\cite{osqp}; both are open source and have been shown to work well in model predictive control scenarios.
-
+We test with qpOASES~\cite{qpOASES} and OSQP~\cite{osqp} as QP solvers; both are open source and have been shown to work well in model predictive control scenarios.
+
+A supplemental video containing some of our simulations and physical experiments is available at \url{https://youtu.be/LbWRvLfdwTA}.%https://youtu.be/Q96rTWdgSGQ}.
 % TODO: figure out if there is some baseline (look at buffered vornoi paper)
@@
 \subsection{Simulation}\label{simulationSection}
-We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) with Ubuntu 16.04 as operating system.
+We test our algorithm in a simulation running on a laptop computer (i7-4700MQ \SI{2.4}{GHz}, \SI{16}{GB}) with Ubuntu 16.04 as the operating system.
 
@@
 % (one example (16 case or generate larger w/ 32))
-In the first experiment, we test the scalability of our method in terms of the number of curves $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
-Our results are summarized in Tables~\ref{tab:curveCountScalability}, \ref{tab:obstacleCountScalability} and \ref{tab:robotCountScalability}, where $t_{avg}$ is the average time that qpOASES takes per iteration.
+In the first set of experiments, we test the scalability of our method in terms of the number of pieces $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
+Our results are summarized in Tables~\ref{tab:curveCountScalability}, \ref{tab:obstacleCountScalability} and \ref{tab:robotCountScalability}, where $t_{\text{avg}}$ is the average time that qpOASES takes per iteration.
 Our algorithm scales well with the number of robots.
@@
         \hline
-         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
          %1 & $1$ & $0$ & $4$ &$10$\\ \hline
@@
         \hline
-         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
          %7 & $4$ & $2$ & $4$ &$9$\\ \hline
@@
         \hline
-         \#&$l$&$\uptheta$ &$m$&$t_{avg}(ms)$  \\ \hline
+         \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
          %13 & $4$ & $5$ & $2$ &$10$\\ \hline
@@
 \end{minipage}
+\vspace{-10mm}
 \end{table}
+
+\begin{table}
+    \centering
+    \begin{tabular}{ |c|  c|c  | c| c| c| c| c| c| c|}
+      \cline{4-10}
+       \multicolumn{3}{c|}{} & \multicolumn{2}{c| }{ORCA} & \multicolumn{2}{c| }{DS+ORCA} & \multicolumn{3}{c|}{Our Method}\\ \hline
+      \# & $m$ &  $\uptheta$ &  $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & \changed{QP failures [\%]}\\ \hline
+      $16$ & $2$ & $4$  & $<1$  & $0$ & $<1$  & $2$ & $7$  & $2$ & \changed{$0.00$}\\ \hline
+      $17$ & $4$ & $12$  & $<1$  & $0$ & $<1$  & $4$ & $10$  & $4$ & \changed{$0.30$}\\ \hline
+      $18$ & $8$ & $30$  & $<1$  & $4$ & $<1$  & $8$ & $13$  & $8$ & \changed{$0.00$}\\ \hline
+      $19$ & $16$ & $9$ & $<1$  & $13$ & $<1$  & $16$ & $12$  & $16$ & \changed{$0.08$}\\ \hline
+      $20$ & $32$ & $30$ & $<1$ & $23$ & $<1$ & $32$ & $16$ & $32$ & \changed{$0.09 $}\\ \hline
+      \multicolumn{9}{c}{} \\
+    \end{tabular}
+    \caption{Comparison of our method, ORCA, and DS+ORCA with respect to average computation time ($t_{\text{avg}}$), the number of robots that reach  their destinations ($s$)\changed{, and the percentage of time that our QP fails}.
+    %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
+    %$t_{\text{avg}}$ is the average time of computation in each iteration, $v_{min}$ is the minimum percentage of being in a collision-free (valid) configuration among all robots, and $s$ is the number of robots that reach to their destinations in the end.
+    }
+    \label{tab:rvo2Comparison}
+\end{table}
+
+We also compare our method to two ORCA variants in the second set of experiments.
+\changed{In the first ORCA variant, w}e use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp_i\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp_i}{\delta t}$ otherwise.
+\changed{In the second ORCA variant, we combine ORCA and our discrete planning method with a dynamic receding horizon approach (denoted as DS+ORCA).
+We demonstrate that this variant resolves deadlocks better than the first variant.}
+For our method we use $\delta t = \SI{0.1}{s}$, $l=4$, and $d=7$ and for the ORCA variants we use $\delta t = \SI{0.01}{s}$.
+The results are summarized in Table~\ref{tab:rvo2Comparison}.
+All robots using our method or DS+ORCA reach their destinations, while robots using ORCA can easily get stuck around obstacles.
+Our method takes more time in computation compared to the ORCA variants, but produces smooth curves up to a user-defined smoothness.
+\changed{We use $c=2$ in our experiments meaning that the generated trajectories are continuous in position, velocity, and acceleration.}
+The ORCA variants, on the other hand, provide smoothness guarantees up to $c=0$ only, i.e., velocities can jump between iterations.
+Furthermore, the ORCA variants must sense the other robots' velocities and positions while our approach relies on positions only.
+
+\changed{We also report the percentage of time our QP fails, which happens no more than $\SI{0.3}{\percent}$ of the time.
+Notice that even if our QP fails, robots do not collide with each other and the obstacles, because the QP becomes feasible in the following iteration after $\SI{100}{ms}$.
+There are two reasons for QP failures: infeasibilities, which are explained in Section~\ref{theoreticalGuarantees}, and numerical issues.
+The numerical issues stem from separating hyperplane calculations between robots and obstacles.
+We use hard-margin SVMs to calculate separating hyperplanes.
+When robots get too close to obstacles, small epsilon values in SVM optimization may result in invalid hyperplanes, and hence QP fails}.
+%A video showing some experiments is available at \url{TODO}.
+The original trajectories and the occupancy grids in some experiments are shown in Fig.~\ref{fig:examples} and the supplemental video contains selected simulations.
 
@@
 \centering
-%\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
-\includegraphics[width=0.18\textwidth]{images/ex_16.pdf}
-%\label{fig:swap2:discrete}
-%}
+\includegraphics[width=0.32\textwidth]{images/ex_17.pdf}
 \hfill
-%\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
-\includegraphics[width=0.4\textwidth]{images/ex_17.pdf}
-%\label{fig:swap2:cont}
-%}
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=1.0\textwidth]{images/swap2_discrete.pdf}
-% \caption{Discrete path around an obstacle and other robot back to the original trajectory.}
-% \label{fig:swap2:discrete}
-% \end{subfigure} \hfill
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=1.0\textwidth]{images/swap2_cont_red.pdf}
-% \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
-% \label{fig:swap2:cont}
-% \end{subfigure}
+\includegraphics[width=0.32\textwidth]{images/ex_19.pdf}
 \hfill
-\includegraphics[width=0.40\textwidth]{images/ex_18.pdf}
-\hfill
-\includegraphics[width=0.40\textwidth]{images/ex_19.pdf}
+\includegraphics[width=0.33\textwidth]{images/physical.pdf}
 \caption{
-TODO
+The original trajectories and the occupancy grids in the simulation experiments 17 (a), 19 (b), and the physical experiment (c).
 }
-\label{fig:swap2_2}
+\label{fig:examples}
 \end{figure}
 
-We also compare our method (RME) to two ORCA variants.
-We use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp(\psi)\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp(\psi)}{\delta t}$ otherwise.
-In order to improve the behavior with obstacles, we combine ORCA in a different set of experiments with our discrete planning method (denoted as DS+ORCA).
-We use $l=4$ as the number of curves, and $d=7$ as the degree of B\'ezier curves.
-For RME we use $\delta t = \SI{0.1}{s}$ and for the ORCA variants $\delta t = \SI{0.01}{s}$.
-All algorithms are given more time than the original plans to complete because of the introduction of new obstacles to the environment.
-The results are summarized in Table~\ref{tab:rvo2Comparison}.
-Our method takes more time in computation, however is significantly better at avoiding collisions.
-All robots using RME reach their destinations, while robots using ORCA can get stuck as seen in all examples.
-Also, robots using ORCA appear in invalid configurations (collisions) as much as 49\% of the time, while robots using RME are almost never in invalid configurations.
-Invalid configurations in RME occur because of numerical problems particularly in seperating hyperplane calculations between robots and obstacles.
-We also note that ORCA does not provide the same smoothness guarantees ($c=0$, i.e., velocities can jump between iterations) and that it requires to sense the other robot's velocities instead of positions only.
-A video showing some examples is available at \url{TODO}.
-\begin{table}
-    \centering
-    \begin{tabular}{ |l|  c|c|  p{30mm} | c | c | c| c| c| c| c| c| r| }
-      \cline{5-13}
-       \multicolumn{4}{c|}{} & \multicolumn{3}{c| }{ORCA} & \multicolumn{3}{c| }{DS+ORCA} & \multicolumn{3}{c|}{RME}\\ \hline
-      \# & $m$ &  $\uptheta$ & description&  $t_{avg}(ms)$ & ? & $s$ & $t_{avg}(ms)$ & ? & $s$ & $t_{avg}(ms)$ & ? & $s$ \\ \hline
-      $16$ & $2$ & $4$ & \noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$2$ robots tries to swap  positions with an obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $0$ & $<1$ & $ $ & $2$ & $8$ & $ $ & $2$\\ \hline
-      $17$ & $4$ & $12$ & \noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$4$ robots tries to swap positions with a u-shaped obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $0$ & $<1$ & $ $ & $4$ & $11$ & $ $ & $4$\\ \hline
-      $18$ & $16$ & $12$ &\noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$16$ robots tries to swap positions with a u-shaped obstacle in the middle\vspace{.2\baselineskip}} & $<1$ & $ $ & $15$ & $<1$ & $ $ & $15$ & $14$ & $ $ & $16$\\ \hline
-      $19$ & $16$ & $9$ &\noindent\parbox[c]{\hsize}{\vspace{.2\baselineskip}$16$ robots tries to swap positions with $3$ obstacles in the middle\vspace{.2\baselineskip}}& $<1$ & $ $ & $13$ & $<1$ & $ $ & $14$ & $16$ & $ $ & $16$\\ \hline
-      $20$ & $16$ & $5$ &desc& $<1$ & $ $ & $13$ & $<1$ & $ $ & $12$ & $14$ & $ $ & $16$\\ \hline
-      \multicolumn{12}{c}{} \\
-    \end{tabular}
-    \caption{Comparison of RME with ORCA and DS+ORCA with respect to average computation time ($t_{avg}$), percentage of the worst-case robot being collision-free ($v_{min}$), and number of robots that reach their destinations eventually ($s$).
-    %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
-    %$t_{avg}$ is the average time of computation in each iteration, $v_{min}$ is the minimum percentage of being in a collision-free (valid) configuration among all robots, and $s$ is the number of robots that reach to their destinations in the end.
-    }
-    \label{tab:rvo2Comparison}
-\end{table}
 % could talk about nlopt/ipopt "issues"; or: other subsection (e.g, other approaches)
@@
 Those computers run Ubuntu 16.04 with ROS Kinetic, but C1+ has very limited computation capabilities (ARM Cortex-A5, max. \SI{10}{W}).
-The robots are arranged in a circle (\SI{2}{m} radius) and are tasked with swapping sides.
+The robots are arranged in a circle (\SI{2}{m} radius) and are tasked with swapping sides (Fig.~\ref{fig:examples}c).
 We plan the original trajectories with one static obstacle using a centralized planner~\cite{crazyplanning-heterogeneous}.
@@
 We conduct several experiments and add an additional obstacle, change the robots initial position, disturb the robots during run-time, or artificially stop one of the robots.
-In all cases robots successfully avoid collisions and in many cases they reach their final destination within the originally planned time limit.
+In all cases robots successfully avoid collisions and in many cases they reach their final destination within the originally planned durations.
 We also saw a few cases where robots got into a deadlock, which we attribute to the fact that the robots, unlike the simulation, cannot execute very low velocity commands.
-A video of our experiment is available at \url{TODO}.
+The supplemental video includes recordings of our experiment.
+%A video of our experiment is available at \url{TODO}.
 
@@
 
-\section{Related Work}
-\label{sec:relatedWork}
-
-% Our method is closely related to cooperative collision avoidance.
-% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
-% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
-% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
-% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
-Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
-Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
-%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
-Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
-Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
-Safety barrier certificates achieves collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
-%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
-Our robust motion execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)
-
-%Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
-%Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
-%The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
-%The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search.
-Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
-Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
-Similar to previous work we use discrete search to quickly get out of local minima, but do so in a distributed manner.
-
-While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
-%Using a discrete plan (generated by RRT*), polynomial trajectories can be generated using a quadratic program~\cite{richterISRR}.
-%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
-%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
-Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
-In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
-In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
-%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
-The optimization can use a discrete plan as initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
-In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.
-
-% multi-robot:
-% BVC, RVO, barrier certificate
-
-% stanford paper
-
-% tu munich paper
-%\cite{replanning-usenko}
-
-% t-ro paper (& other traj opt papers)
-%\cite{crazyplanning-ieeetro}
-%\cite{tang}
-%\cite{flores}
-
-% other traj opt:
-%\cite{replanning-eth}
-%\cite{richterISRR}
-
 \section{Conclusion}
 
-We present a method for robust motion execution that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
+We present a method for robust trajectory execution that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
 Our approach does not require communication between the robots.
 We use a novel planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
-We demonstrate in simulation and on physical robots that we can generate smooth trajectories in real-time, while avoiding collisions and deadlocks more successfully compared to ORCA.
-
-In future work we would like to conduct additional experiments with flying robots, handle dynamic obstacles, and consider the ability of robots to communicate to improve their plans.
+We demonstrate in simulation and on physical robots that we can generate smooth trajectories in real-time, while avoiding deadlocks successfully.
+In comparison, ORCA neither generates smooth trajectories nor avoids deadlocks in our test cases.
+
+\changed{In future work we would like to conduct additional experiments with robots using on-board perception and flying robots; handle dynamic obstacles; and consider communication between robots to improve their plans.
+We also would like to actively address numerical issues and QP infeasibilities.}
+
+\vfill
 
@@
 
+\pagebreak
+
 %
@@
 \bibliography{bibliography}
+
+\section{TODO}
+
+\begin{enumerate}
+    \item Reviewer 3
+        \begin{itemize}
+            \item[\checkmark] Check if ``robot executes the first segment'' was not clearly described in paper (flow chart + text)
+            \item[\checkmark] make sure that we clarified that QP can fail (and not that beziers might be colliding)
+        \end{itemize}
+    \item Reviewer 4
+        \begin{itemize}
+            \item[\checkmark] clarify that DS+ORCA is also ours; clarify that DS+ORCA resolves deadlocks better than ORCA
+            \item[\checkmark] define smoothness clearly (potentially just in experimental section)
+        \end{itemize}
+    \item Reviewer 5
+        \begin{itemize}
+            \item[\checkmark] consider putting related work after intro (check for ``dependencies'' in definitions etc)
+            \item[\checkmark] Numerical issues need some more description; in experiments, check how frequently it happens (quantify); make it clear that no collisions were observed in the final experiments; add more detailed investigation with relation to the cause of this as part of planned future work
+            \item[\checkmark] Check if BVC has ``better'' theoretical guarantees for second+-order systems; if no, we can refer to the BVC paper and state that we retain the same guarantees; otherwise: discuss:-)
+            \item[\checkmark] mention number of collisions (0) and smoothness parameter in experimental section
+        \end{itemize}
+\end{enumerate}
 

### 2018-08-28 paper/paper.tex
paper: latex source clean-up

@@
-%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% sample root file for your "contribution" to a proceedings volume
-%
-% Use this file as a template for your own input.
-%
-%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \documentclass{svproc}
@@
 \usepackage{hyperref}
-%\usepackage{nicefrac}
-
-%\usepackage{caption}
-%\usepackage{subcaption}
-%\captionsetup{compatibility=false}
-
-% Springer does not support subcaption/caption => use subfig instead and avoid loading the caption package
-\usepackage[caption=false]{subfig}
 
@@
 \usepackage{adjustbox}
-
-\usepackage{ upgreek }
-
+\usepackage{upgreek}
 \usepackage{xcolor}
-\newcommand{\Nora}[1] {\textbf{\textcolor{red}{#1}}}
-
 \usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,shadows, shapes.geometric, shapes.misc}
 \usepackage[utf8]{inputenc}
-
 \inputencoding{utf8}
@@
 
-%%%%%%%%%%%%%
-\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}
-\newcommand{\changed}[1]{\textcolor{purple}{#1}}
-
 \begin{document}
 \mainmatter              % start of a contribution
-%
-% Robust Trajectory Execution
-% 
-\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}% in Multi-Robot Systems}
-
-% Distributed Real-time Trajectory Replanning for Robust Trajectory Execution
-% Robust Trajectory Execution for Distributed Multi-Robot Systems
-% Robust Trajectory Execution for Distributed UGV Teams
-% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Planning
-% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Replanning
-% Robust Trajectory Execution for Distributed Multi-Robot Teams Using Real-time Replanning
-
-%
+\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}
 \titlerunning{Robust Trajectory Execution for Multi-Robot Teams}  % abbreviated title (for running head)
@@
 Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives such as total energy used~\cite{crazyplanning-ieeetro};
-however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.
+however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.
 
@@
 In this example, robots can get stuck if a local cooperative collision avoidance strategy is applied.
-%We propose robust trajectory execution as an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
-%Our algorithm compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
-%Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
-%Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
 Using our method, the robots can successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
@@
 \begin{figure}
-%\centering
-%\subfloat[Initial configuration and pre-planned trajectories.]{
 \includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
-%\label{fig:swap2:initial}
-%}
 \hfill
-%\subfloat[Final configuration and executed trajectories.]{
 \includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
-%\label{fig:swap2:final}
-%}
-%\begin{subfigure}[t]{0.48\textwidth}
-%\centering
-%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
-%\caption{Initial configuration.}
-%\label{fig:swap2:initial}
-%\end{subfigure} \hfill
-%\begin{subfigure}[t]{0.48\textwidth}
-%\centering
-%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
-%\caption{Final configuration and executed trajectories.}
-%\label{fig:swap2:final}
-%\end{subfigure}
 \caption{(a) Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines).
@@
 The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.
-%We also apply our dynamic receding horizon approach to ORCA and show that it helps to avoid deadlocks more effectively in that case, although the ORCA-based solution does not support higher-order dynamic limits.
 
-% The contributions of this work are
 The main contribution of this work is a novel distributed algorithm for robust trajectory execution that considers higher-order dynamic limits.
 It also compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
-%It also compensates for environmental changes and imperfect trajectory execution.
 We show in simulations that our method avoids deadlocks better than ORCA~\cite{orca}.
@@
 
-%\todo{perhaps write some more about what experiments we did, after we have the material}
-
-% \begin{tabular}{l||l}
-% \hline % global
-% $m$ & number of robots\\
-% $n$ & problem dimension\\
-% $c$ & order of derivative up to which smoothness is required \\
-% $\gamma_k$ & dynamic limit of each robot for the $k\th$ derivative of its trajectory\\
-% %$\Gamma_k$ & \\
-% %$r_s$ & radius\\
-% $R(\vp), r_s$ & space that robot occupies at position $\vp$ (sphere with radius $r_s$)\\
-% $\psi$ & current time\\
-% $\uptheta, \uptheta'$ & number of static obstacles\\
-% \hline % per robot
-% $\vo_i(t), t\in[0, T_i]$     &  original trajectory of robot $i$\\
-% $\vp_i(t)$ & position of robot $i$ at time $t$\\
-% $\cO_i$ & obstacles\\
-% %$\vf_i(t)$ & \\
-% $\cV_i$ & voronoi cell\\
-% $\cS_i^j$ & \\
-% $\cH_i^j, \valpha_i^j, \beta_i^j$ & hyperplane robot-robot\\
-% $M_j^b$ & hyperplane robot-obstacle\\
-% %$H$, $A$, $lbA$, $ubA$, $g$ & QP\\
-% $K$ & iteration\\
-% \hline % algorithm
-% $l$ & pieces\\
-% $d$ & degree\\
-% $\lambda_i, \theta_j$ & QP\\
-% $\tau, \tau'$ & \\
-% $\delta t$ & \\
-% $\vf^{K}_i(t)$ & duration $T^{K}_i$ \\
-% $\vf^{K}_{i,j}(t), t\in[0, T^{K}_{i,j}]$ & $j\th$ piece\\
-% $\vP^{K}_{i,j,\rho}$ & denotes the $\rho\th$ control point\\
-% \end{tabular}
-
 \section{Related Work}
 \label{sec:relatedWork}
-
-% Our method is closely related to cooperative collision avoidance.
-% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
-% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
-% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
-% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
 Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
 Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
-%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
 Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
@@
 Safety barrier certificates achieve collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
-%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
 Our robust trajectory execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)
 
-%Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
-%Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
-%The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
-%The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search.
-Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
 Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
@@
 While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
-%Polynomial trajectories can be generated using a QP~\cite{richterISRR} without taking obstacles directly into account.
-%QP-based formulations on B-splines or B\'ezier curves have been used to consider obstacles in form of linear hard constraints~\cite{flores,tang}.
-%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
-%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
 Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
@@
 In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
-%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
 The optimization can use a discrete plan as an initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
@@
 
-% multi-robot:
-% BVC, RVO, barrier certificate
-
-% stanford paper
-
-% tu munich paper
-%\cite{replanning-usenko}
-
-% t-ro paper (& other traj opt papers)
-%\cite{crazyplanning-ieeetro}
-%\cite{tang}
-%\cite{flores}
-
-% other traj opt:
-%\cite{replanning-eth}
-%\cite{richterISRR}
-
 \section{Problem Formulation} \label{problemFormulation}
-% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
-% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
-% output: at each dt: new trajectory such that there is no collision (guaranteed)
-% issues: no live-lock guarantee
 The general problem we would like to solve can be formulated as follows. 
@@
     \vo_i(t)&:\text{ original trajectory $(\R\to \R^n)$ of $i\th$ robot where time } t\in[0,T_i],\\
-    %ct&:\text{ current global time},\\
-    %\delta t&:\text{ replanning period},\\
-    %\tau&: \text{time horizon},\\ 
     c&:\text{ order of derivative up to which smoothness is required},\\
-    %\cO&:\text{ free space representation of the environment},\\
-    %\{\vp_i\}&:\text{ set of positions of all robots},\\
-    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\ %(we use a sphere with }
-     %     & \text{radius $r_s$, but $R(\vp)$ can be any convex shape), and}\\
-    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
-    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
+    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\
+    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.
 \end{align*}
@@
 We represent $\cO_i$ as a set of $\uptheta$ convex obstacles.
-%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
 Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
-%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
 Each robot $i$ must execute a trajectory $\vf_i(t)$, where $\vf_i(t)$ is a solution to the following optimization problem:
@@
 We set $R(\vp)$ to a sphere with radius $r_s$ centered at $\vp$.
-%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.
-
-%\todo{add paragraph about how we actually (approximately solve this problem)}
-
-% \begin{align*}
-%     \text{Given,}\ \ \ \ \ &\\
-%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
-%     ct&:\text{ current global time},\\
-%     \delta t&:\text{ replanning period},\\
-%     \tau&: \text{time horizon},\\ 
-%     c&:\text{ maximum continuity between pieces},\\
-%     \cO&:\text{ free space representation of the environment},\\
-%     \{\vp_i\}&:\text{ set of positions of all robots},\\
-%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
-%     &\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
-%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
-%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
-%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
-%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
-%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
-%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
-% \end{align*}
 
 \section{Preliminaries}
-
 This section introduces important mathematical concepts and notations that will be used throughout the paper.
@@
 \end{equation}
-% \begin{align}
-%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
-%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s. \label{voronoiBeta}
-% \end{align}
 
-% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
 For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside of at most one of the buffered Voronoi cells.
@@
 
-% \begin{align}
-%     \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
-% \end{align}
-
-% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
-% \begin{align}
-%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
-% \end{align}
 Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.
@@
 A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein};
-%This is called the \emph{convex hull property of B\'ezier curves}.
 we leverage this property to avoid robot-to-obstacle collisions.
@@
 $\vP^{K}_{i,j,\rho}$ denotes the $\rho\th$ control point of the $j\th$ piece where $\rho \in \{0,1,\ldots,d\}$.
-
-% \subsection{Support Vector Machine}\label{svmSection}
-% A support vector machine is a supervised learning method that is used to classify data into several classes.
-% In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
-% The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
-% The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
-% \begin{align*}
-%     \text{minimize}\ \ \  &\|\vw\|\\
-%     \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
-% \end{align*}
-% We use SVMs to define collision free convex subspaces that are obstacle-free.
 
@@
     \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
-    % &\vlb \leq \vx \leq \vub
 \end{split}
 \end{align}
-%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.
 
@@
 
-% There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
-
-% \begin{description}
-% \item [Initial Point Constraints]
-% An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
-% This requires $n$ linear constraints on the control points. %, $n$ being the dimension we are working in.
-
-% \item[Continuity Constraints]
-% A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
-% We take the vector difference of those values and require it to be equal to $\vzero$.
-% This requires $n$ linear constraints on the control points.
-
-% \item[Hyperspace Constraints]
-% A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
-% Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires one linear constraint for each relevant control point.
-% \end{description}
-
-% The construction of the QP is discussed in more detail in previous work~\cite{crazyplanning-ieeetro}.
-
 \section{Approach}
-
-% TODO: running example?
-
-%\subsection{Approach Overview}
 Replanning is done at a fixed period of $\delta t$.
-In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory \changed{$\vf^K_i(t)$}.
+In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $\vf^K_i(t)$.
 The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
-
-% In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i$.
-% We also assume that we have a current representation of the occupied space ($\cO_i$).
-Even if we use the complete occupation map in our examples, our method also works for local maps which can be constructed in practice by using LIDAR or RGB-D sensors.
-
-%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.
 
@@
 \centering
-%\begin{adjustbox}{width=\textwidth,caption={bla}}
 \resizebox{1.0\textwidth}{!}{
-% \footnotesize
 \begin{tikzpicture}[node distance = 2cm]
@@
     \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {Construct QP};
-    %\node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
-    %{constraint builder};
     \node (trajopt) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width = 2.5cm] {Trajectory Optimization};
@@
     \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {Rescaling};
-    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};
 
@@
     \draw [arrow] (contobjbuild) -- (trajopt);
-    %\draw [arrow] (constraintbuild) -- (trajopt);
     \draw [arrow] (trajopt) -- (dynamiclimits);
@@
 }
-%\end{adjustbox}
 \caption{Overview of the replanning pipeline.
@@
 
-%\todo{DISCUSS: planning/execution overlap?}
-
 \subsection{Discrete Planning} \label{discretePlanning}
-
 Robot $i$ executes discrete planning if any of the following conditions are true, where $\psi=K\delta t$ is the current time:
@@
 The second condition handles cases where previously unknown robots appear and cases where robots are close and moving towards each other.
-\changed{The third condition handles dynamic obstacles, and  also infeasibilities and numerical issues that resulted in a trajectory with collisions in the previous iteration.
-Sections~\ref{theoreticalGuarantees} and Section~\ref{simulationSection} detail reasons for infeasibilities and  numerical issues, respectively.}
-%The reason for infeasibilities is explained in Section~\ref{theoreticalGuarantees} and the reason for numerical issues is explained in Section~\ref{simulationSection}.}
+The third condition handles dynamic obstacles, and  also infeasibilities and numerical issues that resulted in a trajectory with collisions in the previous iteration.
+Sections~\ref{theoreticalGuarantees} and Section~\ref{simulationSection} detail reasons for infeasibilities and  numerical issues, respectively.
 
@@
 We find the earliest time $\tau'$ such that $R(\vo_g(\psi+\tau'))$ does not intersect with the obstacle and the blue robot where $g$ is the green robot.
-% such that the green robot re-joins its original trajectory after the obstacle.
 The discrete planner is then used to find a path  (green dotted line) that avoids both the static obstacle and the other (blue) robot, with a total of six path segments.
@@
 \centering
-%\subfloat[Discrete path around an obstacle and other robot back to the original trajectory.]{
 \includegraphics[width=0.49\textwidth]{images/swap2_discrete.pdf}
-%\label{fig:swap2:discrete}
-%}
 \hfill
-%\subfloat[Continuous trajectory split into four pieces and respective hyperspaces.]{
 \includegraphics[width=0.49\textwidth]{images/swap2_cont_red.pdf}
-%\label{fig:swap2:cont}
-%}
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=1.0\textwidth]{images/swap2_discrete.pdf}
-% \caption{Discrete path around an obstacle and other robot back to the original trajectory.}
-% \label{fig:swap2:discrete}
-% \end{subfigure} \hfill
-% \begin{subfigure}[t]{0.48\textwidth}
-% \centering
-% \includegraphics[width=1.0\textwidth]{images/swap2_cont_red.pdf}
-% \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
-% \label{fig:swap2:cont}
-% \end{subfigure}
 \caption{
@@
 \end{figure}
-
-% \begin{figure}
-% \centering
-% \subfloat[Voronoi decomposition.]{
-% \includegraphics[width=0.48\textwidth]{images/swap2_voronoi.pdf}
-% \label{fig:swap2:voronoi}
-% }
-% % \begin{subfigure}[b]{0.48\textwidth}
-% % \centering
-% % \includegraphics[width=1.0\textwidth]{images/swap2_voronoi.pdf}
-% % \caption{Voronoi decomposition.}
-% % \label{fig:swap2:voronoi}
-% % \end{subfigure} \hfill
-% % \begin{subfigure}[b]{0.45\textwidth}
-% % \centering
-% % \includegraphics[scale=0.6]{images/swap2_cont_red.pdf}
-% % \caption{Continuous trajectory split into four pieces and respective hyperspaces.}
-% % \label{fig:swap2:cont}
-% % \end{subfigure}
-% \caption{
-% %Snapshot at $t=3.9$.
-% }
-% \label{fig:swap2_3}
-% \end{figure}
-
-% consider moving ushape down (so green guy goes up)
-% fig showing (one of the) initial conditions violated
-% fig showing discrete plan and initial control points, color-coded by piece [might be just one figure]
 
@@
 where $\vchi_j$ is the point  where we want piece $j$ to end.
-%Refer to Section~\ref{bezierCurves} for the B\'ezier curve notation we use.
 The first term of the objective minimizes the energy along the trajectory, and is the combination of integrated squared derivatives up to user provided degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
@@
 If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
-%If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
-%This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
 The matrix $H$ (see Section~\ref{trajectoryOptimization}) for the first term of our objective can be constructed as in our previous work~\cite{crazyplanning-ieeetro}.
-%The construction of matrix $H$, as defined in Section~\ref{trajectoryOptimization}, for the first term of our objective function is explained in \cite{crazyplanning-ieeetro}.
 The second term is a quadratic function of the control points; hence it is straightforward to construct the $H$ matrix and the $\vg$ vector.
@@
 For robot-to-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
-% . For each control point of the first piece, we add $m-1$ hyperspace constraints as
-% \begin{align}
-%     \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
-% \end{align}
 These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
@@
 
-% Lastly, we add initial point constraints that enforce 
-% \begin{align*}
-% \frac{d^j\vf^{K}_i}{dt^j}(0) &= \frac{d^j\vp_i}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
-% \end{align*}
-
-% All these constraints are linear as explained in Section~\ref{trajectoryOptimization}. Therefore, we indeed have a constructible quadratic optimization problem.
-
-% For an instance of a problem in dimension $n$ where the trajectory has $l$ pieces of degree $d$, the number of variables in the optimization is $l(d+1)n$.
-% %Therefore the dimensions of the matrix $H$ is $l(d+1)n\times l(d+1)n$ and the vector $\vg$ is $l(d+1)\times 1$.
-% If there are $m$ robots in the environment, buffered voronoi decomposition imposes $(m-1)(d+1)$ linear constraints.
-% If there number of obstacles in the environment is $\uptheta$, SVM seperations impose $\uptheta l (d+1)$ linear constraints.
-If maximum required continuity is $c$, continuity requirements impose $(c+1)nl$ linear constraints.
-Therefore the matrix $A$ has $(m-1)(d+1) + \uptheta l(d+1) + (c+1)nl$ rows in total.
-% For example, in 2-dimensional space with $4$ robots where the trajectory has $4$ pieces of degree $7$, the environment is occupied with $10$ obstacles and $C^{2}$ continuity is required, the number of variables would be $64$, and the number of linear constraints would be $368$.
-
-% fig showing result from before (initial control points), hyperspaces (transparent, color-coded by piece), and resulting smooth trajectory (color-coded by piece).
-
-\subsection{Temporal Rescaling}  \label{temporalRescaling} % might be part of overview
+\subsection{Temporal Rescaling}  \label{temporalRescaling}
 Since we use fixed durations of the pieces and do not account for the dynamic limits of the robot during optimization, the resulting trajectory may violate the dynamic limits of the robot.
@@
 
-% potentially more subsections about SVM, hyperplanes etc, as needed
-% can look at T-RO paper for this part
-
 \subsection{Theoretical Guarantees} \label{theoreticalGuarantees}
-
-\changed{For robot-to-robot collision avoidance our approach uses buffered Voronoi cells which has the following theoretical guarantee:}
+For robot-to-robot collision avoidance our approach uses buffered Voronoi cells which has the following theoretical guarantee:
 if robots start in a collision-free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision-free.
 However, this guarantee has only been proven for the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
-\changed{The QP in our formulation has additional constraints that can cause it to be infeasible.
-However, in this case, we can simply fallback to the QP formulation of the BVC approach, thus retain the same theoretical guarantee.}
+The QP in our formulation has additional constraints that can cause it to be infeasible.
+However, in this case, we can simply fallback to the QP formulation of the BVC approach, thus retain the same theoretical guarantee.
 
-Formal guarantees under arbitrary disturbances \changed{and higher order dynamics cannot be provided}.
-\changed{In fact, our QP can fail if it is not feasible to satisfy all safety and continuity constraints under the given dynamic limits.}
-\changed{However, our empirical evaluation presented in Section~\ref{simulationSection} shows that the QP rarely fails and even if it does, the robots do not collide with each other and the obstacles since the QP becomes feasible in the following iterations.}
-\changed{In addition}, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
+Formal guarantees under arbitrary disturbances and higher order dynamics cannot be provided.
+In fact, our QP can fail if it is not feasible to satisfy all safety and continuity constraints under the given dynamic limits.
+However, our empirical evaluation presented in Section~\ref{simulationSection} shows that the QP rarely fails and even if it does, the robots do not collide with each other and the obstacles since the QP becomes feasible in the following iterations.
+In addition, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
 
@@
 
-%%%%%%%%%%
-
-% To provide formal guarantees, we make the following assumptions:
-% First, the robots have first-order integrator dynamics (and thus $c=0$);
-% second, the execution of the robots in synchronous;
-% third, robots execute trajectories perfectly;
-% fourth, robot trajectories are initially valid up to time $\tau$; and
-% fifth, obstacles are static.
-
-% For robot-robot collision avoidance our approach uses buffered Voronois cells and retains the same theoretical guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
-% \begin{lemma}
-% If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
-% \end{lemma}
-
-% For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, and then that the resulting QP is feasible.
-
-% \begin{lemma}
-% \label{lemma:hyperplanes}
-% In each iteration $K$, there exist separating hyperplanes $M_j^b$ that separate the initially guessed control points of the $j\th$ piece from the $b\th$ obstacle.
-% \end{lemma}
-% \begin{proof}
-% We consider two cases.
-% In the first case, discrete planning was successfully executed in iteration $K$.
-% Therefore, the discrete planner has found a collision free discrete path that separates the robot from all other obstacles and robots. 
-% Because the initially guessed control points are set on top of this path, the corresponding hyperplanes $M_j^b$ must exist.
-
-% In the second case, discrete planning was not executed (or failed to produce a path).
-% In that case, we use the computed control points from the previous iteration $K-1$.
-% By our assumption, the initial trajectories are valid up to time $\tau$.
-% Thus, by induction, the previous iteration had a valid trajectory. This trajectory is still valid, since the obstacles cannot move and therefore new hyperplanes $M_j^b$ must exist.\qed
-% \end{proof}
-
-% \begin{lemma}
-% In each iteration $K$, the constructed QP is feasible.
-% \end{lemma}
-% \begin{proof}
-% We consider each of the three types of constraints that could render the QP infeasible.
-% Hyperspace constraints can be fulfilled, because all hyperplanes exist according to Lemma~\ref{lemma:hyperplanes}.
-% Initial point constraints are limited to one constraint by our assumption that $c=0$.
-% Since the previous iteration $K-1$ produced a valid trajectory and the robot executed the trajectory perfectly, the initial point must be feasible.
-% We have $l-1$ continuity constraints that constrain the position of the last control point of curve $j$ to be identical to the first control point of curve $j+1$.
-% Those control points are already equal to each other for the initially guessed control points, no matter if discrete planning was executed or not.
-% %In case discrete planning was successfully executed, the last and first control points share a corner of the discrete path.
-% %In case discrete planning was not executed, the initially guessed control points are based on the result of the previous iteration $K-1$.
-% Because those points do not violate any of the other constraints, the continuity constraints must be feasible.\qed
-% \end{proof}
-
-% All lemmas together show that our approach is collision free under the stated assumptions.
-% Similar to other work, there are no formal liveness guarantees and there might be deadlocks~\cite{bufferedVoronoiCells}.
-% Our approach also works in practice for robots with higher-order dynamics, if robot execution is asynchronous, or trajectories are not executed perfectly, although there are no formal guarantees.
-% %This can be achieved by choosing larger safety radii~\cite{bufferedVoronoiCells}.
-
-% %%%%
-
-% % Our approach uses buffered voronoi cells and retains the same theoretical robot-robot collision guarantee, that we first restate here~\cite{bufferedVoronoiCells}:
-% % If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq r_s, \forall i\neq j$), then all future positions are in a collision-free configuration as well.
-
-% % We note that this only holds under two assumptions:
-% % first, the robots have first-order integrator dynamics, and second, the execution of the robot is synchronous.
-% % The first problem can be mitigated in practice by choosing larger safety radii~\cite{bufferedVoronoiCells}.
-% % We propose to address the second problem by shifting the voronoi hyperplanes by $\delta t \gamma_1$ to account for the worst-case phase shift in the robots' execution cycle.
-
-% % For robot-obstacle collision avoidance, we first show that the separating hyperplanes always exist, assuming perfect trajectory execution:
-
-% % \todo{need to remove third condition in discrete planning?}
-% % % assume c=0 for proof
-
-% % \begin{enumerate}
-% %     \item As long as each robot $i$ follows the same rule, no robot-to-robot collision occurs.
-The maximum phase shift between robots is $\delta t$.
-If the dynamic limit $\gamma_1$ for velocities is uniform between robots, we can account for the phase shift by shifting each voronoi hyperplane $H_i^j$ by $\gamma_i \delta t$.
-Notice that this is a pessimistic shift, that does not take robot $j$'s extend into account.
-We can do even better if the geometry of the robots are uniform.
-This update gives \emph{no robot collision guarantee} even there is phase shift during the execution.
-% %     \item The pessimistic shift mentioned above actually gives no robot-to-robot collision guarantee even if peers are non-cooperative that they do not obey buffered voronoi cell constraints.
-% %     \item As long as obstacles are not moving, no robot-to-obstacle collision occurs.
-If we know the maximum velocity $\nu$ of the obstacles in the environment, we can avoid moving obstacles as well by shifting the SVM seperating hyperplanes by $\nu \delta t $.
-This update gives \emph{no obstacle collision guarantee} even the obstacles are moving.
-% % \end{enumerate}
-% % see if we can formally get collision-free behavior (maybe only for synchronous execution) [see stanford paper]
-% % might be able to account for possible faceshift
-
 \section{Evaluation} \label{evaluationSection}
-
 We implement our approach in C\texttt{++}.
@@
 
-A supplemental video containing some of our simulations and physical experiments is available at \url{https://youtu.be/LbWRvLfdwTA}.%https://youtu.be/Q96rTWdgSGQ}.
-% TODO: figure out if there is some baseline (look at buffered vornoi paper)
-% different use-case examples (see README.md)
+A supplemental video containing some of our simulations and physical experiments is available at \url{https://youtu.be/LbWRvLfdwTA}.
 
@@
 
-% table1: scalability: #curves, #obstacles, #robots (voronoi constraint), qp-solver
-% (one example (16 case or generate larger w/ 32))
 In the first set of experiments, we test the scalability of our method in terms of the number of pieces $l$ we plan for, the number of occupied cells $\uptheta$ in the occupancy grid and the number of robots $m$.
@@
          \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
-         %1 & $1$ & $0$ & $4$ &$10$\\ \hline
          1 & $4$ & $0$ & $4$ & $10$\\ \hline
@@
          \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
-         %7 & $4$ & $2$ & $4$ &$9$\\ \hline
          6 & $4$ & $4$ & $4$ & $9$ \\ \hline
@@
          \#&$l$&$\uptheta$ &$m$&$t_{\text{avg}}\,[\si{ms}]$  \\ \hline
-         %13 & $4$ & $5$ & $2$ &$10$\\ \hline
          11 & $4$ & $5$ & $4$ &$9$\\ \hline
@@
        \multicolumn{3}{c|}{} & \multicolumn{2}{c| }{ORCA} & \multicolumn{2}{c| }{DS+ORCA} & \multicolumn{3}{c|}{Our Method}\\ \hline
-      \# & $m$ &  $\uptheta$ &  $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & \changed{QP failures [\%]}\\ \hline
-      $16$ & $2$ & $4$  & $<1$  & $0$ & $<1$  & $2$ & $7$  & $2$ & \changed{$0.00$}\\ \hline
-      $17$ & $4$ & $12$  & $<1$  & $0$ & $<1$  & $4$ & $10$  & $4$ & \changed{$0.30$}\\ \hline
-      $18$ & $8$ & $30$  & $<1$  & $4$ & $<1$  & $8$ & $13$  & $8$ & \changed{$0.00$}\\ \hline
-      $19$ & $16$ & $9$ & $<1$  & $13$ & $<1$  & $16$ & $12$  & $16$ & \changed{$0.08$}\\ \hline
-      $20$ & $32$ & $30$ & $<1$ & $23$ & $<1$ & $32$ & $16$ & $32$ & \changed{$0.09 $}\\ \hline
+      \# & $m$ &  $\uptheta$ &  $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & $t_{\text{avg}}\,[\si{ms}]$  & $s$ & QP failures [\%]\\ \hline
+      $16$ & $2$ & $4$  & $<1$  & $0$ & $<1$  & $2$ & $7$  & $2$ & $0.00$\\ \hline
+      $17$ & $4$ & $12$  & $<1$  & $0$ & $<1$  & $4$ & $10$  & $4$ & $0.30$\\ \hline
+      $18$ & $8$ & $30$  & $<1$  & $4$ & $<1$  & $8$ & $13$  & $8$ & $0.00$\\ \hline
+      $19$ & $16$ & $9$ & $<1$  & $13$ & $<1$  & $16$ & $12$  & $16$ & $0.08$\\ \hline
+      $20$ & $32$ & $30$ & $<1$ & $23$ & $<1$ & $32$ & $16$ & $32$ & $0.09 $\\ \hline
       \multicolumn{9}{c}{} \\
     \end{tabular}
-    \caption{Comparison of our method, ORCA, and DS+ORCA with respect to average computation time ($t_{\text{avg}}$), the number of robots that reach  their destinations ($s$)\changed{, and the percentage of time that our QP fails}.
-    %$m$ is the number of robots, $O$ is the number of occupied cells in the occupancy grid with grid size of $0.5$ meters.
-    %$t_{\text{avg}}$ is the average time of computation in each iteration, $v_{min}$ is the minimum percentage of being in a collision-free (valid) configuration among all robots, and $s$ is the number of robots that reach to their destinations in the end.
+    \caption{Comparison of our method, ORCA, and DS+ORCA with respect to average computation time ($t_{\text{avg}}$), the number of robots that reach  their destinations ($s$), and the percentage of time that our QP fails.
     }
@@
 We also compare our method to two ORCA variants in the second set of experiments.
-\changed{In the first ORCA variant, w}e use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp_i\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp_i}{\delta t}$ otherwise.
-\changed{In the second ORCA variant, we combine ORCA and our discrete planning method with a dynamic receding horizon approach (denoted as DS+ORCA).
-We demonstrate that this variant resolves deadlocks better than the first variant.}
+In the first ORCA variant, we use the RVO2 library~\cite{orca} and set the preferred velocities at time $\psi$ to $\vo_i'(\psi)$ if $\vp_i\approx \vo_i(\psi)$ or to $\frac{\vo_i(\psi) - \vp_i}{\delta t}$ otherwise.
+In the second ORCA variant, we combine ORCA and our discrete planning method with a dynamic receding horizon approach (denoted as DS+ORCA).
+We demonstrate that this variant resolves deadlocks better than the first variant.
 For our method we use $\delta t = \SI{0.1}{s}$, $l=4$, and $d=7$ and for the ORCA variants we use $\delta t = \SI{0.01}{s}$.
@@
 Our method takes more time in computation compared to the ORCA variants, but produces smooth curves up to a user-defined smoothness.
-\changed{We use $c=2$ in our experiments meaning that the generated trajectories are continuous in position, velocity, and acceleration.}
+We use $c=2$ in our experiments meaning that the generated trajectories are continuous in position, velocity, and acceleration.
 The ORCA variants, on the other hand, provide smoothness guarantees up to $c=0$ only, i.e., velocities can jump between iterations.
@@
 
-\changed{We also report the percentage of time our QP fails, which happens no more than $\SI{0.3}{\percent}$ of the time.
+We also report the percentage of time our QP fails, which happens no more than $\SI{0.3}{\percent}$ of the time.
 Notice that even if our QP fails, robots do not collide with each other and the obstacles, because the QP becomes feasible in the following iteration after $\SI{100}{ms}$.
@@
 We use hard-margin SVMs to calculate separating hyperplanes.
-When robots get too close to obstacles, small epsilon values in SVM optimization may result in invalid hyperplanes, and hence QP fails}.
-%A video showing some experiments is available at \url{TODO}.
+When robots get too close to obstacles, small epsilon values in SVM optimization may result in invalid hyperplanes, and hence QP fails.
 The original trajectories and the occupancy grids in some experiments are shown in Fig.~\ref{fig:examples} and the supplemental video contains selected simulations.
@@
 
-% could talk about nlopt/ipopt "issues"; or: other subsection (e.g, other approaches)
 \subsection{Physical Robots}
@@
 The supplemental video includes recordings of our experiment.
-%A video of our experiment is available at \url{TODO}.
-
-% \todo{screenshot?}
-%\todo{add url}
-
-%    describe typical examples (inline with the introduction)
-% potentially add picture real vs sim?
 
 \section{Conclusion}
-
 We present a method for robust trajectory execution that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, robots breaking down, or external disturbances.
@@
 
-\changed{In future work we would like to conduct additional experiments with robots using on-board perception and flying robots; handle dynamic obstacles; and consider communication between robots to improve their plans.
-We also would like to actively address numerical issues and QP infeasibilities.}
+In future work we would like to conduct additional experiments with robots using on-board perception and flying robots; handle dynamic obstacles; and consider communication between robots to improve their plans.
+We also would like to actively address numerical issues and QP infeasibilities.
 
 \vfill
-
-% future work
-% * how to get out of invalid states "as safe as possible"
-% * dynamic obstacles (w/ upper velocity bound)
-% * physical experiment w/ sensing
-% * 3D (drones w/ downwash)
-% * allow some communication (e.g., exchange planned control points) => can performance be improved?
 
@@
 
-\section{TODO}
-
-\begin{enumerate}
-    \item Reviewer 3
-        \begin{itemize}
-            \item[\checkmark] Check if ``robot executes the first segment'' was not clearly described in paper (flow chart + text)
-            \item[\checkmark] make sure that we clarified that QP can fail (and not that beziers might be colliding)
-        \end{itemize}
-    \item Reviewer 4
-        \begin{itemize}
-            \item[\checkmark] clarify that DS+ORCA is also ours; clarify that DS+ORCA resolves deadlocks better than ORCA
-            \item[\checkmark] define smoothness clearly (potentially just in experimental section)
-        \end{itemize}
-    \item Reviewer 5
-        \begin{itemize}
-            \item[\checkmark] consider putting related work after intro (check for ``dependencies'' in definitions etc)
-            \item[\checkmark] Numerical issues need some more description; in experiments, check how frequently it happens (quantify); make it clear that no collisions were observed in the final experiments; add more detailed investigation with relation to the cause of this as part of planned future work
-            \item[\checkmark] Check if BVC has ``better'' theoretical guarantees for second+-order systems; if no, we can refer to the BVC paper and state that we retain the same guarantees; otherwise: discuss:-)
-            \item[\checkmark] mention number of collisions (0) and smoothness parameter in experimental section
-        \end{itemize}
-\end{enumerate}
-
-% \section{TODO}
-
-% \todo{why are functions marked as vectors?}
-% %\todo{constraints are also slightly different for discrete vs. continuous}
-% %\todo{if discrete planning fails, we might not be able to compute separating hyperplanes!}
-% %\todo{$tau'$ so far only defined if discrete stage is executed!}
-
-% %BASKIN:
-% % * ros planning node
-% % * statistics python script for #robots succeed and #time invalid state (collision with other robots or obstacles)
-% * "evaluation framework"/automation to generate evaluation results
-
-% %WOLFGANG
-% % * traj controller C++ node for creates (including custom messages)
-% % * add realistic 6-robot example case
-% % * update sections 4.2 onwards
-%  * add video export to vis.py
-
-%Sunday:
-% * Meet at 10m warehouse
-% * test & tune create2 traj controller
-% * test planner
-% * record 4 videos (6 to 8 robots):
-%   * normal execution
-%   * execution w/ added obstacle
-%   * execution w/ motion manually disturbed
-%   * execution w/ robot(s) breaking in middle
-
-% Monday - Thursday/ Saturday: writing
-% 
-% May 11/13: physical robot experiments [warehouse]
-% May 14: paper ready for review within the lab
-% Tuesday May 22: submission
-
 \end{document}
